### 2021-07-06 paper/glossa/glossa-template-knitr-wordcount.tex
anonimized links

% see http://info.semprag.org/basics for a full description of this template
%\documentclass[linguex]{glossa}
% DO NOT FORGET TO setwd("paper/glossa/") where the Rnw file is.
\documentclass[brill,linguex]{glossa}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

% possible options: 
% [times] for Times font (default if no option is chosen)
% [cm] for Computer Modern font 
% [lucida] for Lucida font (not freely available)
% [brill] open type font, freely downloadable for non-commercial use from http://www.brill.com/about/brill-fonts; requires xetex
% [charis] for CharisSIL font, freely downloadable from http://software.sil.org/charis/
% for the Brill an CharisSIL fonts, you have to use the XeLatex typesetting engine (not pdfLatex)
% for headings, tables, captions, etc., Fira Sans is used: https://www.fontsquirrel.com/fonts/fira-sans
% [biblatex] for using biblatex (the default is natbib, do not load the natbib package in this file, it is loaded automatically via the document class glossa.cls)
% [linguex] loads the linguex example package
% !! a note on the use of linguex: in glossed examples, the third line of the example (the translation) needs to be prefixed with \glt. This is to allow a first line with the name of the language and the source of the example. See example (2) in the text for an illustration.
% !! a note on the use of bibtex: for PhD dissertations to typeset correctly in the references list, the Address field needs to contain the city (for US cities in the format "Santa Cruz, CA")

%\addbibresource{sample.bib} 
% the above line is for use with biblatex
% replace this by the name of your bib-file (extension .bib is required)
% comment out if you use natbib/bibtex

\let\B\relax %to resolve a conflict in the definition of these commands between xyling and xunicode (the latter called by fontspec, called by charis)
\let\T\relax
\usepackage{xyling} %for trees; the use of xyling with the CharisSIL font produces poor results in the branches. This problem does not arise with the packages qtree or forest.
\usepackage[linguistics]{forest} %for nice trees!

% \pdf* commands provide metadata for the PDF output. ASCII characters only!
\pdfauthor{A.B. \& C.D.}
\pdftitle{Agreement Attraction in Turkish}
\pdfkeywords{agreement attraction, syncretism, Turkish, bayesian, replication}

\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: 2,749}
% Optional short title inside square brackets, for the running headers.

\author[A.B. \& C.D.]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
{%as many authors as you like, each separated by \AND.
  \spauthor{\texttt{Hidden Hidden (A.B.)}\\ 
  \institute{\texttt{Hidden University}}\\
  \small{
    \texttt{hidden@hidden.edu}}
  }
  \AND
  \spauthor{\texttt{Hidden Hidden (C.D.)}\\ 
  \institute{\texttt{Hidden University}}\\
  \small{
    \texttt{hidden@hidden.edu}}
  }%
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\sffamily
\maketitle

\begin{abstract}
We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.
\end{abstract}

\begin{keywords}
  agreement attraction; syncretism; Turkish; bayesian; replication
\end{keywords}

\rmfamily

\section{Introduction}

People often fail to accurately process grammatical dependencies between different parts of a sentence \citep[e.g.,][]{GibsonThomas:1999,PhillipsEtAl:2011}. For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the syntactically unrelated attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed \textit{key}. Previous  studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with the singular attractor. This phenomenon, known as \textit{agreement attraction} \citep{BockMiller:1991} has been attested in a number of languages, such as in Arabic \citep{TuckerEtAl:2015}, Armenian \citep{AvetisyanEtAl:2020}, German \citep{LagoFelser:2018}, Hindi \citep{BhatiaDillon:2020}, Serbian \citep{RisticEtAl:2016}, Slovak \citep{BadeckerKuminiak:2007}, Spanish \citep{LagoEtAl:2015}, and recently in Turkish \citep{LagoEtAl:2019}.

\ex. \label{ex:pearlmutter} * The \underline{key} to the cabinets \underline{were} rusty from many years of disuse.

\citet{LagoEtAl:2019} demonstrated that genitive possessor (such as \textit{painters} in \textit{the painters' rival}) cause agreement attraction effects in Turkish. This finding appears to be at odds with \citeauthor{NicolEtAl:2016}'s (\citeyear{NicolEtAl:2016}) results, who failed to find a similar effect in English. \citet{LagoEtAl:2019} hypothesize that Turkish possessor noun phrases, unlike their English counterparts, may function as agreement attractors because Turkish genitive NPs may function as subjects of non-finite clauses in Turkish \citep{GokselKerslake:2005,Kornfilt:2011}. As a result, genitive NP in Turkish, but not in English, may match the subjecthood feature which may be used for cue-based retrieval of a verb's subject \citep{LewisVasishth:2005, ArnettWagers:2017}.

In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of case syncretism in the experimental sentences in their experiment, which resulted in all subject head nouns being ambiguous between possessive and accusative case.

\section{Agreement Attraction in Turkish}

Turkish is an SOV word order language which uses case to mark arguments \citep{GokselKerslake:2005,Kornfilt:2011,Kornfilt:2013}. Case markers have different forms depending on whether or not the last sound is a vowel. In order to break vowel-vowel clusters, Turkish uses a variety of sounds as epenthetic consonants including \textit{s}, \textit{y}, or \textit{n}.  For example, the genitive case can surface as \textit{-nin} or as \textit{-in}, depending on the last consonant of the stem. Importantly, the forms of the possessive marker and the accusative case are identical except for the epenthetic consonant. This means that they surface as \textit{-i} in consonant-ending words, but as \textit{-si} and \textit{-yi} respectively in vowel-ending words.

\citet{LagoEtAl:2019} present a speeded acceptability judgment study with sentences like \ref{ex:lago}, in which the number of the attractor and the verb was manipulated. The resulting 2x2 design indicated by slashes in \ref{ex:lago} consisted of two grammatical conditions, in which the verb agreed with the singular subject head noun, and two ungrammatical conditions, in which the verb carried plural agreement, and thus did not agree with the subject. In ungrammatical sentences, they found a higher percentage of \textit{acceptable} responses when the genitive attractor was plural than when it was singular, indicating agreement attraction. No such effect was found in grammatical sentences.

\ex. \label{ex:lago}
\gll Ressam-lar/\O-(n){\i}n rakib-i at\"{o}lye-den h{\i}zla uzakla\c{s}-t{\i}-lar/\O.\\
painter-\textsc{pl}/\textsc{sg}-\textsc{gen} rival-\textsc{poss} workshop-\textsc{abl} quickly walked.away-\textsc{pst}-\textsc{pl}/\textsc{sg}\\
\glt `The painter's/painters' rival walked away from the workshop quickly.'

\citet{LagoEtAl:2019} hypothesized that these effects originated from how case and number information is encoded and retrieved. According to \citeauthor{LewisVasishth:2005}'s (\citeyear{LewisVasishth:2005}) cue-based retrieval model, phrases are encoded in a content-addressable memory as bundles of features called \textit{chunks} which include information like number, gender, case, and syntactic function \citep{SmithVasishth:2020}. Under \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) proposal, participants predict the number of the verb based on the chunks they formed while reading the subject. In grammatical sentences with singular verb agreement, the number prediction and the verb number match, which causes no processing difficulty. In contrast, when participants fail to find the predicted number morphology on the verb, a memory-retrieval process is initiated. This process activates the search for a chunk matching two cues: the subjecthood feature ([+SUBJECT]) and the plural feature ([+PL]). While neither of the available noun phrases matches this specification in ungrammatical agreement attraction sentences, each of the NPs headed by \textit{painter} and \textit{rival} matches one of these cues. While this partial match mostly results in participants finding the sentence ungrammatical, they may retrieve the attractor \textit{painters} on some trials. \citet{LagoEtAl:2019} argue that this erroneous retrieval may be facilitated by the fact that genitive case marking on the attractor because genitive NPs can function as subjects of embedded clauses in Turkish. Due to the ubiquity of genitive subjects, attractors marked with genitive case were hypothesized to be a priori more likely agreement controllers.

A potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that all head nouns such as \textit{rival} in \ref{ex:lago} were consonant-ending and therefore locally ambiguous between possessive and accusative case \citep[66--67]{GokselKerslake:2005}. Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the head nouns' reduced association with subjecthood due case syncretism. We tested this hypothesis in a speeded-acceptability experiment with sentences similar to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}), but with unambiguously marked vowel-ending head nouns.

\section{The Present Study}

The present study tested predictions of the syncretism between possessive and accusative cases as an alternative explanation of the previously found agreement attraction effect in Turkish. We disambiguated between them by using vowel-ending nouns instead of consonant-ending head nouns as done in \citet{LagoEtAl:2019}. When attached to a vowel-ending noun, the possessive is realized as using \textit{-ni}, while the accusative maker would surface as \textit{-yi}. We hypothesized that if the morpho-phonological ambiguity was a key factor in agreement attraction in Turkish, resolving it should diminish the attraction effects.

\subsection{Participants}

We recruited 118 undergraduate students to participate in the experiment in exchange for course credit. All participants were native Turkish speakers, with an average age of 20 (range: 18 -- 32). The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at \texttt{Hidden University}. All participants provided informed consent before their participation and their identity are completely anonimized.

\subsection{Materials}

We used 40 sets of sentences like \ref{ex:our_items}, in which we manipulated (i) the number of the attractor noun and (ii) the number agreement on the verb. Plural number and plural agreement were both marked with the suffix \textit{-ler/-lar}, while the singular number and singular agreement were marked by its absence. We used the experimental items from \citet{LagoEtAl:2019} as a starting point for all items. We substituted ambiguous nouns for unambiguous alternatives, and in some cases, modified other parts of the sentence for plausibility reasons.

All sentences started with a complex subject NP like \textit{y\"{o}neticinin a\c{s}\c{c}{\i}s{\i}} `\textit{the manager's cook},' in which the genitive possessor functioned as the attractor, and the head noun carried an unambiguous possessive case marker. Because the plural marking on nominals is not optional and the head noun was singular, absent of \textit{-lar}, in all conditions, sentences with plural verb agreement were ungrammatical. Moreover, the relationship between the possessor and the head noun was controlled as in \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) original study and can be paraphrased using \textit{'s} or \textit{of} in English. The distribution of the verb types matched that of the original study, with twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. Pre-verbal adverbials also consisted of 2-3 words (15 characters on average).

One example set of experimental items is in \ref{ex:our_items}. The subject phrase is marked with square brackets, and the dependency between the subject head and the matrix verb is signaled using bold-face.

\ex. \label{ex:our_items}
  \a. * Plural Attractor, Ungrammatical (Plural Verb) \label{ex:expitem-plpl}\\
  \gll [Y\"{o}netici-ler-in \textbf{a\c{s}\c{c}{\i}-s{\i}}] mutfak-ta s\"{u}rekli \textbf{z{\i}pla-d{\i}-lar}\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
  \glt `The cooks of the manager jumped\textsubscript{\textsc{pl}} in the kitchen non-stop.'
  \b. Plural Attractor, Grammatical (Singular Verb) \label{ex:expitem-plsg} \\
  \gll [Y\"{o}netici-ler-in \textbf{a\c{s}\c{c}{\i}-s{\i}}] mutfak-ta s\"{u}rekli \textbf{z{\i}pla-d{\i}}\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
  \glt `The cooks of the manager jumped\textsubscript{\textsc{sg}} in the kitchen non-stop.'
  \b. * Singular Attractor, Ungrammatical (Plural Verb) \label{ex:expitem-sgpl}\\
  \gll [Y\"{o}netici-nin \textbf{a\c{s}\c{c}{\i}-s{\i}}] mutfak-ta s\"{u}rekli \textbf{z{\i}pla-d{\i}-lar}.\\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}\\
  \glt `The cook of the manager jumped\textsubscript{\textsc{pl}} in the kitchen non-stop.'
  \b. Singular Attractor, Grammatical (Singular Verb) \label{ex:expitem-sgsg}\\
  \gll [Y\"{o}netici-nin \textbf{a\c{s}\c{c}{\i}-s{\i}}] mutfak-ta s\"{u}rekli \textbf{z{\i}pla-d{\i}}. \\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}\\
  \glt `The cook of the manager jumped\textsubscript{\textsc{sg}} in the kitchen non-stop.'

We hypothesized that the experimental sentences in \ref{ex:our_items} might elicit a simple response strategy based on verb number because all ungrammatical sentences end with a plural-agreement-bearing verb. In contrast, all grammatical sentences end with a verb that lacks a plural agreement, thus singular. As a result, some participants may resort to classifying sentence acceptability based on their last word after repeated exposure to sentences like \ref{ex:our_items}. In order to preclude such a response strategy, we designed 40 filler sentences that would render it ineffective. We included 20 grammatical sentences like \ref{ex:gram_filler} with plural and 20 ungrammatical sentences like \ref{ex:ung_filler} with a singular verb. Filler items resembled experimental sentences in that they started with a complex genitive-possessive noun phrase. In contrast to the experimental items, however, the complex NPs were the subject of an adverbial clause instead of the main sentence. In grammatical fillers like \ref{ex:gram_filler}, we have used pro-dropped subjects, which enabled us to use plural verbs without having ungrammatical sentences.

\ex. \label{ex:fillers}
  \a. Grammatical Filler (Plural Verb) \label{ex:gram_filler}\\
  \gll [Sosyolog-un \textbf{\"{o}\u{g}renci-si}] konu\c{s}-unca tutars{\i}zl{\i}k a\c{c}{\i}\u{g}-a \textbf{\c{c}{\i}kar-d{\i}-lar}.\\ 
  sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}\\
  \glt `When the student of the sociologist spoke, they revealed an inconsistency.'
  \b. * Ungrammatical Filler (Singular Verb) \label{ex:ung_filler}\\
  \gll [Dans\"{o}z-\"{u}n \textbf{koca-s{\i}}] var-{\i}nca kap{\i} sakince \textbf{a\c{c}-t{\i}}. \\
  dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}\\
  \glt Intended:`When the husband of the dancer came, the door opened slowly.'

\subsection{Procedure}

The experiment was run online, using the web-based platform Ibex Farm \citep{Drummond2013}. Each experimental session took approximately 25 minutes to complete. Participants provided demographic information and gave informed consent to participate in the experiment. They then proceeded to read the instructions and were given nine practice trials before the experiment began.

Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentation of the sentence in the center of the screen, followed by a prompt to indicate their acceptability judgment. Sentences were presented word-by-word in the center for the screen in 30 pt font size, at a rate of 400 ms per word. Participants saw a blank screen for 100 ms between each word, and to see the next item, they needed to press the \texttt{space} key. Participants were asked to press the key \texttt{P} to indicate that a sentence is acceptable and \texttt{Q} to indicate that the sentence is unacceptable. They were instructed to provide judgments as quickly as possible. During the experiment, a warning message in red font appeared if they did not respond within 5,000 ms.

Participants saw 40 experimental and 40 filler sentences. Experimental sentences were distributed among four different lists according to a Latin-square design. Every participant saw one version of the experiment with a specific list and one item per condition.

\subsection{Analysis}

In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect we analyzed the data from the present experiment together with \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data, using the experiment as an additional factor in the analysis.

Prior to the analysis, we removed the data for all participants who failed to show sufficient sensitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected. Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between the grammatical condition \ref{ex:expitem-sgsg} and the ungrammatical condition \ref{ex:expitem-sgpl} fell below the threshold of 0.25 percentage points. We also excluded trials in which the participants missed the response deadline or gave too fast responses (below 200 ms). As a result, we excluded 10.22\% of the trials from our experiment and 2.38\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.

We analyzed responses using a Bayesian GLM assuming a Bernoulli-distributed response with a probit link function.  We used the R packages brms \citep{brms} and rstan \citep{rstan} to fit Bayesian hierarchical models \citep[e.g.,][]{GelmanHill:2007, NicenboimVasishth:2016}. We analyzed only experimental sentences and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors. We used by-participant and by-item intercepts and slopes for all predictors. All factors were sum-coded. We have used standard priors provided by the brms package.

In the results section, we provide posterior distributions for parameters given our data and model with 95\% credible intervals. For our models, we run 4 chains, each of which consists of 1000 warm-up iterations and 1000 sampling iterations. Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.

\subsection{Results}

Figure \ref{fig:AverageResponses} shows the average proportions of `acceptable' responses by experimental condition for both the original experiment in \citet{LagoEtAl:2019} and our replication with unambiguous possessive marking. It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = 0.22, SE = 0.01) than their counterparts with singular attractors (M = 0.11, SE=0.01). The magnitude of the effect (0.11) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was 0.11. Accuracy rates for grammatical conditions were nearly equal (M = 0.93 and 0.92, SE = 0.01 and 0.01, for singular and plural attractors respectively).

\begin{figure}[hbt!]
\centering

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/AverageResponses-1}

}

\end{knitrout}

\caption{The average percentage of acceptable responses according to the experimental conditions in our study and \citet{LagoEtAl:2019}. Error bars signal standard errors calculated following \citet{Cousineau:2007}.}
\label{fig:AverageResponses}
\end{figure}

Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function. The main effect of grammaticality ($\hat{\beta}=3.08;$ $CI=[2.84; 3.33];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences. Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.04; -0.42];$ $P(\beta<0)> .999$) indicated a more prominent effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect. There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.27;$ $CI=[-0.77; 0.25];$ $P(\beta<0)=    .85$).

\begin{figure}[hbt!]
\centering

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/ResponseModel-1}

}

\end{knitrout}

\caption{Estimates and 95\% credible intervals for the regression coefficients for the model of our experiment and \citet{LagoEtAl:2019}.}
\label{fig:ResponseModel}
\end{figure}

\section{Discussion \& Conclusion}

In this paper, we re-examined the findings of \citet{LagoEtAl:2019} and investigated the effect of local case ambiguity on Turkish agreement attraction using genitive-possessive constructions in a speeded acceptability judgment experiment. The main question we asked was whether \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings can be explained with an alternative hypothesis. In their work, there was a possible confound in the experimental items. All head nouns were locally ambiguous between the possessive and the accusative case. We hypothesized that participants may encode the head-noun as marked with the accusative case (a non-subject case in Turkish), and thus, the retrieval of the head subject may be hindered in some trials. If Turkish agreement attraction effects resulted from this ambiguity, we should not observe any effect of plural attractor in ungrammatical sentences when the case of the head noun is disambiguated.

Our experimental findings were comparable with \citet{LagoEtAl:2019} and previous agreement attraction studies. We observed that the existence of a plural attractor increased the overall error rates the participants did, and this effect was amplified even more in ungrammatical sentences. As for the effects of case ambiguity, the findings did not support our hypothesis. The findings were not conclusive on whether or not ambiguity played a role. Participants still retrieved plural attractors in ungrammatical sentences more than they did with singular attractors.

Our model, where we incorporate data from both our experiment and \citet{LagoEtAl:2019}, did not show a three-way interaction between Ambiguity, Grammaticality, and Plural Attractor. This means that when the possessive marker is disambiguated agreement attraction (the interaction between Grammaticality and Plural Attractor) does not diminish in effect size. Considering the posterior distributions, we interpreted these results as pointing towards a piece of inconclusive evidence for the effect of ambiguity in agreement attraction effects. As a result, we successfully replicated the findings of \citet{LagoEtAl:2019} with disambiguated head nouns.

Taken together, these results suggest (i) that Turkish agreement attraction effects are not due to a possible erroneous encoding of the possessive marker, and (ii) that local ambiguities in case, syncretism, do not play a role in agreement attraction. Participants do not rely on form-related cues in decision-making processes. These findings support an agreement attraction theory that makes use of abstract linguistic features.

%\printbibliography %for use with biblatex; comment out if you use natbib
\bibliography{gp_short} %for use with natbib; comment out if you use biblatex, and change 'sample' by the name of your bib-file

\section*{Appendix A: Ungrammatical Sentences Model}

\begin{figure}[hbt!]
\centering

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/UngramResponseModel-1}

}

\end{knitrout}

\caption{Estimates and 95\% credible intervals for the regression coefficients for the model of our experiment and \citet{LagoEtAl:2019}. In this model, only the ungrammatical sentences are included}
\label{fig:UngramResponseModel}
\end{figure}

\begin{table}

\caption{\label{tab:unnamed-chunk-3}Point estimate, estimate error, and credible interval for Regression coefficients}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
  & Estimate & Est.Error & Q2.5 & Q97.5\\
\midrule
Intercept & -1.2216372 & 0.0897748 & -1.3990933 & -1.0491069\\
cEndsInConsonant & 0.0740791 & 0.1739013 & -0.2713538 & 0.4199774\\
cAttractorPlural & 0.4594237 & 0.0995349 & 0.2560289 & 0.6526212\\
cEndsInConsonant:cAttractorPlural & 0.0077682 & 0.1629159 & -0.3157023 & 0.3250568\\
\bottomrule
\end{tabular}
\end{table}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% TeX-engine: luatex
%%% End:

### 2021-07-06 paper/glossa/glossa-template-knitr.Rnw
anonimized links

--- 2021-07-06 paper/glossa/glossa-template-knitr-wordcount.tex
@@
 % DO NOT FORGET TO setwd("paper/glossa/") where the Rnw file is.
-\documentclass[brill,linguex]{glossa}\usepackage[]{graphicx}\usepackage[]{color}
-% maxwidth is the original width if it is less than linewidth
-% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
+\documentclass[brill,linguex]{glossa}
 
@@
 
+<<wordcount, echo=FALSE, cache=FALSE>>=
+library(knitr)
+
+comma <- function (x, ...) {
+  format(x, ..., big.mark = ",", scientific = FALSE, trim = TRUE)
+}
+
+# To dynamically extract name of the current file, use code below
+nameoffile <- current_input() # get name of file
+nof2 <-  strsplit(nameoffile,"\\.")[[1]][1] # extract name, drop extension
+noftex <- paste(nof2, ".tex", sep="") # add .tex extension
+nofwordcount <-  paste(nof2, '-','wordcount', '.tex', sep = "") # prepare a tex file for word count
+if (file.exists(nofwordcount)) {unlink(nofwordcount)} #delete the previous file.
+
+con <- file(noftex, open = 'r') # open the file with R
+while(TRUE) {
+  line <- readLines(con, n = 1) # read lines
+  if(length(line) == 0) break # pass if nothing is there
+  else if(!endsWith(line, "%exclude")){ # if the line does not end with %exclude 
+    write(line, file = nofwordcount, append = TRUE) # write it to the new file
+  } 
+}
+close(con)
+
+systemcall <- paste("system('texcount -inc -incbib -total -sum ", nofwordcount, "', intern=TRUE)", sep="") # paste together texcount system command
+texcount.out <- eval(parse(text=systemcall)) # run texcount on current last compiled .tex file with edits
+
+sum.row <- grep("Sum count", texcount.out, value=TRUE) # extract row
+pattern <- "(\\d)+" # regex pattern for digits
+
+count <- regmatches(sum.row, regexpr(pattern, sum.row) )
+# extract digits
+
+count <- comma(as.numeric(count)) # add comma
+
+@
+
 % \pdf* commands provide metadata for the PDF output. ASCII characters only!
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: 2,749}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: \Sexpr{count}}
 % Optional short title inside square brackets, for the running headers.
@@
 }
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+
 \begin{document}
+
+<<include=FALSE>>=
+library(knitr)
+opts_chunk$set(
+concordance=TRUE
+)
+@
 
@@
 
-We recruited 118 undergraduate students to participate in the experiment in exchange for course credit.
-All participants were native Turkish speakers, with an average age of 20 (range: 18 -- 32).
+We recruited \Sexpr{n_subject} undergraduate students to participate in the experiment in exchange for course credit.
+All participants were native Turkish speakers, with an average age of \Sexpr{mean_age} (range: \Sexpr{min_age} -- \Sexpr{max_age}).
 The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at \texttt{Hidden University}.
@@
 Prior to the analysis, we removed the data for all participants who failed to show sufficient sensitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected.
-Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between the grammatical condition \ref{ex:expitem-sgsg} and the ungrammatical condition \ref{ex:expitem-sgpl} fell below the threshold of 0.25 percentage points.
-We also excluded trials in which the participants missed the response deadline or gave too fast responses (below 200 ms).
-As a result, we excluded 10.22\% of the trials from our experiment and 2.38\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.
+Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between the grammatical condition \ref{ex:expitem-sgsg} and the ungrammatical condition \ref{ex:expitem-sgpl} fell below the threshold of \Sexpr{accuracy_threshold} percentage points.
+We also excluded trials in which the participants missed the response deadline or gave too fast responses (below \Sexpr{rt_threshold} ms).
+As a result, we excluded \Sexpr{perc_deletion_exp1}\% of the trials from our experiment and \Sexpr{perc_deletion_lago}\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.
 
@@
 In the results section, we provide posterior distributions for parameters given our data and model with 95\% credible intervals.
-For our models, we run 4 chains, each of which consists of 1000 warm-up iterations and 1000 sampling iterations.
-Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.
+For our models, we run \Sexpr{n_chains} chains, each of which consists of \Sexpr{n_warmup} warm-up iterations and \Sexpr{n_iter-n_warmup} sampling iterations.
+Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/tr_short_agreement_attraction/}.
 
@@
 Figure \ref{fig:AverageResponses} shows the average proportions of `acceptable' responses by experimental condition for both the original experiment in \citet{LagoEtAl:2019} and our replication with unambiguous possessive marking.
-It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = 0.22, SE = 0.01) than their counterparts with singular attractors (M = 0.11, SE=0.01).
-The magnitude of the effect (0.11) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was 0.11.
-Accuracy rates for grammatical conditions were nearly equal (M = 0.93 and 0.92, SE = 0.01 and 0.01, for singular and plural attractors respectively).
+It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = \Sexpr{exp1_cur_entry1$M}, SE = \Sexpr{exp1_cur_entry1$SE}) than their counterparts with singular attractors (M = \Sexpr{exp1_cur_entry2$M}, SE=\Sexpr{exp1_cur_entry2$SE}).
+The magnitude of the effect (\Sexpr{m_effect}) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was \Sexpr{m_effect_lago}.
+Accuracy rates for grammatical conditions were nearly equal (M = \Sexpr{exp1_cur_entry3$M} and \Sexpr{exp1_cur_entry4$M}, SE = \Sexpr{exp1_cur_entry3$SE} and \Sexpr{exp1_cur_entry4$SE}, for singular and plural attractors respectively).
 
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+<<AverageResponses, echo=FALSE, fig.align='center', fig.height=3, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=
 
-{\centering \includegraphics[width=\maxwidth]{figure/AverageResponses-1}
+plot(p_avg_resp)
 
-}
-
-\end{knitrout}
+@
 
@@
 Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function.
-The main effect of grammaticality ($\hat{\beta}=3.08;$ $CI=[2.84; 3.33];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.04; -0.42];$ $P(\beta<0)> .999$) indicated a more prominent effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
-There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.27;$ $CI=[-0.77; 0.25];$ $P(\beta<0)=    .85$).
+The main effect of grammaticality (\Sexpr{estimate_cGrammatical}) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the negative interaction between grammaticality and attractor number (\Sexpr{estimate_cGrammatical_cAttractorPlural}) indicated a more prominent effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
+There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number (\Sexpr{estimate_threeway_interaction}).
 
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+<<ResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=
 
-{\centering \includegraphics[width=\maxwidth]{figure/ResponseModel-1}
+suppressWarnings({
+p_m_response
+})
 
-}
-
-\end{knitrout}
+@
 
@@
 
+\section*{Abbreviations} %exclude
+
+\textsc{abl} = ablative, \textsc{dat} = dative, \textsc{gen} = genitive, \textsc{loc} = locative, \textsc{nmlz} = nominalizer, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular.
+%exclude
+
+\section*{Data Availability} %exclude
+
+The data that support the findings of this study, the code, and the paper resources including \LaTeX{} and \texttt{Sweave} files are openly available in the anonimized github page at \url{https://anonymous.4open.science/r/tr_short_agreement_attraction/}.
+%exclude
+
+\section*{Authors' Contributions} %exclude
+
+A.B.
+conceived the initial version of the presented idea.
+A.B.
+and C.D.
+conceived and planned the final version of the experiment.
+A.B.
+implemented and carried out the experiment and performed initial numerical calculations and Bayesian analyses of the experiment.
+C.D.
+verified the analytical methods and carried out advanced analyses including \citet{Cousineau:2007} standard errors, advanced plotting, advanced decisions in Bayesian modelling, and R workflow.
+A.B.
+took the lead in writing the draft of the manuscript and C.D.
+edited the draft heavily.
+All authors discussed the results and commented on the manuscript.
+C.D.
+supervised the whole process.
+%exclude
+
 %\printbibliography %for use with biblatex; comment out if you use natbib
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+<<UngramResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=
 
-{\centering \includegraphics[width=\maxwidth]{figure/UngramResponseModel-1}
+suppressWarnings({
+p_m_ungram_response
+})
 
-}
-
-\end{knitrout}
+@
 
@@
 
-\begin{table}
+<<echo=FALSE, warning=FALSE, message=FALSE>>=
+library(knitr)
+dat <- tables$results_table_ungram_responses
+options(knitr.table.format = "latex")
+@
 
-\caption{\label{tab:unnamed-chunk-3}Point estimate, estimate error, and credible interval for Regression coefficients}
-\centering
-\begin{tabular}[t]{lrrrr}
-\toprule
-  & Estimate & Est.Error & Q2.5 & Q97.5\\
-\midrule
-Intercept & -1.2216372 & 0.0897748 & -1.3990933 & -1.0491069\\
-cEndsInConsonant & 0.0740791 & 0.1739013 & -0.2713538 & 0.4199774\\
-cAttractorPlural & 0.4594237 & 0.0995349 & 0.2560289 & 0.6526212\\
-cEndsInConsonant:cAttractorPlural & 0.0077682 & 0.1629159 & -0.3157023 & 0.3250568\\
-\bottomrule
-\end{tabular}
-\end{table}
+<<results='asis', echo=FALSE, warning=FALSE, message=FALSE>>=
+kable(dat, booktabs=TRUE, caption="Point estimate, estimate error, and credible interval for Regression coefficients")
+@
 

### 2021-07-06 paper/glossa/glossa-template-knitr.tex
anonimized links

--- 2021-07-06 paper/glossa/glossa-template-knitr-wordcount.tex
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: 2,749}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: 2,759}
 % Optional short title inside square brackets, for the running headers.
@@
 For our models, we run 4 chains, each of which consists of 1000 warm-up iterations and 1000 sampling iterations.
-Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.
+Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/tr_short_agreement_attraction/}.
 

### 2021-07-06 paper/glossa/glossa-template.Rnw
anonimized links

--- 2021-07-06 paper/glossa/glossa-template-knitr.Rnw
@@
 
-<<include=FALSE>>=
-library(knitr)
-opts_chunk$set(
-concordance=TRUE
-)
-@
+\SweaveOpts{concordance=TRUE}
 
@@
 
-<<AverageResponses, echo=FALSE, fig.align='center', fig.height=3, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=
+<<AverageResponses, echo=FALSE, fig.align='center', height=3, dev=cairo_pdf, png=TRUE, dpi = 300, message=FALSE>>=
 
@@
 
-<<ResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=
+<<ResponseModel,  echo=FALSE, fig.align='center', height=3, warning=FALSE, dev = cairo_pdf, png=TRUE, dpi = 300, message=FALSE>>=
 
@@
 
-<<UngramResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dev='png', dpi = 300, message=FALSE>>=
+<<UngramResponseModel,  echo=FALSE, fig.align='center', height=3, warning=FALSE, dev = cairo_pdf, png=TRUE, dpi = 300, message=FALSE>>=
 

### 2021-07-14 paper/glossa/manuscript-knitr-wordcount.tex
anonimization first step

--- 2021-07-06 paper/glossa/glossa-template-knitr-wordcount.tex
@@
-% see http://info.semprag.org/basics for a full description of this template
-%\documentclass[linguex]{glossa}
-% DO NOT FORGET TO setwd("paper/glossa/") where the Rnw file is.
-\documentclass[brill,linguex]{glossa}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[apacite,linguex]{glossa}\usepackage[]{graphicx}\usepackage[]{color}
 % maxwidth is the original width if it is less than linewidth
@@
 
-% possible options: 
-% [times] for Times font (default if no option is chosen)
-% [cm] for Computer Modern font 
-% [lucida] for Lucida font (not freely available)
-% [brill] open type font, freely downloadable for non-commercial use from http://www.brill.com/about/brill-fonts; requires xetex
-% [charis] for CharisSIL font, freely downloadable from http://software.sil.org/charis/
-% for the Brill an CharisSIL fonts, you have to use the XeLatex typesetting engine (not pdfLatex)
-% for headings, tables, captions, etc., Fira Sans is used: https://www.fontsquirrel.com/fonts/fira-sans
-% [biblatex] for using biblatex (the default is natbib, do not load the natbib package in this file, it is loaded automatically via the document class glossa.cls)
-% [linguex] loads the linguex example package
-% !!
-a note on the use of linguex: in glossed examples, the third line of the example (the translation) needs to be prefixed with \glt.
-This is to allow a first line with the name of the language and the source of the example.
-See example (2) in the text for an illustration.
-% !! a note on the use of bibtex: for PhD dissertations to typeset correctly in the references list, the Address field needs to contain the city (for US cities in the format "Santa Cruz, CA")
-
-%\addbibresource{sample.bib} 
-% the above line is for use with biblatex
-% replace this by the name of your bib-file (extension .bib is required)
-% comment out if you use natbib/bibtex
-
-\let\B\relax %to resolve a conflict in the definition of these commands between xyling and xunicode (the latter called by fontspec, called by charis)
+\let\B\relax
 \let\T\relax
-\usepackage{xyling} %for trees; the use of xyling with the CharisSIL font produces poor results in the branches. This problem does not arise with the packages qtree or forest.
-\usepackage[linguistics]{forest} %for nice trees!
+\usepackage{xyling} 
+\usepackage[linguistics]{forest}
 
 % \pdf* commands provide metadata for the PDF output. ASCII characters only!
-\pdfauthor{A.B. \& C.D.}
+\pdfauthor{A.A and B.B}
 \pdftitle{Agreement Attraction in Turkish}
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish\\ \bigskip \large Word count: 2,749}
-% Optional short title inside square brackets, for the running headers.
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,100}
 
-\author[A.B. \& C.D.]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
+\newcommand{\firstauthor}{{A.A.}}
+\newcommand{\firstauthorshort}{{A.A.}}
+\newcommand{\secondauthor}{{B.B.}}
+\newcommand{\secondauthorshort}{{B.B.}}
+
+\author[\firstauthor \& \secondauthor]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
 {%as many authors as you like, each separated by \AND.
-  \spauthor{\texttt{Hidden Hidden (A.B.)}\\ 
+  \spauthor{\texttt{Hidden Hidden (\firstauthor)}\\ 
   \institute{\texttt{Hidden University}}\\
@@
   \AND
-  \spauthor{\texttt{Hidden Hidden (C.D.)}\\ 
+  \spauthor{\texttt{Hidden Hidden (\secondauthor)}\\ 
   \institute{\texttt{Hidden University}}\\
@@
 \begin{abstract}
-We report the results of two speeded acceptability judgment experiments in Turkish.
-We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing.
-Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.
+
+Previous studies have shown that speakers may find sentences violating subject-verb agreement grammatical when the sentence contains a feature-matching noun phrase. 
+%
+This so-called agreement attraction effect has also been found in genitive possessive structures such as \textit{'the teacher's brother'} in Turkish (Lago et al., 2019), which is in contrast with its absence in similar constructions in English (Nicol et al., 2016).
+This discrepancy has been hypothesized to be a result of the association between genitive case marking and subjecthood in Turkish, but not in English.
+%
+In the present research, we test an alternative explanation in which Turkish agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
+We hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
+To test this hypothesis, we conducted a speeded acceptability judgment experiment and our results suggest that case-ambiguity does not play a role in agreement attraction, and thus lends credibility to the claim that genitive noun phrases may function as attractors in Turkish due to the association between genitive case and subjecthood.
+
 \end{abstract}
@@
 For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the syntactically unrelated attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed \textit{key}.
-Previous  studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with the singular attractor.
+A number of previous  studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with a singular attractor.
 This phenomenon, known as \textit{agreement attraction} \citep{BockMiller:1991} has been attested in a number of languages, such as in Arabic \citep{TuckerEtAl:2015}, Armenian \citep{AvetisyanEtAl:2020}, German \citep{LagoFelser:2018}, Hindi \citep{BhatiaDillon:2020}, Serbian \citep{RisticEtAl:2016}, Slovak \citep{BadeckerKuminiak:2007}, Spanish \citep{LagoEtAl:2015}, and recently in Turkish \citep{LagoEtAl:2019}.
@@
 
-\citet{LagoEtAl:2019} demonstrated that genitive possessor (such as \textit{painters} in \textit{the painters' rival}) cause agreement attraction effects in Turkish.
-This finding appears to be at odds with \citeauthor{NicolEtAl:2016}'s (\citeyear{NicolEtAl:2016}) results, who failed to find a similar effect in English.
+\citet{LagoEtAl:2019} demonstrated that genitive possessors (such as \textit{painters} in \textit{the painters' rival}) cause agreement attraction effects in Turkish.
+However, this finding appears to be at odds with \citeauthor{NicolEtAl:2016}'s (\citeyear{NicolEtAl:2016}) results, who failed to find a similar effect in English.
 \citet{LagoEtAl:2019} hypothesize that Turkish possessor noun phrases, unlike their English counterparts, may function as agreement attractors because Turkish genitive NPs may function as subjects of non-finite clauses in Turkish \citep{GokselKerslake:2005,Kornfilt:2011}.
-As a result, genitive NP in Turkish, but not in English, may match the subjecthood feature which may be used for cue-based retrieval of a verb's subject \citep{LewisVasishth:2005, ArnettWagers:2017}.
+As a result, Turkish genitive NPs may match the subjecthood feature used in the cue-based retrieval of a verb's subject \citep{LewisVasishth:2005, ArnettWagers:2017}.
 
-In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of case syncretism in the experimental sentences in their experiment, which resulted in all subject head nouns being ambiguous between possessive and accusative case.
+In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of case syncretism in the experimental sentences in their experiment, as a result of which all subject head nouns were ambiguous between possessive and accusative case.
 
@@
 
-Turkish is an SOV word order language which uses case to mark arguments \citep{GokselKerslake:2005,Kornfilt:2011,Kornfilt:2013}.
-Case markers have different forms depending on whether or not the last sound is a vowel.
-In order to break vowel-vowel clusters, Turkish uses a variety of sounds as epenthetic consonants including \textit{s}, \textit{y}, or \textit{n}.
+Turkish is an SOV word order language with overt case marking \citep{GokselKerslake:2005,Kornfilt:2011,Kornfilt:2013}.
+For example, the possessor in the Turkish equivalent of the Saxon Genitive in \ref{ex:possgenex} is marked with genitive case, while the head noun is marked with possessive case.
+Importantly, the possessive case marker coincides in form with the accusative case marker when the noun stem ends in a consonant: 
+This is because in Turkish, case markers have different forms depending on whether the last sound of the stem is a vowel.
+In order to break up vowel-vowel clusters, Turkish uses epenthetic consonants such as \textit{s}, \textit{y}, or \textit{n}.
 For example, the genitive case can surface as \textit{-nin} or as \textit{-in}, depending on the last consonant of the stem.
-Importantly, the forms of the possessive marker and the accusative case are identical except for the epenthetic consonant.
+The forms of the possessive marker and the accusative case are identical except for the epenthetic consonant.
 This means that they surface as \textit{-i} in consonant-ending words, but as \textit{-si} and \textit{-yi} respectively in vowel-ending words.
 
-\citet{LagoEtAl:2019} present a speeded acceptability judgment study with sentences like \ref{ex:lago}, in which the number of the attractor and the verb was manipulated.
-The resulting 2x2 design indicated by slashes in \ref{ex:lago} consisted of two grammatical conditions, in which the verb agreed with the singular subject head noun, and two ungrammatical conditions, in which the verb carried plural agreement, and thus did not agree with the subject.
+\ex. \label{ex:possgenex}
+\gll teknisyen-in eğitmen-i \\
+    technician-\textsc{gen} instructor-\textsc{poss} \\
+\glt `the instructor of the technician'
+
+\citet{LagoEtAl:2019} demonstrated an agreement attraction effect in Turkish genitive-possessive constructions in a speeded acceptability judgment study with sentences like \ref{ex:lago}, in which the number of the attractor and the verb was manipulated.
+The resulting $2$x$2$ design, indicated by brackets and slashes in \ref{ex:lago}, consisted of two grammatical conditions, in which the verb agreed with the singular subject head noun, and two ungrammatical conditions, in which the verb carried plural agreement, and thus did not agree with the subject.
 In ungrammatical sentences, they found a higher percentage of \textit{acceptable} responses when the genitive attractor was plural than when it was singular, indicating agreement attraction.
@@
 \ex. \label{ex:lago}
-\gll Ressam-lar/\O-(n){\i}n rakib-i at\"{o}lye-den h{\i}zla uzakla\c{s}-t{\i}-lar/\O.\\
-painter-\textsc{pl}/\textsc{sg}-\textsc{gen} rival-\textsc{poss} workshop-\textsc{abl} quickly walked.away-\textsc{pst}-\textsc{pl}/\textsc{sg}\\
-\glt `The painter's/painters' rival walked away from the workshop quickly.'
+\gll Teknisyen-\{ler/\O\}-in e\u{g}itmen-i ola\u{g}an{\"u}st{\"u} h{\i}zl{\i} ko\c{s}-tu-\{lar/\O\}.\\
+technician-\{\textsc{pl}/\textsc{sg}\}-\textsc{gen} instructor-\textsc{poss} extraordinarily fast run-\textsc{pst}-\{\textsc{pl}/\textsc{sg}\}\\
+\glt `The technician's/technicians' instructor extraordinarily fast ran\{\textsc{pl}/\textsc{sg}\}.'
 
-\citet{LagoEtAl:2019} hypothesized that these effects originated from how case and number information is encoded and retrieved.
-According to \citeauthor{LewisVasishth:2005}'s (\citeyear{LewisVasishth:2005}) cue-based retrieval model, phrases are encoded in a content-addressable memory as bundles of features called \textit{chunks} which include information like number, gender, case, and syntactic function \citep{SmithVasishth:2020}.
-Under \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) proposal, participants predict the number of the verb based on the chunks they formed while reading the subject.
+\citet{LagoEtAl:2019} hypothesized that these effects originated from how case and number information is encoded and retrieved: According to \citeauthor{LewisVasishth:2005}'s (\citeyear{LewisVasishth:2005}) cue-based retrieval model, phrases are encoded in a content-addressable memory as bundles of features called \textit{chunks} which include information like number, gender, case, and syntactic function \citep[e.g.,][]{SmithVasishth:2020}.
+Under \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) proposal, participants predict the number of the verb based on the noun phrases they process while reading the subject.
 In grammatical sentences with singular verb agreement, the number prediction and the verb number match, which causes no processing difficulty.
@@
 This process activates the search for a chunk matching two cues: the subjecthood feature ([+SUBJECT]) and the plural feature ([+PL]).
-While neither of the available noun phrases matches this specification in ungrammatical agreement attraction sentences, each of the NPs headed by \textit{painter} and \textit{rival} matches one of these cues.
-While this partial match mostly results in participants finding the sentence ungrammatical, they may retrieve the attractor \textit{painters} on some trials.
-\citet{LagoEtAl:2019} argue that this erroneous retrieval may be facilitated by the fact that genitive case marking on the attractor because genitive NPs can function as subjects of embedded clauses in Turkish.
-Due to the ubiquity of genitive subjects, attractors marked with genitive case were hypothesized to be a priori more likely agreement controllers.
+While neither of the available noun phrases matches this specification in ungrammatical agreement attraction sentences, each of the NPs headed by \textit{technician} and \textit{instructor} matches one of these cues.
+While this partial match mostly results in participants finding the sentence ungrammatical, they may retrieve the attractor \textit{technicians} on some trials.
+\citet{LagoEtAl:2019} argue that this erroneous retrieval may be facilitated by the genitive case marking on the attractor, because genitive NPs can function as subjects of embedded clauses in Turkish.
+Due to the ubiquity of genitive subjects, attractors marked with genitive case a priori likely to be agreement controllers.
 
-A potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that all head nouns such as \textit{rival} in \ref{ex:lago} were consonant-ending and therefore locally ambiguous between possessive and accusative case \citep[66--67]{GokselKerslake:2005}.
-Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the head nouns' reduced association with subjecthood due case syncretism.
+However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{eğitmen-i} (\textit{'instructor'}) in \ref{ex:lago} were consonant-ending, which made them locally ambiguous between possessive and accusative case \citep[pp.
+66--67]{GokselKerslake:2005} because the surface form of both, the possessive and accusative case is \textit{-i}.
+%
+Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due case syncretism between possessive and accusative.
 We tested this hypothesis in a speeded-acceptability experiment with sentences similar to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}), but with unambiguously marked vowel-ending head nouns.
@@
 
-The present study tested predictions of the syncretism between possessive and accusative cases as an alternative explanation of the previously found agreement attraction effect in Turkish.
-We disambiguated between them by using vowel-ending nouns instead of consonant-ending head nouns as done in \citet{LagoEtAl:2019}.
-When attached to a vowel-ending noun, the possessive is realized as using \textit{-ni}, while the accusative maker would surface as \textit{-yi}.
-We hypothesized that if the morpho-phonological ambiguity was a key factor in agreement attraction in Turkish, resolving it should diminish the attraction effects.
+The present study tested the predictions of the case syncretism account as an alternative explanation of the previously found agreement attraction effect in Turkish.
+To avoid the ambiguity present in \citet{LagoEtAl:2019}, we used vowel-ending head nouns nouns such as \textit{terzi} (\textit{'tailor'}), for which the possessive marker surfaces as \textit{-si} and is distinct from the accusative (\textit{-yi}).
+We hypothesized that if the morpho-phonological ambiguity was a key factor in agreement attraction in Turkish, unambiguous sentences like ours in \ref{ex:our_items} should not elicit attraction effects.
+
+\ex. \label{ex:our_items}
+  \a. * Plural Attractor, Ungrammatical (Plural Verb) \label{ex:expitem-plpl}\\
+  \gll [Milyoner-ler-in \textbf{terzi-si}] tamamen gereksizce \textbf{kov-ul-du-lar}.\\
+  millionaire-\textsc{pl}-\textsc{gen} tailor-\textsc{poss} completely without.reason fire-\textsc{pass}-\textsc{pst}-\textsc{pl}\\
+  \glt `The millionaires' tailor were fired for no reason at all.'
+  \b. Plural Attractor, Grammatical (Singular Verb) \label{ex:expitem-plsg} \\
+  \gll [Milyoner-ler-in \textbf{terzi-si}] tamamen gereksizce \textbf{kov-ul-du}.\\
+  millionaire-\textsc{pl}-\textsc{gen} tailor-\textsc{poss} completely without.reason fire-\textsc{pass}-\textsc{pst}\\
+  \glt `The millionaires' tailor was fired for no reason at all.'
+  \b. * Singular Attractor, Ungrammatical (Plural Verb) \label{ex:expitem-sgpl}\\
+  \gll [Milyoner-in \textbf{terzi-si}] tamamen gereksizce \textbf{kov-ul-du-lar}.\\
+  millionaire-\textsc{gen} tailor-\textsc{poss} completely without.reason fire-\textsc{pass}-\textsc{pst}-\textsc{pl}\\
+  \glt `The millionaire's tailor were fired for no reason at all.'
+  \b. Singular Attractor Grammatical (Singular Verb) \label{ex:expitem-sgsg}\\
+  \gll [Milyoner-in \textbf{terzi-si}] tamamen gereksizce \textbf{kov-ul-du}.\\
+  millionaire-\textsc{gen} tailor-\textsc{poss} completely without.reason fire-\textsc{pass}-\textsc{pst}\\
+  \glt `The millionaire's tailor was fired for no reason at all.'
 
@@
 
-\subsection{Materials}
-
 We used 40 sets of sentences like \ref{ex:our_items}, in which we manipulated (i) the number of the attractor noun and (ii) the number agreement on the verb.
@@
 
-All sentences started with a complex subject NP like \textit{y\"{o}neticinin a\c{s}\c{c}{\i}s{\i}} `\textit{the manager's cook},' in which the genitive possessor functioned as the attractor, and the head noun carried an unambiguous possessive case marker.
+All sentences started with a complex subject NP like \textit{milyonerlerin terzisi} `\textit{the millionaires' tailor},' in which the genitive possessor functioned as the attractor, and the head noun carried an unambiguous possessive case marker.
 Because the plural marking on nominals is not optional and the head noun was singular, absent of \textit{-lar}, in all conditions, sentences with plural verb agreement were ungrammatical.
-Moreover, the relationship between the possessor and the head noun was controlled as in \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) original study and can be paraphrased using \textit{'s} or \textit{of} in English.
+Moreover, the semantic relationship between the possessor and the head noun was kept as it is in \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) original study and genitive-possessive structures can be paraphrased using \textit{'s} or \textit{of} in English.
 The distribution of the verb types matched that of the original study, with twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs.
@@
 
-\ex. \label{ex:our_items}
-  \a. * Plural Attractor, Ungrammatical (Plural Verb) \label{ex:expitem-plpl}\\
-  \gll [Y\"{o}netici-ler-in \textbf{a\c{s}\c{c}{\i}-s{\i}}] mutfak-ta s\"{u}rekli \textbf{z{\i}pla-d{\i}-lar}\\ 
-  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
-  \glt `The cooks of the manager jumped\textsubscript{\textsc{pl}} in the kitchen non-stop.'
-  \b. Plural Attractor, Grammatical (Singular Verb) \label{ex:expitem-plsg} \\
-  \gll [Y\"{o}netici-ler-in \textbf{a\c{s}\c{c}{\i}-s{\i}}] mutfak-ta s\"{u}rekli \textbf{z{\i}pla-d{\i}}\\ 
-  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
-  \glt `The cooks of the manager jumped\textsubscript{\textsc{sg}} in the kitchen non-stop.'
-  \b. * Singular Attractor, Ungrammatical (Plural Verb) \label{ex:expitem-sgpl}\\
-  \gll [Y\"{o}netici-nin \textbf{a\c{s}\c{c}{\i}-s{\i}}] mutfak-ta s\"{u}rekli \textbf{z{\i}pla-d{\i}-lar}.\\ 
-  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}\\
-  \glt `The cook of the manager jumped\textsubscript{\textsc{pl}} in the kitchen non-stop.'
-  \b. Singular Attractor, Grammatical (Singular Verb) \label{ex:expitem-sgsg}\\
-  \gll [Y\"{o}netici-nin \textbf{a\c{s}\c{c}{\i}-s{\i}}] mutfak-ta s\"{u}rekli \textbf{z{\i}pla-d{\i}}. \\ 
-  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}\\
-  \glt `The cook of the manager jumped\textsubscript{\textsc{sg}} in the kitchen non-stop.'
-
 We hypothesized that the experimental sentences in \ref{ex:our_items} might elicit a simple response strategy based on verb number because all ungrammatical sentences end with a plural-agreement-bearing verb.
-In contrast, all grammatical sentences end with a verb that lacks a plural agreement, thus singular.
+In contrast, all grammatical sentences end with a verb that lacks plural agreement, thus singular.
 As a result, some participants may resort to classifying sentence acceptability based on their last word after repeated exposure to sentences like \ref{ex:our_items}.
@@
 Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentation of the sentence in the center of the screen, followed by a prompt to indicate their acceptability judgment.
-Sentences were presented word-by-word in the center for the screen in 30 pt font size, at a rate of 400 ms per word.
+Sentences were presented word-by-word in the center of the screen in 30 pt font size, at a rate of 400 ms per word.
 Participants saw a blank screen for 100 ms between each word, and to see the next item, they needed to press the \texttt{space} key.
@@
 Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between the grammatical condition \ref{ex:expitem-sgsg} and the ungrammatical condition \ref{ex:expitem-sgpl} fell below the threshold of 0.25 percentage points.
-We also excluded trials in which the participants missed the response deadline or gave too fast responses (below 200 ms).
+We also excluded trials in which the participants missed the response deadline or gave overly fast responses (below 200 ms).
 As a result, we excluded 10.22\% of the trials from our experiment and 2.38\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.
 
-We analyzed responses using a Bayesian GLM assuming a Bernoulli-distributed response with a probit link function.
+We analyzed responses using two Bayesian GLMs assuming a Bernoulli-distributed response with a probit link function.
 We used the R packages brms \citep{brms} and rstan \citep{rstan} to fit Bayesian hierarchical models \citep[e.g.,][]{GelmanHill:2007, NicenboimVasishth:2016}.
@@
 We used by-participant and by-item intercepts and slopes for all predictors.
-All factors were sum-coded.
-We have used standard priors provided by the brms package.
+All factors were sum-coded. We have used standard priors provided by the brms package.
 
-In the results section, we provide posterior distributions for parameters given our data and model with 95\% credible intervals.
-For our models, we run 4 chains, each of which consists of 1000 warm-up iterations and 1000 sampling iterations.
-Data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.
+Because the magnitude of the agreement attraction effect can operationalized either as the interaction between grammaticality and the presence of a plural attractor, or as the effect of a plural attractor in ungrammatical sentences, we used a second model with predictors (ii) and (iii) and their interaction to analyze responses to ungrammatical conditions only.
+
+In the results section, we provide summaries of the coefficient posterior distributions.
+For our model, we ran 4 chains with 1000 warm-up iterations and 1000 sampling iterations.
+The data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.
 
@@
 
-Figure \ref{fig:AverageResponses} shows the average proportions of `acceptable' responses by experimental condition for both the original experiment in \citet{LagoEtAl:2019} and our replication with unambiguous possessive marking.
+Figure \ref{fig:AverageResponses} shows the average proportions of `acceptable' responses by experimental condition in our experiment with unambiguous possessive marking, side by side with Lago et al.'s findings.
 It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = 0.22, SE = 0.01) than their counterparts with singular attractors (M = 0.11, SE=0.01).
-The magnitude of the effect (0.11) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was 0.11.
+The magnitude of the effect (0.11) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was also 0.11.
 Accuracy rates for grammatical conditions were nearly equal (M = 0.93 and 0.92, SE = 0.01 and 0.01, for singular and plural attractors respectively).
@@
 \caption{The average percentage of acceptable responses according to the experimental conditions in our study and \citet{LagoEtAl:2019}.
-Error bars signal standard errors calculated following \citet{Cousineau:2007}.}
+Error bars signal standard errors calculated following \citet{Morey:2008,Cousineau:2005}.}
 \label{fig:AverageResponses}
@@
 The main effect of grammaticality ($\hat{\beta}=3.08;$ $CI=[2.84; 3.33];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.04; -0.42];$ $P(\beta<0)> .999$) indicated a more prominent effect of attractor number in ungrammatical conditions, and thus a number agreement attraction effect.
-There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.27;$ $CI=[-0.77; 0.25];$ $P(\beta<0)=    .85$).
+Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.04; -0.42];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
+There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.27;$ $CI=[-0.77; 0.25];$ $P(\beta<0)=    .85$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments ().
+This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor (($\hat{\beta}=0.01;$ $CI=[-0.32; 0.33];$ $P(\beta<0)=    .48$).
+It also showed a main effect of plural attractor ($\hat{\beta}=0.46;$ $CI=[0.26; 0.65];$ $P(\beta<0)< .001$).
+Taken together, the coefficients indicated a substantial agreement attraction effect regardless of the presence of local ambiguity.
 
@@
 
-\caption{Estimates and 95\% credible intervals for the regression coefficients for the model of our experiment and \citet{LagoEtAl:2019}.}
+\caption{Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses in our experiment and \citet{LagoEtAl:2019}.}
 \label{fig:ResponseModel}
 \end{figure}
-
-\section{Discussion \& Conclusion}
-
-In this paper, we re-examined the findings of \citet{LagoEtAl:2019} and investigated the effect of local case ambiguity on Turkish agreement attraction using genitive-possessive constructions in a speeded acceptability judgment experiment.
-The main question we asked was whether \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings can be explained with an alternative hypothesis.
-In their work, there was a possible confound in the experimental items.
-All head nouns were locally ambiguous between the possessive and the accusative case.
-We hypothesized that participants may encode the head-noun as marked with the accusative case (a non-subject case in Turkish), and thus, the retrieval of the head subject may be hindered in some trials.
-If Turkish agreement attraction effects resulted from this ambiguity, we should not observe any effect of plural attractor in ungrammatical sentences when the case of the head noun is disambiguated.
-
-Our experimental findings were comparable with \citet{LagoEtAl:2019} and previous agreement attraction studies.
-We observed that the existence of a plural attractor increased the overall error rates the participants did, and this effect was amplified even more in ungrammatical sentences.
-As for the effects of case ambiguity, the findings did not support our hypothesis.
-The findings were not conclusive on whether or not ambiguity played a role.
-Participants still retrieved plural attractors in ungrammatical sentences more than they did with singular attractors.
-
-Our model, where we incorporate data from both our experiment and \citet{LagoEtAl:2019}, did not show a three-way interaction between Ambiguity, Grammaticality, and Plural Attractor.
-This means that when the possessive marker is disambiguated agreement attraction (the interaction between Grammaticality and Plural Attractor) does not diminish in effect size.
-Considering the posterior distributions, we interpreted these results as pointing towards a piece of inconclusive evidence for the effect of ambiguity in agreement attraction effects.
-As a result, we successfully replicated the findings of \citet{LagoEtAl:2019} with disambiguated head nouns.
-
-Taken together, these results suggest (i) that Turkish agreement attraction effects are not due to a possible erroneous encoding of the possessive marker, and (ii) that local ambiguities in case, syncretism, do not play a role in agreement attraction.
-Participants do not rely on form-related cues in decision-making processes.
-These findings support an agreement attraction theory that makes use of abstract linguistic features.
-
-%\printbibliography %for use with biblatex; comment out if you use natbib
-\bibliography{gp_short} %for use with natbib; comment out if you use biblatex, and change 'sample' by the name of your bib-file
-
-\section*{Appendix A: Ungrammatical Sentences Model}
 
@@
 
-{\centering \includegraphics[width=\maxwidth]{figure/UngramResponseModel-1}
+{\centering \includegraphics[width=\maxwidth]{figure/ResponseModelUngram-1}
 
@@
 
-\caption{Estimates and 95\% credible intervals for the regression coefficients for the model of our experiment and \citet{LagoEtAl:2019}. In this model, only the ungrammatical sentences are included}
-\label{fig:UngramResponseModel}
+\caption{Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses to \protect{\textbf{ungrammatical sentences}} in our experiment and \citet{LagoEtAl:2019}.}
+\label{fig:ResponseModelUngram}
 \end{figure}
 
-\begin{table}
+\section{Discussion \& Conclusion}
 
-\caption{\label{tab:unnamed-chunk-3}Point estimate, estimate error, and credible interval for Regression coefficients}
-\centering
-\begin{tabular}[t]{lrrrr}
-\toprule
-  & Estimate & Est.Error & Q2.5 & Q97.5\\
-\midrule
-Intercept & -1.2216372 & 0.0897748 & -1.3990933 & -1.0491069\\
-cEndsInConsonant & 0.0740791 & 0.1739013 & -0.2713538 & 0.4199774\\
-cAttractorPlural & 0.4594237 & 0.0995349 & 0.2560289 & 0.6526212\\
-cEndsInConsonant:cAttractorPlural & 0.0077682 & 0.1629159 & -0.3157023 & 0.3250568\\
-\bottomrule
-\end{tabular}
-\end{table}
+We re-examined the findings of \citet{LagoEtAl:2019} and investigated the contributution of a possible confound to their finding of an agreement attraction effect in genitive-possessive constructions in Turkish.
+Our main question was whether \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings can be explained by an alternative hypothesis:
+Because in their experimental sentences, all head nouns were locally ambiguous between the possessive and the accusative case (a non-subject case in Turkish), we hypothesized that this may have weakened the strength of association between the subject head noun and the subjecthood feature.
+If Turkish agreement attraction effects in genitive-possessive structures resulted from this ambiguity, we expected the absence of agreement attraction effects when the case of the head noun was unambiguous.
+
+Our experimental findings were comparable to \citet{LagoEtAl:2019}: We observed that the presence of a plural attractor increased the rate of erroneous `acceptable' responses  
+% increased the overall error rate
+in ungrammatical sentences.
+Importantly, we did not find an effect of case ambiguity: While our model based on all experimental conditions indicated a weak three-way interaction between ambiguity, grammaticality, and attractor number, a model based on ungrammatical sentences only demonstrated that this is due to a difference in acceptability rates in grammatical conditions.
+This model showed no evidence of an interaction between attractor number and ambiguity, indicating no evidence of a modulation of the effect size of the agreement attraction effect by the presence of a local case ambiguity.
+Although the $95\%$ credible interval for the interaction term was relatively wide, our findings indicate the presence of a substantial agreement attraction effect regardless of the presence of local ambiguity.
+Thus, we successfully replicated the findings of \citet{LagoEtAl:2019} with disambiguated head nouns.
+
+{\firstauthor} conceived the initial version of the presented idea. Both authors designed the the experiment together. 
+{\firstauthor} wrote the stimuli and conducted the experiment.
+The statistical analysis was carried out by {\secondauthor}; {\firstauthor} prepared all summaries and plots.
+{\firstauthor} wrote the first draft of the manuscript and both authors edited it subsequently.
+
+%\printbibliography %for use with biblatex; comment out if you use natbib
+%\bibliography{gp_short} %for use with natbib; comment out if you use biblatex, and change 'sample' by the name of your bib-file
+\bibliographystyle{apacite}
+\bibliography{gp_short.bib}
 

### 2021-07-14 paper/glossa/manuscript-knitr.Rnw
anonimization first step

--- 2021-07-14 paper/glossa/manuscript-knitr-wordcount.tex
@@
-\documentclass[apacite,linguex]{glossa}\usepackage[]{graphicx}\usepackage[]{color}
-% maxwidth is the original width if it is less than linewidth
-% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
+\documentclass[apacite,linguex]{glossa}
 
@@
 
+<<wordcount, echo=FALSE, cache=FALSE>>=
+library(knitr)
+
+comma <- function (x, ...) {
+  format(x, ..., big.mark = ",", scientific = FALSE, trim = TRUE)
+}
+
+# To dynamically extract name of the current file, use code below
+nameoffile <- 'manuscript-knitr.Rnw' # get name of file
+nof2 <-  strsplit(nameoffile,"\\.")[[1]][1] # extract name, drop extension
+noftex <- paste(nof2, ".tex", sep="") # add .tex extension
+nofwordcount <-  paste(nof2, '-','wordcount', '.tex', sep = "") # prepare a tex file for word count
+if (file.exists(nofwordcount)) {unlink(nofwordcount)} #delete the previous file.
+
+con <- file(noftex, open = 'r') # open the file with R
+while(TRUE) {
+  line <- readLines(con, n = 1) # read lines
+  if(length(line) == 0) break # pass if nothing is there
+  else if(!endsWith(line, "%exclude")){ # if the line does not end with %exclude 
+    write(line, file = nofwordcount, append = TRUE) # write it to the new file
+  } 
+}
+close(con)
+
+systemcall <- paste("system('texcount -inc -incbib -total -sum ", nofwordcount, "', intern=TRUE)", sep="") # paste together texcount system command
+texcount.out <- eval(parse(text=systemcall)) # run texcount on current last compiled .tex file with edits
+
+sum.row <- grep("Sum count", texcount.out, value=TRUE) # extract row
+pattern <- "(\\d)+" # regex pattern for digits
+
+count <- regmatches(sum.row, regexpr(pattern, sum.row) )
+# extract digits
+
+count <- comma(as.numeric(count)) # add comma
+
+@
+
 % \pdf* commands provide metadata for the PDF output. ASCII characters only!
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,100}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: \Sexpr{count}}
 
@@
 In the results section, we provide summaries of the coefficient posterior distributions.
-For our model, we ran 4 chains with 1000 warm-up iterations and 1000 sampling iterations.
+For our model, we ran \Sexpr{n_chains} chains with \Sexpr{n_warmup} warm-up iterations and \Sexpr{n_iter-n_warmup} sampling iterations.
 The data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.
@@
 Figure \ref{fig:AverageResponses} shows the average proportions of `acceptable' responses by experimental condition in our experiment with unambiguous possessive marking, side by side with Lago et al.'s findings.
-It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = 0.22, SE = 0.01) than their counterparts with singular attractors (M = 0.11, SE=0.01).
-The magnitude of the effect (0.11) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was also 0.11.
-Accuracy rates for grammatical conditions were nearly equal (M = 0.93 and 0.92, SE = 0.01 and 0.01, for singular and plural attractors respectively).
+It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = \Sexpr{exp1_cur_entry1$M}, SE = \Sexpr{exp1_cur_entry1$SE}) than their counterparts with singular attractors (M = \Sexpr{exp1_cur_entry2$M}, SE=\Sexpr{exp1_cur_entry2$SE}).
+The magnitude of the effect (\Sexpr{m_effect}) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was also 0.11.
+Accuracy rates for grammatical conditions were nearly equal (M = \Sexpr{exp1_cur_entry3$M} and \Sexpr{exp1_cur_entry4$M}, SE = \Sexpr{exp1_cur_entry3$SE} and \Sexpr{exp1_cur_entry4$SE}, for singular and plural attractors respectively).
 
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+<<AverageResponses, echo=FALSE, fig.align='center', fig.height=3, dev='cairo_pdf', dpi = 300, message=FALSE>>=
 
-{\centering \includegraphics[width=\maxwidth]{figure/AverageResponses-1}
+plot(p_avg_resp)
 
-}
-
-\end{knitrout}
+@
 
@@
 Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function.
-The main effect of grammaticality ($\hat{\beta}=3.08;$ $CI=[2.84; 3.33];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.04; -0.42];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
-There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.27;$ $CI=[-0.77; 0.25];$ $P(\beta<0)=    .85$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments ().
-This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor (($\hat{\beta}=0.01;$ $CI=[-0.32; 0.33];$ $P(\beta<0)=    .48$).
-It also showed a main effect of plural attractor ($\hat{\beta}=0.46;$ $CI=[0.26; 0.65];$ $P(\beta<0)< .001$).
+The main effect of grammaticality (\Sexpr{estimate_cGrammatical}) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the negative interaction between grammaticality and attractor number (\Sexpr{estimate_cGrammatical_cAttractorPlural}) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
+There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number (\Sexpr{estimate_threeway_interaction}), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments (\Sexpr{m_effect_lago}).
+This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor ((\Sexpr{estimate_ungramResp_cAmbiguity_cAttractorPlural}).
+It also showed a main effect of plural attractor (\Sexpr{estimate_ungramResp_cAttractorPlural}).
 Taken together, the coefficients indicated a substantial agreement attraction effect regardless of the presence of local ambiguity.
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+<<ResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dpi = 300, message=FALSE>>=
 
-{\centering \includegraphics[width=\maxwidth]{figure/ResponseModel-1}
+suppressWarnings({
+p_m_response
+})
 
-}
-
-\end{knitrout}
+@
 
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+<<ResponseModelUngram,  echo=FALSE, fig.align='center', fig.height=1.5, warning=FALSE, dev='cairo_pdf', dpi = 300, message=FALSE>>=
 
-{\centering \includegraphics[width=\maxwidth]{figure/ResponseModelUngram-1}
+suppressWarnings({
+p_m_ungram_response
+})
 
-}
-
-\end{knitrout}
+@
 
@@
 
+\section*{Abbreviations} %exclude
+
+\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{nmlz} = nominalizer, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular.
+%exclude
+
+\section*{Data Availability} %exclude
+
+The data that support the findings of this study, the code, and the paper resources including \LaTeX{} and \texttt{Sweave} files are openly available in the anonimized github page at \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.
+%exclude
+
+\section*{Authors' Contributions} %exclude
+
 {\firstauthor} conceived the initial version of the presented idea. Both authors designed the the experiment together. 

### 2021-07-14 paper/glossa/manuscript-knitr.tex
anonimization first step

--- 2021-07-14 paper/glossa/manuscript-knitr-wordcount.tex
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,100}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,070}
 

### 2021-07-14 paper/glossa/manuscript.Rnw
anonimization first step

--- 2021-07-14 paper/glossa/manuscript-knitr.Rnw
@@
 
-<<AverageResponses, echo=FALSE, fig.align='center', fig.height=3, dev='cairo_pdf', dpi = 300, message=FALSE>>=
+<<AverageResponses, echo=FALSE, fig.align='center', height=3, dev = cairo_pdf, dpi = 300, message=FALSE>>=
 
@@
 
-<<ResponseModel,  echo=FALSE, fig.align='center', fig.height=3, warning=FALSE, dev='cairo_pdf', dpi = 300, message=FALSE>>=
+<<ResponseModel,  echo=FALSE, fig.align='center', height=3, warning=FALSE, dev = cairo_pdf, dpi = 300, message=FALSE>>=
 
@@
 
-<<ResponseModelUngram,  echo=FALSE, fig.align='center', fig.height=1.5, warning=FALSE, dev='cairo_pdf', dpi = 300, message=FALSE>>=
+<<ResponseModelUngram,  echo=FALSE, fig.align='center', height=1.5, warning=FALSE, dev = cairo_pdf, dpi = 300, message=FALSE>>=
 

### 2021-07-14 R/analysis/01_data_wrangling.R

@@ -4,15 +4,6 @@ data_exp1 <- readRDS(fname_data)
 fname_form <- "./data/exp_form.rds"
 form_exp1 <- readRDS(file = fname_form)
 
-### note: the low accuracy on fillers is not caused by a couple of items
-###       -> see below
-# filler_avgs <- 
-# data_exp1 %>% subset(Type == "filler") %>% group_by(Item, condition) %>% 
-#               summarize(M = mean(ResponseYes, na.rm = T)) %>%
-#               arrange(condition, Item)
-# fillers %>% subset(condition == "a") 
-# fillers %>% subset(condition == "b")
-###
 
 # compute by-subject percentages of 'yes' responses, and average RTs 
 avg_by_subj <- data_exp1 %>%
@@ -37,10 +28,6 @@ df_lagoetal <- read.csv(fname_lagoetal, encoding = "UTF-8", as.is = T)
 df_lagoetal %<>% subset(Group == "monolingual")
 df_lagoetal %<>% dplyr::select(-Accuracy, -L1:-Group, -List:-SelfRateGerman)
 
-# Note: All rows with Experiment == "offline" also seem to be for 
-#       the UNP task ('Grammatical' is NA). I wonder if these were
-#       the same subjects, or if the subject labels were simply the same
-#       for the two experiments.
 with(df_lagoetal, stopifnot( is.na(Grammatical) == (Experiment == "offline") ))
 
 df_lagoetal_unp <- df_lagoetal %>% 
@@ -126,5 +113,5 @@ df_merge_lago <- df_lagoetal_attr_clean %>%
                       ungroup() %>% 
                       dplyr::select(grammatical, attractor_num,
                                     subject, item, ResponseYes, RT)
-df_merge_lago$experiment <- "Lago et al. (2018)" 
+df_merge_lago$experiment <- "Lago et al. (2019)" 
 df_merge_lago$source <- NA

### 2021-07-14 R/analysis/02_word_freq.R

@@ -13,8 +13,7 @@ word_freq %<>% dplyr::group_by(exp) %>%
                               freqlog_n1n2 = log(n1) - log(n2)
                             ) %>% 
                 ungroup()
-# word_freq$freq_cat_n1 %<>% as.factor()
-# word_freq$freq_cat_n2 %<>% as.factor()
+
 
 
 word_freq_exp1 <- word_freq %>% subset(exp == "exp1") %>% dplyr::select(-exp)

### 2021-07-14 R/analysis/03_descriptive_plots.R

@@ -4,11 +4,6 @@ df_merged %<>% subset( !is.na(ResponseYes) )
 df_merged %<>% mutate(ResponseCorrect = (ResponseYes == (grammatical == "grammatical") ) )
 df_merged_nonna <- df_merged %>% subset(!is.na(ResponseYes))
 
-# avg_clean <- 
-# df_merged %>% subset(experiment == "Lago et al. (2018)") %>%
-#      group_by(experiment, source, grammatical, attractor_num, subject) %>%
-#      summarize(p_yes = mean(ResponseYes, na.rm=T)) %>%
-#      summarize(p_yes = mean(p_yes))
 
 avg_clean <- list()
 avg_clean$resp <- df_merged_nonna %>% 
@@ -43,18 +38,17 @@ p_avg_resp <- avg_exp$resp %>%
               ggplot(aes(grammatical_plot, M, #linetype = attractor_num, 
                          color = attractor_num, group = attractor_num)) + 
                 geom_point(position = pd) + geom_line(position = pd) + 
-                facet_wrap(~experiment)
+                facet_wrap(~experiment) + 
+  theme_bw(base_family = 'Fira Sans')+
+  theme(strip.background =element_rect(fill="white"))+
+  theme(strip.text = element_text(colour = 'black'))
 
 p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)
 
-# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
-#                             geom_point(data = avg_fillers) + 
 
-p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
-                           theme_bw(base_family = "Fira Sans") + xlab("") + ylab("Percentage 'acceptable'")
 p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
-p_avg_resp <- p_avg_resp + theme_bw(base_family = "Fira Sans")
 p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
+p_avg_resp <- p_avg_resp + xlab("") + ylab("Percentage 'acceptable'")
 
 avg_exp_resp_exp1 <- avg_exp$resp %>% subset(experiment == "Experiment 1")
[…]

### 2021-07-14 R/analysis/04_bayesian_models.R

@@ -11,12 +11,6 @@ df_merged %<>% within(., {
 })
 df_merged_nofillers <- df_merged %>% subset(is.na(source) | source != "filler")
 
-# ## test model parameterization using a simple GLM first
-# m <- glm(ResponseYes ~ (cFreqlog_n1 + cFreqlog_n2) *
-#            cEndsInConsonant * cUngrammatical * cAttractorPlural,
-#          data = df_merged_nofillers,
-#          family = binomial("probit"))
-# summary(m)
 
 models <- c()
 

### 2021-07-14 R/analysis/06_text_inputs.R

@@ -29,3 +29,6 @@ m_effect_lago <- sprintf("%0.2f", lago_cur_entry1$M-lago_cur_entry2$M)
 estimate_cGrammatical <- print_estimate_with_ci( m_responses, 'cGrammatical' )
 estimate_cGrammatical_cAttractorPlural <- print_estimate_with_ci( m_responses, 'cGrammatical:cAttractorPlural')
 estimate_threeway_interaction <- print_estimate_with_ci( m_responses, 'cEndsInConsonant:cGrammatical:cAttractorPlural')
+
+estimate_ungramResp_cAmbiguity_cAttractorPlural <- print_estimate_with_ci(m_ungram_responses, 'cEndsInConsonant:cAttractorPlural')
+estimate_ungramResp_cAttractorPlural <- print_estimate_with_ci(m_ungram_responses, 'cAttractorPlural')

### 2021-07-14 R/scripts/00.2-eda.R

@@ -16,8 +16,3 @@ dataAvSplit <- data %>%
   as.data.frame()
 
 plot_split <- dataAvSplit %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attractor_num), color = experiment )) + geom_point() + geom_line(aes(linetype =attractor_num)) + facet_wrap(~trial_group)
-
-
-#dataAvClean <- slice(dataAvSplit, 1:4)
-
-#plot_average <- dataAvClean %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attractor_num), color = experiment )) + geom_point() + geom_line(aes(linetype =attractor_num)) #+ facet_wrap(~experiment, scales = "free_y")

### 2021-07-14 full_analysis.R

@@ -8,22 +8,22 @@ setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 
 ## Set parameters for the model analysis
 # parameters:
-# By default, only run a model for 'acceptable responses 
+# By default, only run a model for 'acceptable responses
 # in which the data from exp1 and lago et al is pooled
 # Change the following values to True if you would like to have
 # additional exp1 only bayesian model and coefs
 # additional lago only bayesian model and coes
-# model of the RTs 
+# model of the RTs
 
 exp1only <- F; lagoonly <- F; rt <- F
 
 
-# If else in which we check 
+# If else in which we check
 # First, the complete environment needed for the paper
 # If the file does not exist, it runs all scripts and analyses
 # saves the environment, which would already be present here.
 # If the file exist, it asks whether or not you would like to refresh it.
-# This would be done after some stuff within the analysis are changed 
+# This would be done after some stuff within the analysis are changed
 # or the parameters above are changed.
 # If said yes (y), then everything is run again.
 # If said no (n), then it loads the complete_environment.RData

### 2021-07-14 pdf_render.R

@@ -7,11 +7,11 @@ setwd(
 )
 
 # Convert it to knitr
-knitr::Sweave2knitr("glossa-template.Rnw")
+knitr::Sweave2knitr("manuscript.Rnw")
 
 # knit it to a pdf
-knitr::knit2pdf(compiler = 'xelatex', 'glossa-template-knitr.Rnw')
+knitr::knit2pdf(compiler = 'xelatex', 'manuscript-knitr.Rnw')
 
 # open the PDF
-system2('open', args = 'glossa-template-knitr.pdf', wait = FALSE)
+system2('open', args = 'manuscript-knitr.pdf', wait = FALSE)
 

### 2021-07-14 paper/glossa/manuscript.Rnw
anonimization full

@@
 For our model, we ran \Sexpr{n_chains} chains with \Sexpr{n_warmup} warm-up iterations and \Sexpr{n_iter-n_warmup} sampling iterations.
-The data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.
+The data for our study, along with our analysis scripts can be found \url{hhttps://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}.
 
@@
 
-The data that support the findings of this study, the code, and the paper resources including \LaTeX{} and \texttt{Sweave} files are openly available in the anonimized github page at \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.
+The data that support the findings of this study, the code, and the paper resources including \LaTeX{} and \texttt{Sweave} files are openly available in the anonimized github page at \url{https://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}.
 %exclude

### 2021-07-17 paper/glossa/manuscript-knitr-wordcount.tex
typos resolved

@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,100}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 2,865}
 
@@
 \begin{abstract}
-
-Previous studies have shown that speakers may find sentences violating subject-verb agreement grammatical when the sentence contains a feature-matching noun phrase. 
-%
-This so-called agreement attraction effect has also been found in genitive possessive structures such as \textit{'the teacher's brother'} in Turkish (Lago et al., 2019), which is in contrast with its absence in similar constructions in English (Nicol et al., 2016).
-This discrepancy has been hypothesized to be a result of the association between genitive case marking and subjecthood in Turkish, but not in English.
-%
-In the present research, we test an alternative explanation in which Turkish agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
-We hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
-To test this hypothesis, we conducted a speeded acceptability judgment experiment and our results suggest that case-ambiguity does not play a role in agreement attraction, and thus lends credibility to the claim that genitive noun phrases may function as attractors in Turkish due to the association between genitive case and subjecthood.
 
@@
 
+\subsection{Materials}
+
 We used 40 sets of sentences like \ref{ex:our_items}, in which we manipulated (i) the number of the attractor noun and (ii) the number agreement on the verb.
@@
 For our model, we ran 4 chains with 1000 warm-up iterations and 1000 sampling iterations.
-The data for our study, along with our analysis scripts can be found \url{https://anonymous.4open.science/r/replication_lagoetal2018-AC8C/}.
+The data for our study, along with our analysis scripts can be found \url{hhttps://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}.
 
@@
 
+Taken together, our results suggest (i) that agreement attraction effects in Turkish are not due to a reduced association between case-ambiguous nouns and the subjecthood features, and (ii) that local ambiguities, such as case syncretism, do not appear to play a role in agreement attraction.
+Participants do not appear to rely on form-related cues in their decision-making processes and instead use of abstract linguistic features as retrieval cues.
+
 {\firstauthor} conceived the initial version of the presented idea. Both authors designed the the experiment together. 

### 2021-07-17 paper/glossa/manuscript.Rnw
typos resolved

@@
 Previous studies have shown that speakers may find sentences violating subject-verb agreement grammatical when the sentence contains a feature-matching noun phrase.
-%
 This so-called agreement attraction effect has also been found in genitive possessive structures such as \textit{'the teacher's brother'} in Turkish (Lago et al., 2019), which is in contrast with its absence in similar constructions in English (Nicol et al., 2016).
 This discrepancy has been hypothesized to be a result of the association between genitive case marking and subjecthood in Turkish, but not in English.
-%
 In the present research, we test an alternative explanation in which Turkish agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
@@
 To test this hypothesis, we conducted a speeded acceptability judgment experiment and our results suggest that case-ambiguity does not play a role in agreement attraction, and thus lends credibility to the claim that genitive noun phrases may function as attractors in Turkish due to the association between genitive case and subjecthood.
+%exclude
 
@@
 Turkish is an SOV word order language with overt case marking \citep{GokselKerslake:2005,Kornfilt:2011,Kornfilt:2013}.
-For example, the possessor in the Turkish equivalent of the Saxon Genitive in \ref{ex:possgenex} is marked with genitive case, while the head noun is marked with possessive case.
+For example, the possessor in the Turkish equivalent of the Saxon Genitive in \ref{ex:possgenex} is marked with genitive case, while the head noun is marked with possessive marker.
 Importantly, the possessive case marker coincides in form with the accusative case marker when the noun stem ends in a consonant: 
@@
 \ex. \label{ex:possgenex}
-\gll teknisyen-in eğitmen-i \\
+\gll teknisyen-in e\u{g}itmen-i \\
     technician-\textsc{gen} instructor-\textsc{poss} \\
@@
 
-However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{eğitmen-i} (\textit{'instructor'}) in \ref{ex:lago} were consonant-ending, which made them locally ambiguous between possessive and accusative case \citep[pp.
+However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{e\u{g}itmen-i} (\textit{`instructor'}) in \ref{ex:lago} were consonant-ending, which made them locally ambiguous between possessive and accusative case \citep[pp.
 66--67]{GokselKerslake:2005} because the surface form of both, the possessive and accusative case is \textit{-i}.
@@
 The present study tested the predictions of the case syncretism account as an alternative explanation of the previously found agreement attraction effect in Turkish.
-To avoid the ambiguity present in \citet{LagoEtAl:2019}, we used vowel-ending head nouns nouns such as \textit{terzi} (\textit{'tailor'}), for which the possessive marker surfaces as \textit{-si} and is distinct from the accusative (\textit{-yi}).
+To avoid the ambiguity present in \citet{LagoEtAl:2019}, we used vowel-ending head nouns nouns such as \textit{terzi} (\textit{`tailor'}), for which the possessive marker surfaces as \textit{-si} and is distinct from the accusative (\textit{-yi}).
 We hypothesized that if the morpho-phonological ambiguity was a key factor in agreement attraction in Turkish, unambiguous sentences like ours in \ref{ex:our_items} should not elicit attraction effects.
@@
   \gll [Sosyolog-un \textbf{\"{o}\u{g}renci-si}] konu\c{s}-unca tutars{\i}zl{\i}k a\c{c}{\i}\u{g}-a \textbf{\c{c}{\i}kar-d{\i}-lar}.\\ 
-  sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}\\
+  sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{when} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}\\
   \glt `When the student of the sociologist spoke, they revealed an inconsistency.'
@@
   \gll [Dans\"{o}z-\"{u}n \textbf{koca-s{\i}}] var-{\i}nca kap{\i} sakince \textbf{a\c{c}-t{\i}}. \\
-  dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}\\
+  dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{when} door slowly  open-\textsc{pst}\\
   \glt Intended:`When the husband of the dancer came, the door opened slowly.'
@@
 
-Because the magnitude of the agreement attraction effect can operationalized either as the interaction between grammaticality and the presence of a plural attractor, or as the effect of a plural attractor in ungrammatical sentences, we used a second model with predictors (ii) and (iii) and their interaction to analyze responses to ungrammatical conditions only.
+Because the magnitude of the agreement attraction effect can be operationalized either as the interaction between grammaticality and the presence of a plural attractor, or as the effect of a plural attractor in ungrammatical sentences, we used a second model with predictors (ii) and (iii) and their interaction to analyze responses to ungrammatical conditions only.
 
@@
 
+Taken together, our results suggest (i) that agreement attraction effects in Turkish are not due to a reduced association between case-ambiguous nouns and the subjecthood features, and (ii) that local ambiguities, such as case syncretism, do not appear to play a role in agreement attraction.
+Participants do not appear to rely on form-related cues in their decision-making processes and instead use of abstract linguistic features as retrieval cues.
+
 \section*{Abbreviations} %exclude
 
-\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{nmlz} = nominalizer, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular.
-%exclude
+\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular, \textsc{when} = when. %exclude
 

### 2021-10-17 paper/glossa/response/response.tex
revisions done

\documentclass{response}

\usepackage{pdfpages}

\title{Agreement Attraction in Turkish: The case of genitive attractors}
\author{Utku T\"urk \& Pavel Loga\v{c}ev}
\journal{Glossa Psycholinguistics}
%\doi{12345}

\begin{document}

\maketitle

Dear Editors and Reviewers,

We thank you for your hardwork in preparing the proceedings and giving us the opportunity to submit a revised version of our manuscript entitled \emph{Agreement Attraction in Turkish: The case of genitive attractors}. We highly appreciate the constructive criticisms and valuable comments of the anonymous reviewers on our manuscript. We have revised the manuscript in the submitted version based on the comments of the reviewers.

Please find below our response to some of the reviewers’ comments. We hope the reviewers find the revised manuscript and our response below to satisfactorily address their comments.

Please note that reviewers' comments are in bold and italics while our answers are not. Additions to the original manuscript are indicated in blue and deletions with red \emph{only in the response letter}.

For reference, we add an additional PDF to the end of this response letter in which line numbers are shown and all additions are indicated with red font.

Yours Sincerely,\\
Utku T\"urk, Department of Linguistics, Boğaziçi University\\
Pavel Loga\v{c}ev, Department of Linguistics, Boğaziçi University\\

\section{Reviewer \#1}

\subsection{Clarification of the alternative hypothesis}

\RC My biggest concern is that the predictions of the alternative hypothesis are not clear. I understand the ambiguity, but it’s not clear how the “head noun’s reduced association with subjecthood” as a result of the ambiguity would lead to the contrast observed in Lago et al. The ambiguity would affect all the conditions similarly, so any differences in the ungrammatical conditions for instance (e.g., more “acceptable” responses in the ungrammatical attractor match condition) cannot be reduced to the ambiguity. The authors should step through the details of how their alternative hypothesis predicts the effects observed in Lago et al.

\AR We thank the reviewer for pointing out the missing part in our argumentation. We agree with the reviewer and decided to add more details on the notion of reduced association with subjecthood. At the end of the Section 2, we dwelled more on the notion of reduced association with subjecthood. We pointed out the syntactic ambiguity and how it would make participants have a different reading of case endings.

\subsection{Analysis Comparison to Lago et al.}

\RC My only concern with the analysis is more care should be taken to describe how closely the current analysis followed the steps reported in Lago et al. (2019), e.g., did the current study use the same data exclusion techniques, priors, etc.? This is important because if the results were to differ from those reported in Lago et al. (2019), it would not be clear whether the difference is due to the analysis methods or the manipulation.

\AR

\subsection{Suggestions}

\RC \ldots the example item set seems well-constructed (although the full list of materials should be provided in the supplemental materials)

\AR

\RC \ldots the sample size likely provides sufficient power, but a power analysis was not provided.

\AR

\subsection{Minor Comments}

\RC p. 1: I would suggest a term other than “unrelated” to describe the relation between the attractor and verb. There is a relation, even if indirect. The key point is that the attractor is not the subject of the verb.

\AR We changed the term ``syntactically unrelated'' to the ``agreement-wise irrelevant.''

\RC p. 1. Typo: agreement controller headed BY key

\AR We included the missing preposition.

\RC Introduction: The authors should note that the studies of interest are on *number* attraction effects. This is important to orient the reader since it’s been recently shown that attraction arises with other forms of agreement as well.

\AR We included the word ``number'' in the abstract to differentiate the focus of our work from other types of agreement attraction.

\RC p. 3 Typo: due TO case syntcretism

\AR We included the missing preposition.

\RC p. 3: The examples in (4) should have condition labels that match the figure on p. 6

\AR We believe the condition names and the labels on the figures are quite similar. Thus, we did not make any changes.

\RC p. 6 Typo: empty parentheses was identical in both experiments ().

\AR We corrected the empty parantheses. Now it shows the magnitute that we are discussing.

\section{Reviewer \#2}

\subsection{Clarification of the alternative hypothesis}

\RC I would have liked to see the actual mechanism by which "association with subjecthood" and the case-driven idea is implemented within a cue-based framework like Lewis & Vasishth. At the moment the paper gestures towards the possibility that an implementation is possible, but I suspect that it would be harder than the paper suggests to make the trains run on time. If the authors actually spelled out how they imagine attraction to occur mechanistically with examples, that would be a very nice theoretical contribution.

\AR

\subsection{Suggestions}

\RC In the abstract: "Subject head nouns were locally ambiguous between the possessive and the accusative case. We hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish." Perhaps a follow up sentence is in order here, explaining that that caused the possessor to be erroneously interpreted as the subject? Or increased the availability of the distractor?

\AR As suggested by the reviewer, we included a sentence explaining how this ambiguity may serve as a basis for our alternative hypothesis.

\RC I feel that it would be helpful to have a more explicit illustration of the partial match effect that is hypothesized to lead to agreement, wrt feature-matching, case and number. It is not clear to me how "association with subjecthood" is implemented via Case-features. Especially because there are apparently multiple cases that can be associated with subjecthood. Is the proposal that the verb cues for *any* Case that might be associated with subjects (nominative, genitive, possessive...). Or is something else meant? Articulating this would be increase the theoretical contribution of the paper.

\AR We thank the reviewer for their comment. We now articulated more in the Section 2 on how this association is affected by the syncretism.

\RC At the moment, the description of Lago et al's results, the (terse) explanation for agreement attraction, and the information about the accusative/genitive syncretism are all interwoven in the rather short section 2. I'd recommend separating them out into three distinct parts: Lago et al's results, Lago et al's explanation, Alternative explanation (with discussion of syncretism).

\AR ASK PAVEL

\RC The explanation would be improved by having a clearer description and concrete examples of the accusative/genitive syncretism. It'd be helpful to have examples with nouns that DON'T exhibit the ambiguity and those that DO exhibit the ambiguity presented side-by-side before we get to the materials.

\AR TODO

\subsection{Minor Comments}

\RC The phrasing "possessive case marker *coincides in form with* the accusative case marker" is needlessly indirect. Why not just say it's syncretic in certain cases?

\AR We thank the reviewer for the minor comment. We edited the paper as suggested by the reviewer.

\RC The phrasing "we analyzed the data from the present experiment together with Lago et al.’s (2019) data" made me first think that the data were combined. Maybe say the data were compared with the results from Lago et al. 2019? Was Lago et al's data re-analyzed?

\AR We thank the reviewer for their comment. We now have reworded the first sentence in Section 3.4. We indeed re-analyzed Lago et al.'s (2019) data. However, now we emphasize that our intention were to compare our results.

\RC I'm surprised that Wagers, Lau & Phillips (2009) is not cited in favor of the retrieval position.

\AR We thank the reviewer for pointing out this deficiency. We wanted to include the Wagers, Lau & Phillips (2009), however, we confused the citation key in bibtex file. It was a mistake on our part.

\clearpage

%\includepdf[pages=-]{edits_shown.pdf}
\end{document}

### 2021-10-17 paper/glossa/manuscript-knitr-wordcount.tex
revisions done

@@
 
+\newcommand{\revise}[1]{\textcolor{red}{#1}}
+
 % \pdf* commands provide metadata for the PDF output. ASCII characters only!
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 2,865}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,296}
 
@@
 People often fail to accurately process grammatical dependencies between different parts of a sentence \citep[e.g.,][]{GibsonThomas:1999,PhillipsEtAl:2011}.
-For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the syntactically unrelated attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed \textit{key}.
-A number of previous  studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with a singular attractor.
+For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the \revise{agreement-wise irrelevant} attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed \revise{by} \textit{key}.
+A number of previous studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999, WagersEtAl:2009} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with a singular attractor.
 This phenomenon, known as \textit{agreement attraction} \citep{BockMiller:1991} has been attested in a number of languages, such as in Arabic \citep{TuckerEtAl:2015}, Armenian \citep{AvetisyanEtAl:2020}, German \citep{LagoFelser:2018}, Hindi \citep{BhatiaDillon:2020}, Serbian \citep{RisticEtAl:2016}, Slovak \citep{BadeckerKuminiak:2007}, Spanish \citep{LagoEtAl:2015}, and recently in Turkish \citep{LagoEtAl:2019}.
@@
 \citet{LagoEtAl:2019} hypothesize that Turkish possessor noun phrases, unlike their English counterparts, may function as agreement attractors because Turkish genitive NPs may function as subjects of non-finite clauses in Turkish \citep{GokselKerslake:2005,Kornfilt:2011}.
-As a result, Turkish genitive NPs may match the subjecthood feature used in the cue-based retrieval of a verb's subject \citep{LewisVasishth:2005, ArnettWagers:2017}.
+As a result, Turkish genitive NPs may match the subjecthood feature used in the cue-based retrieval of a verb's subject \citep{LewisVasishth:2005, WagersEtAl:2009, ArnettWagers:2017}.
 
@@
 Turkish is an SOV word order language with overt case marking \citep{GokselKerslake:2005,Kornfilt:2011,Kornfilt:2013}.
-For example, the possessor in the Turkish equivalent of the Saxon Genitive in \ref{ex:possgenex} is marked with genitive case, while the head noun is marked with possessive case.
-Importantly, the possessive case marker coincides in form with the accusative case marker when the noun stem ends in a consonant: 
+For example, the possessor in the Turkish equivalent of the Saxon Genitive in \ref{ex:possgenex} is marked with genitive case, while the head noun is marked with possessive marker.
+Importantly, the possessive case marker \revise{is syncretic with} the accusative case marker when the noun stem ends in a consonant: 
 This is because in Turkish, case markers have different forms depending on whether the last sound of the stem is a vowel.
@@
 
-However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{eğitmen-i} (\textit{'instructor'}) in \ref{ex:lago} were consonant-ending, which made them locally ambiguous between possessive and accusative case \citep[pp.
+However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{e\u{g}itmen-i} (\textit{`instructor'}) in \ref{ex:lago} were consonant-ending, which made them locally ambiguous between possessive and accusative case \citep[pp.
 66--67]{GokselKerslake:2005} because the surface form of both, the possessive and accusative case is \textit{-i}.
 %
-Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due case syncretism between possessive and accusative.
+
+Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due \revise{to} case syncretism between possessive and accusative.
+\revise{Because of this syncretism, there are two possible structures that readers may entertain upon reading the first two NPs.
+Consider \ref{ex:ambiguous} which can be represented with two different structures depending on the possible endings, which are shown in \ref{ex:simplexreading} and \ref{ex:embeddedreading}.}
+
+{\color{red}
+\ex. Ambiguous Part \label{ex:ambiguous}\\
+\gll Teknisyen-in e\u{g}itmen-i ola\u{g}an{\"u}st{\"u} h{\i}zl{\i} \ldots \\
+technician-\textsc{sg}-\textsc{gen} instructor-\textsc{poss} extraordinarily fast \ldots \\
+  \a. Simplex Sentence \label{ex:simplexreading} \\
+  \gll \ldots{} ko\c{s}-tu.\\
+  \ldots{} run-\textsc{pst}\\
+  \glt `The technician's instructor extraordinarily fast ran.'
+  \b. Embedded Sentence \label{ex:embeddedreading}\\
+  \gll \ldots{} kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
+  \ldots{} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
+  \glt `I saw the technician firing the instructor really fast.'
+
+}
+
+\revise{This ambiguity stems from the fact that the genitive case can serve as an embedded subject marker, and the accusative case can surface as \textit{-i}.
+In some trials, participants may erroneously encode the genitive case on the first noun as a subject marker, and the \textit{-i} marked the second noun as an object.
+We hypothesize that the head noun will not be treated as a subject in those trials until a possible reanalysis after reading the matrix verb.
+We expect this reduced association to be reflected as an overall decrease in accuracy in grammatical conditions.
+Upon reading the verb, participants will either find the sentence ungrammatical since they have expected a structure similar to \ref{ex:embeddedreading} or reanalyze the sentence and will judge the sentence according to the structure in \ref{ex:simplexreading}.
+Since there is no plural marker at the matrix verb, the plural on the attractor will not have an additional effect.
+However, in ungrammatical conditions in which the matrix verb has an overt plural marker, we expect to have an easier interference of a plural marked Genitive NP which was recently encoded as a subject and an overall decrease in the accuracy.
 We tested this hypothesis in a speeded-acceptability experiment with sentences similar to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}), but with unambiguously marked vowel-ending head nouns.
+We expect that the agreement attraction effect may arise specifically on trials where participants misparse the two initial NP cases and where the sentence contains a plural attractor with a plural verb.
+On trials where participants misparse the two initial NP cases, but the sentence does not have a plural attractor or a plural verb, we expect overall higher errors without the specific effect of a plural attractor.}
 
@@
 
-In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect we analyzed the data from the present experiment together with \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data, using the experiment as an additional factor in the analysis.
+In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect, we analyzed the data from the present experiment \revise{compared our results to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) results, by including \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data in our Bayesian GLM and} using the experiment as an additional factor in the analysis.
 
@@
 Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function.
-The main effect of grammaticality ($\hat{\beta}=3.08;$ $CI=[2.84; 3.33];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.04; -0.42];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
-There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.27;$ $CI=[-0.77; 0.25];$ $P(\beta<0)=    .85$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments ().
-This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor (($\hat{\beta}=0.01;$ $CI=[-0.32; 0.33];$ $P(\beta<0)=    .48$).
+The main effect of grammaticality ($\hat{\beta}=3.09;$ $CI=[2.85; 3.35];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.03; -0.43];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
+There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.28;$ $CI=[-0.78; 0.23];$ $P(\beta<0)=    .86$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments (0.11).
+This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor (($\hat{\beta}=0.01;$ $CI=[-0.31; 0.33];$ $P(\beta<0)=    .46$).
 It also showed a main effect of plural attractor ($\hat{\beta}=0.46;$ $CI=[0.26; 0.65];$ $P(\beta<0)< .001$).

### 2021-10-17 paper/glossa/manuscript-knitr.Rnw
revisions done

@@
 \usepackage[linguistics]{forest}
+
+\newcommand{\revise}[1]{\textcolor{red}{#1}}
 
@@
 Previous studies have shown that speakers may find sentences violating subject-verb agreement grammatical when the sentence contains a feature-matching noun phrase.
-%
 This so-called agreement attraction effect has also been found in genitive possessive structures such as \textit{'the teacher's brother'} in Turkish (Lago et al., 2019), which is in contrast with its absence in similar constructions in English (Nicol et al., 2016).
 This discrepancy has been hypothesized to be a result of the association between genitive case marking and subjecthood in Turkish, but not in English.
-%
-In the present research, we test an alternative explanation in which Turkish agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
-We hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
+In the present research, we test an alternative explanation in which Turkish \revise{number} agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
+\revise{When this ambiguity leads to erroneous processing, participants may end up with representations where the head noun is processed as an object of an embedded clause.
+Thus, w}e hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
 To test this hypothesis, we conducted a speeded acceptability judgment experiment and our results suggest that case-ambiguity does not play a role in agreement attraction, and thus lends credibility to the claim that genitive noun phrases may function as attractors in Turkish due to the association between genitive case and subjecthood.
+%exclude
 
@@
 
-However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{eğitmen-i} (\textit{'instructor'}) in \ref{ex:lago} were consonant-ending, which made them locally ambiguous between possessive and accusative case \citep[pp.
+However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{e\u{g}itmen-i} (\textit{`instructor'}) in \ref{ex:lago} were consonant-ending, which made them locally ambiguous between possessive and accusative case \citep[pp.
 66--67]{GokselKerslake:2005} because the surface form of both, the possessive and accusative case is \textit{-i}.
 %
-Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due case syncretism between possessive and accusative.
+
+Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due \revise{to} case syncretism between possessive and accusative.
+\revise{Because of this syncretism, there are two possible structures that readers may entertain upon reading the first two NPs.
+Consider \ref{ex:ambiguous} which can be represented with two different structures depending on the possible endings, which are shown in \ref{ex:simplexreading} and \ref{ex:embeddedreading}.}
+
+{\color{red}
+\ex. Ambiguous Part \label{ex:ambiguous}\\
+\gll Teknisyen-in e\u{g}itmen-i ola\u{g}an{\"u}st{\"u} h{\i}zl{\i} \ldots \\
+technician-\textsc{gen} instructor-\textsc{poss} extraordinarily fast \ldots \\
+  \a. Simplex Sentence \label{ex:simplexreading} \\
+  \gll \ldots{} ko\c{s}-tu.\\
+  \ldots{} run-\textsc{pst}\\
+  \glt `The technician's instructor extraordinarily fast ran.'
+  \b. Embedded Sentence \label{ex:embeddedreading}\\
+  \gll \ldots{} kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
+  \ldots{} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
+  \glt `I saw the technician firing the instructor really fast.'
+
+}
+
+\revise{This ambiguity stems from the fact that the genitive case can serve as an embedded subject marker, and the accusative case can surface as \textit{-i}.
+In some trials, participants may erroneously encode the genitive case on the first noun as a subject marker, and the \textit{-i} marked the second noun as an object.
+We hypothesize that the head noun will not be treated as a subject in those trials until a possible reanalysis after reading the matrix verb.
+We expect this reduced association to be reflected as an overall decrease in accuracy in grammatical conditions.
+Upon reading the verb, participants will either find the sentence ungrammatical since they have expected a structure similar to \ref{ex:embeddedreading} or reanalyze the sentence and will judge the sentence according to the structure in \ref{ex:simplexreading}.
+Since there is no plural marker at the matrix verb, the plural on the attractor will not have an additional effect.
+However, in ungrammatical conditions in which the matrix verb has an overt plural marker, we expect to have an easier interference of a plural marked Genitive NP which was recently encoded as a subject and an overall decrease in the accuracy.
 We tested this hypothesis in a speeded-acceptability experiment with sentences similar to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}), but with unambiguously marked vowel-ending head nouns.
+We expect that the agreement attraction effect may arise specifically on trials where participants misparse the two initial NP cases and where the sentence contains a plural attractor with a plural verb.
+On trials where participants misparse the two initial NP cases, but the sentence does not have a plural attractor or a plural verb, we expect overall higher errors without the specific effect of a plural attractor.}
 
@@
 
+Taken together, our results suggest (i) that agreement attraction effects in Turkish are not due to a reduced association between case-ambiguous nouns and the subjecthood features, and (ii) that local ambiguities, such as case syncretism, do not appear to play a role in agreement attraction.
+Participants do not appear to rely on form-related cues in their decision-making processes and instead use of abstract linguistic features as retrieval cues.
+
 \section*{Abbreviations} %exclude
 
-\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{nmlz} = nominalizer, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular.
+\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{nmlz} = nominalizer, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular, \textsc{when} = when.
 %exclude

### 2021-10-17 paper/glossa/manuscript-knitr.tex
revisions done

--- 2021-07-14 paper/glossa/manuscript-knitr-wordcount.tex
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,100}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,296}
 
@@
 
+Taken together, our results suggest (i) that agreement attraction effects in Turkish are not due to a reduced association between case-ambiguous nouns and the subjecthood features, and (ii) that local ambiguities, such as case syncretism, do not appear to play a role in agreement attraction.
+Participants do not appear to rely on form-related cues in their decision-making processes and instead use of abstract linguistic features as retrieval cues.
+
+\section*{Abbreviations} %exclude
+
+\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{nmlz} = nominalizer, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular, \textsc{when} = when.
+%exclude
+
+\section*{Data Availability} %exclude
+
+The data that support the findings of this study, the code, and the paper resources including \LaTeX{} and \texttt{Sweave} files are openly available in the anonimized github page at \url{https://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}.
+%exclude
+
+\section*{Authors' Contributions} %exclude
+
 {\firstauthor} conceived the initial version of the presented idea. Both authors designed the the experiment together. 

### 2021-10-17 paper/glossa/manuscript.Rnw
revisions done

@@
 This discrepancy has been hypothesized to be a result of the association between genitive case marking and subjecthood in Turkish, but not in English.
-In the present research, we test an alternative explanation in which Turkish agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
-We hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
+In the present research, we test an alternative explanation in which Turkish \revise{number} agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
+\revise{When this ambiguity leads to erroneous processing, participants may end up with representations where the head noun is processed as an object of an embedded clause.
+Thus, w}e hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
 To test this hypothesis, we conducted a speeded acceptability judgment experiment and our results suggest that case-ambiguity does not play a role in agreement attraction, and thus lends credibility to the claim that genitive noun phrases may function as attractors in Turkish due to the association between genitive case and subjecthood.
@@
 For example, the possessor in the Turkish equivalent of the Saxon Genitive in \ref{ex:possgenex} is marked with genitive case, while the head noun is marked with possessive marker.
-Importantly, the possessive case marker coincides in form with the accusative case marker when the noun stem ends in a consonant: 
+Importantly, the possessive case marker \revise{is syncretic with} the accusative case marker when the noun stem ends in a consonant: 
 This is because in Turkish, case markers have different forms depending on whether the last sound of the stem is a vowel.
@@
 %
-Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due case syncretism between possessive and accusative.
+
+Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due \revise{to} case syncretism between possessive and accusative.
+\revise{Because of this syncretism, there are two possible structures that readers may entertain upon reading the first two NPs.
+Consider \ref{ex:ambiguous} which can be represented with two different structures depending on the possible endings, which are shown in \ref{ex:simplexreading} and \ref{ex:embeddedreading}.}
+
+{\color{red}
+\ex. Ambiguous Part \label{ex:ambiguous}\\
+\gll Teknisyen-in e\u{g}itmen-i ola\u{g}an{\"u}st{\"u} h{\i}zl{\i} \ldots \\
+technician-\textsc{gen} instructor-\textsc{poss} extraordinarily fast \ldots \\
+  \a. Simplex Sentence \label{ex:simplexreading} \\
+  \gll \ldots{} ko\c{s}-tu.\\
+  \ldots{} run-\textsc{pst}\\
+  \glt `The technician's instructor extraordinarily fast ran.'
+  \b. Embedded Sentence \label{ex:embeddedreading}\\
+  \gll \ldots{} kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
+  \ldots{} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
+  \glt `I saw the technician firing the instructor really fast.'
+
+}
+
+\revise{This ambiguity stems from the fact that the genitive case can serve as an embedded subject marker, and the accusative case can surface as \textit{-i}.
+In some trials, participants may erroneously encode the genitive case on the first noun as a subject marker, and the \textit{-i} marked the second noun as an object.
+We hypothesize that the head noun will not be treated as a subject in those trials until a possible reanalysis after reading the matrix verb.
+We expect this reduced association to be reflected as an overall decrease in accuracy in grammatical conditions.
+Upon reading the verb, participants will either find the sentence ungrammatical since they have expected a structure similar to \ref{ex:embeddedreading} or reanalyze the sentence and will judge the sentence according to the structure in \ref{ex:simplexreading}.
+Since there is no plural marker at the matrix verb, the plural on the attractor will not have an additional effect.
+However, in ungrammatical conditions in which the matrix verb has an overt plural marker, we expect to have an easier interference of a plural marked Genitive NP which was recently encoded as a subject and an overall decrease in the accuracy.
 We tested this hypothesis in a speeded-acceptability experiment with sentences similar to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}), but with unambiguously marked vowel-ending head nouns.
+We expect that the agreement attraction effect may arise specifically on trials where participants misparse the two initial NP cases and where the sentence contains a plural attractor with a plural verb.
+On trials where participants misparse the two initial NP cases, but the sentence does not have a plural attractor or a plural verb, we expect overall higher errors without the specific effect of a plural attractor.}
 
@@
 
-\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular, \textsc{when} = when. %exclude
+\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{nmlz} = nominalizer, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular, \textsc{when} = when.
+%exclude
 

### 2021-10-17 R/analysis/02_word_freq.R

@@ -26,3 +26,4 @@ df_merge_lago$item %<>% add(1000)
 df_merged <- dplyr::bind_rows(df_merge_exp1, df_merge_lago)
 df_merged$subject %<>% as.factor()
 df_merged$item %<>% as.factor()
+

### 2021-10-17 R/analysis/04_bayesian_models.R

@@ -100,7 +100,7 @@ models[['ungram_responses']] <- m_ungram_responses
 
 tables <- vector('list', length(models))
 for (i in seq_along(models)) {
-  fname <- paste0('results_table_', names(models[i]))
+  fname <<- paste0('results_table_', names(models[i]))
   tables[[fname]] <- fixef(models[[i]], summary = T, robust = F) %>%
     as.data.frame() #%>% tibble::rownames_to_column("variables")
   

### 2021-10-17 R/analysis/05_model_plots.R

@@ -97,3 +97,4 @@ p_m_response <- print(p_m_response + annotate(x=-1, xend=4, y=0, yend=0, lwd=0.2
   p_m_ungram_response <- print(p_m_ungram_response + annotate(x=-1, xend=1, y=0, yend=0, lwd=0.25, geom="segment"))
   
 }
+

### 2021-10-17 R/analysis/06_text_inputs.R

@@ -13,11 +13,11 @@ exp1_cur_entry4 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammati
 exp1_cur_entry4$M %<>% round(.,2)
 exp1_cur_entry4$SE %<>% round(.,2)
 
-lago_cur_entry1 = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "plural")
+lago_cur_entry1 = avg_exp$resp %>% filter(experiment == "Lago et al. (2019)", grammatical == "ungrammatical", attractor_num == "plural")
 lago_cur_entry1$M %<>% round(.,2)
 lago_cur_entry1$SE %<>% round(.,2)
 
-lago_cur_entry2 = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "singular")
+lago_cur_entry2 = avg_exp$resp %>% filter(experiment == "Lago et al. (2019)", grammatical == "ungrammatical", attractor_num == "singular")
 lago_cur_entry2$M %<>% round(.,2)
 lago_cur_entry2$SE %<>% round(.,2)
 

### 2021-10-17 full_analysis.R

@@ -4,7 +4,7 @@
 set.seed(42)
 
 ## Set the path to the active document (full_analysis_and_pdf)
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+setwd(here::here())
 
 ## Set parameters for the model analysis
 # parameters:

### 2021-10-17 pdf_render.R

@@ -2,16 +2,32 @@
 ## set working directory for the paper
 setwd(
   paste0(
-    dirname(rstudioapi::getActiveDocumentContext()$path),'/paper/glossa/'
+    here::here(),'/paper/glossa/'
   )
 )
-
 # Convert it to knitr
 knitr::Sweave2knitr("manuscript.Rnw")
 
+
 # knit it to a pdf
-knitr::knit2pdf(compiler = 'xelatex', 'manuscript-knitr.Rnw')
+knitr::knit2pdf(compiler = 'xelatex', 'manuscript-knitr.Rnw') %>% 
+  file.rename(.,'manuscript.pdf')
+
+  
+# delete aux
+clean.knitr <- function() {
+  if (.Platform$OS.type=="unix") {
+    
+    system(paste0("cd '", getwd(), 
+                  "';rm *.gz;rm *.toc;rm *.log;rm *.glo;rm *.aux;rm *.ist;rm *-knitr.Rnw"))
+  } else {
+    warning("This function works only in UNIX systems")
+  }
+}
+
+#clean.knitr()
 
 # open the PDF
-system2('open', args = 'manuscript-knitr.pdf', wait = FALSE)
+system2('open', args = 'manuscript.pdf', wait = FALSE)
+
 

### 2021-11-06 paper/glossa/manuscript.Rnw
osf

--- 2021-07-17 paper/glossa/manuscript.Rnw
@@
 
-<<wordcount, echo=FALSE, cache=FALSE>>=
-library(knitr)
-
-comma <- function (x, ...) {
-  format(x, ..., big.mark = ",", scientific = FALSE, trim = TRUE)
-}
-
-# To dynamically extract name of the current file, use code below
-nameoffile <- 'manuscript-knitr.Rnw' # get name of file
-nof2 <-  strsplit(nameoffile,"\\.")[[1]][1] # extract name, drop extension
-noftex <- paste(nof2, ".tex", sep="") # add .tex extension
-nofwordcount <-  paste(nof2, '-','wordcount', '.tex', sep = "") # prepare a tex file for word count
-if (file.exists(nofwordcount)) {unlink(nofwordcount)} #delete the previous file.
-
-con <- file(noftex, open = 'r') # open the file with R
-while(TRUE) {
-  line <- readLines(con, n = 1) # read lines
-  if(length(line) == 0) break # pass if nothing is there
-  else if(!endsWith(line, "%exclude")){ # if the line does not end with %exclude 
-    write(line, file = nofwordcount, append = TRUE) # write it to the new file
-  } 
-}
-close(con)
-
-systemcall <- paste("system('texcount -inc -incbib -total -sum ", nofwordcount, "', intern=TRUE)", sep="") # paste together texcount system command
-texcount.out <- eval(parse(text=systemcall)) # run texcount on current last compiled .tex file with edits
-
-sum.row <- grep("Sum count", texcount.out, value=TRUE) # extract row
-pattern <- "(\\d)+" # regex pattern for digits
-
-count <- regmatches(sum.row, regexpr(pattern, sum.row) )
-# extract digits
-
-count <- comma(as.numeric(count)) # add comma
-
-@
-
 % \pdf* commands provide metadata for the PDF output. ASCII characters only!
-\pdfauthor{A.A and B.B}
+\pdfauthor{Utku Turk and Pavel Logacev}
 \pdftitle{Agreement Attraction in Turkish}
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: \Sexpr{count}}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3303}
 
-\newcommand{\firstauthor}{{A.A.}}
-\newcommand{\firstauthorshort}{{A.A.}}
-\newcommand{\secondauthor}{{B.B.}}
-\newcommand{\secondauthorshort}{{B.B.}}
+\newcommand{\firstauthor}{{Utku T\"urk}}
+\newcommand{\firstauthorshort}{{T\"urk}}
+\newcommand{\secondauthor}{{Pavel Loga\v{c}ev}}
+\newcommand{\secondauthorshort}{{Loga\v{c}ev}}
 
-\author[\firstauthor \& \secondauthor]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
+\author[\firstauthorshort \& \secondauthorshort]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
 {%as many authors as you like, each separated by \AND.
-  \spauthor{\texttt{Hidden Hidden (\firstauthor)}\\ 
-  \institute{\texttt{Hidden University}}\\
+  \spauthor{\firstauthor\\ 
+  \institute{Bo\u{g}azi\c{c}i University}\\
   \small{
-    \texttt{hidden@hidden.edu}}
+    \texttt{utku.turk@boun.edu.tr}}
   }
   \AND
-  \spauthor{\texttt{Hidden Hidden (\secondauthor)}\\ 
-  \institute{\texttt{Hidden University}}\\
+  \spauthor{\secondauthor\\ 
+  \institute{Bo\u{g}azi\c{c}i University}\\
   \small{
-    \texttt{hidden@hidden.edu}}
+    \texttt{pavel.logacev@boun.edu.tr}}
   }%
@@
 This discrepancy has been hypothesized to be a result of the association between genitive case marking and subjecthood in Turkish, but not in English.
-In the present research, we test an alternative explanation in which Turkish agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
+In the present research, we test an alternative explanation in which Turkish number agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
 We hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
@@
 
-People often fail to accurately process grammatical dependencies between different parts of a sentence \citep[e.g.,][]{GibsonThomas:1999,PhillipsEtAl:2011}.
-For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the syntactically unrelated attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed \textit{key}.
-A number of previous  studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with a singular attractor.
+Speakers often fail to accurately process grammatical dependencies between different parts of a sentence \citep[e.g.,][]{GibsonThomas:1999,PhillipsEtAl:2011}.
+For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the agreement-wise irrelevant attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed by \textit{key}.
+A number of previous studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999, WagersEtAl:2009} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with a singular attractor.
 This phenomenon, known as \textit{agreement attraction} \citep{BockMiller:1991} has been attested in a number of languages, such as in Arabic \citep{TuckerEtAl:2015}, Armenian \citep{AvetisyanEtAl:2020}, German \citep{LagoFelser:2018}, Hindi \citep{BhatiaDillon:2020}, Serbian \citep{RisticEtAl:2016}, Slovak \citep{BadeckerKuminiak:2007}, Spanish \citep{LagoEtAl:2015}, and recently in Turkish \citep{LagoEtAl:2019}.
@@
 
-\citet{LagoEtAl:2019} demonstrated that genitive possessors (such as \textit{painters} in \textit{the painters' rival}) cause agreement attraction effects in Turkish.
+\citet{LagoEtAl:2019} demonstrated that genitive possessors (such as \textit{painters} in \textit{the painters' rival}) effect agreement attraction effects in Turkish.
 However, this finding appears to be at odds with \citeauthor{NicolEtAl:2016}'s (\citeyear{NicolEtAl:2016}) results, who failed to find a similar effect in English.
 \citet{LagoEtAl:2019} hypothesize that Turkish possessor noun phrases, unlike their English counterparts, may function as agreement attractors because Turkish genitive NPs may function as subjects of non-finite clauses in Turkish \citep{GokselKerslake:2005,Kornfilt:2011}.
-As a result, Turkish genitive NPs may match the subjecthood feature used in the cue-based retrieval of a verb's subject \citep{LewisVasishth:2005, ArnettWagers:2017}.
+As a result, Turkish genitive NPs may match the subjecthood feature used in the cue-based retrieval of a verb's subject \citep{LewisVasishth:2005, WagersEtAl:2009, ArnettWagers:2017}.
 
-In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of case syncretism in the experimental sentences in their experiment, as a result of which all subject head nouns were ambiguous between possessive and accusative case.
+In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of local ambiguity in the experimental sentences in their experiment, as a result of which all subject head nouns were ambiguous between possessive and accusative case.
 
@@
 Turkish is an SOV word order language with overt case marking \citep{GokselKerslake:2005,Kornfilt:2011,Kornfilt:2013}. 
-For example, the possessor in the Turkish equivalent of the Saxon Genitive in \ref{ex:possgenex} is marked with genitive case, while the head noun is marked with possessive marker.
+For example, the possessor in the Turkish construction in \ref{ex:possgenex}, which is similar to the Saxon Genitive, is marked with genitive case, while the head noun is marked with possessive case. 
 Importantly, the possessive case marker coincides in form with the accusative case marker when the noun stem ends in a consonant: 
@@
 \ex. \label{ex:possgenex}
-\gll teknisyen-in e\u{g}itmen-i \\
+\gll $[$$[$teknisyen-in$]$ e\u{g}itmen-i$]$ \\
     technician-\textsc{gen} instructor-\textsc{poss} \\
@@
 \citet{LagoEtAl:2019} argue that this erroneous retrieval may be facilitated by the genitive case marking on the attractor, because genitive NPs can function as subjects of embedded clauses in Turkish.
-Due to the ubiquity of genitive subjects, attractors marked with genitive case a priori likely to be agreement controllers.
+Due to the ubiquity of genitive subjects, attractors marked with genitive case are a priori likely to be agreement controllers.
 
-However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{e\u{g}itmen-i} (\textit{`instructor'}) in \ref{ex:lago} were consonant-ending, which made them locally ambiguous between possessive and accusative case \citep[pp.
-66--67]{GokselKerslake:2005} because the surface form of both, the possessive and accusative case is \textit{-i}.
+However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{e\u{g}itmen-i} (\textit{`instructor'}) in \ref{ex:lago} were consonant-ending, making their possessive forms ambiguous between possessive and accusative case due to case syncretism between them in vowel-ending stems \citep[pp.
+66--67]{GokselKerslake:2005}.
+%because the surface form of both, the possessive and accusative case is \textit{-i}. 
+%locally
+As a result, the head noun (\textit{'instructor'}) in \ref{ex:ambiguous} can be disambiguated towards possessive case as in \ref{ex:ambiguous_possessive}, or towards accusative case as in \ref{ex:ambiguous_accusative}, where the genitive-marked noun functions as an embedded subject, and the matrix subject is omitted due to pro-drop.
+
+\ex.
+\label{ex:ambiguous}
+  \a. \textsc{Possessive Interpretation} \label{ex:ambiguous_possessive} \\
+  \gll Teknisyen-in e\u{g}itmen-i ko\c{s}-tu.\\
+       technician-\textsc{gen} instructor-\textsc{poss} run-\textsc{pst}\\
+  \glt `The technician's instructor ran.'
+  \b. \textsc{Accusative Interpretation} \label{ex:ambiguous_accusative}\\
+  \gll Teknisyen-in e\u{g}itmen-i kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
+  technician-\textsc{gen} instructor-\textsc{poss} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
+  \glt `I saw the technician firing the fast.'
+
+%{\color{red}
+%\ex. %Ambiguous Part 
+%\label{ex:ambiguous}\\
+%\gll Teknisyen-in e\u{g}itmen-i ola\u{g}an{\"u}st{\"u} h{\i}zl{\i} \ldots \\
+%technician-\textsc{gen} instructor-\textsc{poss} extraordinarily fast \ldots \\
+%  \a. Simplex Sentence \label{ex:simplexreading} \\
+%  \gll \ldots{} ko\c{s}-tu.\\
+%  \ldots{} run-\textsc{pst}\\
+%  \glt `The technician's instructor extraordinarily fast ran.'
+%  \b. Embedded Sentence \label{ex:embeddedreading}\\
+%  \gll \ldots{} kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
+%  \ldots{} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
+%  \glt `I saw the technician firing the instructor really fast.'
+%}
+
+Because accusative NPs cannot function as subjects in Turkish, it is possible that Lago et al.'s finding of agreement attraction effects in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the head nouns' \textit{reduced association with subjecthood} due to its ambiguity.
+%This ambiguity stems from the fact that the genitive case can serve as an embedded subject marker, and the accusative case can surface as \textit{-i}. 
+% For example, on some trials, 
+Because sentences like \ref{ex:lago} are locally ambiguous, participants may initially adopt an incorrect analysis of the genitive-possessive structure on some trials, and encode the genitive-marked first noun as the subject of an embedded verb and the ambiguous second noun as an accusative object.
+Under the assumption that remnants of an incorrect analysis affect the parsing process even after after a successful reanalysis \citep{Staub:2007}, the initial association between the genitive noun phrase and subjecthood may lead an agreement attraction effect.
+In contrast, this account predicts that the agreement attraction effect should be either significantly reduced or entirely absent when the head noun is unambiguous, as the function of the genitive noun phrase is disambiguated early, thus preventing potential digging-in effects \citep{Tabor:2004}.
 %
-Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due case syncretism between possessive and accusative.
+%the head noun will arguably not be treated as a subject until a possible reanalysis after reading the matrix verb.
+We expect this reduced association to be reflected as an overall decrease in accuracy in grammatical conditions.
+Upon reading the verb, participants will either find the sentence ungrammatical since they have expected a structure similar to \ref{ex:embeddedreading} or reanalyze the sentence and will judge the sentence according to the structure in \ref{ex:simplexreading}.
+Since there is no plural marker at the matrix verb, the plural on the attractor will not have an additional effect.
+However, in ungrammatical conditions in which the matrix verb has an overt plural marker, we expect to have an easier interference of a plural marked Genitive NP which was recently encoded as a subject and an overall decrease in the accuracy.
+%
 We tested this hypothesis in a speeded-acceptability experiment with sentences similar to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}), but with unambiguously marked vowel-ending head nouns.
+%We expect that the agreement attraction effect may arise specifically on trials where participants misparse the two initial NP cases and where the sentence contains a plural attractor with a plural verb.
+On trials where participants misparse the two initial NP cases, but the sentence does not have a plural attractor or a plural verb, we expect overall higher errors without the specific effect of a plural attractor.
+%}
 
@@
 \ex. \label{ex:our_items}
-  \a. * Plural Attractor, Ungrammatical (Plural Verb) \label{ex:expitem-plpl}\\
+  \a. * \textsc{Plural Attractor, Ungrammatical (Plural Verb)} \label{ex:expitem-plpl}\\
   \gll [Milyoner-ler-in \textbf{terzi-si}] tamamen gereksizce \textbf{kov-ul-du-lar}.\\
@@
   \glt `The millionaires' tailor were fired for no reason at all.'
-  \b. Plural Attractor, Grammatical (Singular Verb) \label{ex:expitem-plsg} \\
+  \b. \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{ex:expitem-plsg} \\
   \gll [Milyoner-ler-in \textbf{terzi-si}] tamamen gereksizce \textbf{kov-ul-du}.\\
@@
   \glt `The millionaires' tailor was fired for no reason at all.'
-  \b. * Singular Attractor, Ungrammatical (Plural Verb) \label{ex:expitem-sgpl}\\
+  \b. * \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{ex:expitem-sgpl}\\
   \gll [Milyoner-in \textbf{terzi-si}] tamamen gereksizce \textbf{kov-ul-du-lar}.\\
@@
   \glt `The millionaire's tailor were fired for no reason at all.'
-  \b. Singular Attractor Grammatical (Singular Verb) \label{ex:expitem-sgsg}\\
+  \b. \textsc{Singular Attractor Grammatical (Singular Verb)} \label{ex:expitem-sgsg}\\
   \gll [Milyoner-in \textbf{terzi-si}] tamamen gereksizce \textbf{kov-ul-du}.\\
@@
 All participants were native Turkish speakers, with an average age of \Sexpr{mean_age} (range: \Sexpr{min_age} -- \Sexpr{max_age}).
-The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at \texttt{Hidden University}.
+The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at Bo\u{g}azi\c{c}i University.
 All participants provided informed consent before their participation and their identity are completely anonimized.
@@
 \ex. \label{ex:fillers}
-  \a. Grammatical Filler (Plural Verb) \label{ex:gram_filler}\\
+  \a. \textsc{Grammatical Filler (Plural Verb)} \label{ex:gram_filler}\\
   \gll [Sosyolog-un \textbf{\"{o}\u{g}renci-si}] konu\c{s}-unca tutars{\i}zl{\i}k a\c{c}{\i}\u{g}-a \textbf{\c{c}{\i}kar-d{\i}-lar}.\\ 
@@
   \glt `When the student of the sociologist spoke, they revealed an inconsistency.'
-  \b. * Ungrammatical Filler (Singular Verb) \label{ex:ung_filler}\\
+  \b. * \textsc{Ungrammatical Filler (Singular Verb)} \label{ex:ung_filler}\\
   \gll [Dans\"{o}z-\"{u}n \textbf{koca-s{\i}}] var-{\i}nca kap{\i} sakince \textbf{a\c{c}-t{\i}}. \\
@@
 
-In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect we analyzed the data from the present experiment together with \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data, using the experiment as an additional factor in the analysis.
+In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect, we analyzed the data from the present experiment compared our results to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) results, by including \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data in our Bayesian GLM and using the experiment as an additional factor in the analysis.
 

### 2021-11-06 R/analysis/04_bayesian_models.R

@@ -16,20 +16,44 @@ models <- c()
 
 n_chains <- 4
 n_cores <- 4
-n_iter <- 2000
-n_warmup <- 1000
+n_iter <- 20000
+n_warmup <- 2000
 
-fname_responses <- "./R/fits/responses"
-fname_responses_stan <- "./R/models/responses.stan"
-m_responses <- brm(ResponseYes ~ cEndsInConsonant * cGrammatical * cAttractorPlural + 
-                                 (cGrammatical * cAttractorPlural + 1| subject) + 
-                                 (cGrammatical * cAttractorPlural + 1| item),
-                   data = df_merged_nofillers,
-                   family = bernoulli("probit"), 
-                   chains = n_chains, cores = n_cores, iter = n_iter, warmup = n_warmup, init_r = .1,
-                   file = fname_responses, save_model = fname_responses_stan)
 
-models[['responses']] <- m_responses
+
+# formula_null <- ResponseYes ~ cGrammatical * cAttractorPlural +
+#                               (cGrammatical * cAttractorPlural + 1| subject) +
+#                               (cGrammatical * cAttractorPlural + 1| item)
+
+# priors_null <- c(
+#   set_prior("student_t(3,0,2.5)", class = "Intercept"),
+#   set_prior("normal(0,1)", class = "b", coef = "cAttractorPlural"),
+#   set_prior("normal(0,1)", class = "b", coef = "cGrammatical"),
+#   set_prior("normal(0,1)", class = "b", coef = "cGrammatical:cAttractorPlural"),
+#   set_prior("cauchy(0,1)", class = "sd"),
+#   set_prior("lkj(2)", class = "cor")
+# )
+
+
+
+fname_responses_full <- "./R/fits/responses_full"
+fname_responses_full_stan <- "./R/models/responses_full.stan"
+m_responses_full <- brm(ResponseYes ~ cEndsInConsonant * cGrammatical * cAttractorPlural + 
+                                      (cGrammatical * cAttractorPlural + 1| subject) + 
+                                      (cGrammatical * cAttractorPlural + 1| item),
+                    data = df_merged_nofillers,
+                    prior = c(
+                              prior(normal(0,1), class = Intercept),
+                              prior(normal(0,1), class = b),
+                              prior(normal(0,1), class = sd),
+                              prior(lkj(2), class = cor)
+                              ),
+                    family = bernoulli("probit"), 
[…]

### 2021-11-06 R/analysis/05_model_plots.R

@@ -7,7 +7,7 @@ contrast_names <- c("cGrammatical" = "Grammaticality",
                     "cEndsInConsonant:cGrammatical:cAttractorPlural" = "Ambiguity * Grammaticality * Plural Attractor")
 
 p_m_response <- 
-  create_model_coefs_plot( m_responses, 
+  create_model_coefs_plot( m_responses_full, 
         plot_stats = T, map_names = contrast_names,
         expand_right = 2.5, expand_top = 1.4, x_stat_adjust = 1.1,
         x_breaks = -1:4 ) + 

### 2021-11-06 R/analysis/06_text_inputs.R

@@ -26,9 +26,9 @@ min_age <- min(form_exp1$Age)
 max_age <- max(form_exp1$Age)
 m_effect <- sprintf("%0.2f", exp1_cur_entry1$M-exp1_cur_entry2$M)
 m_effect_lago <- sprintf("%0.2f", lago_cur_entry1$M-lago_cur_entry2$M)
-estimate_cGrammatical <- print_estimate_with_ci( m_responses, 'cGrammatical' )
-estimate_cGrammatical_cAttractorPlural <- print_estimate_with_ci( m_responses, 'cGrammatical:cAttractorPlural')
-estimate_threeway_interaction <- print_estimate_with_ci( m_responses, 'cEndsInConsonant:cGrammatical:cAttractorPlural')
+estimate_cGrammatical <- print_estimate_with_ci( m_responses_full, 'cGrammatical' )
+estimate_cGrammatical_cAttractorPlural <- print_estimate_with_ci( m_responses_full, 'cGrammatical:cAttractorPlural')
+estimate_threeway_interaction <- print_estimate_with_ci( m_responses_full, 'cEndsInConsonant:cGrammatical:cAttractorPlural')
 
 estimate_ungramResp_cAmbiguity_cAttractorPlural <- print_estimate_with_ci(m_ungram_responses, 'cEndsInConsonant:cAttractorPlural')
 estimate_ungramResp_cAttractorPlural <- print_estimate_with_ci(m_ungram_responses, 'cAttractorPlural')

### 2021-11-06 paper/glossa/manuscript-knitr.Rnw

@@
 
-\newcommand{\revise}[1]{\textcolor{red}{#1}}
-
-<<wordcount, echo=FALSE, cache=FALSE>>=
-library(knitr)
-
-comma <- function (x, ...) {
-  format(x, ..., big.mark = ",", scientific = FALSE, trim = TRUE)
-}
-
-# To dynamically extract name of the current file, use code below
-nameoffile <- 'manuscript-knitr.Rnw' # get name of file
-nof2 <-  strsplit(nameoffile,"\\.")[[1]][1] # extract name, drop extension
-noftex <- paste(nof2, ".tex", sep="") # add .tex extension
-nofwordcount <-  paste(nof2, '-','wordcount', '.tex', sep = "") # prepare a tex file for word count
-if (file.exists(nofwordcount)) {unlink(nofwordcount)} #delete the previous file.
-
-con <- file(noftex, open = 'r') # open the file with R
-while(TRUE) {
-  line <- readLines(con, n = 1) # read lines
-  if(length(line) == 0) break # pass if nothing is there
-  else if(!endsWith(line, "%exclude")){ # if the line does not end with %exclude 
-    write(line, file = nofwordcount, append = TRUE) # write it to the new file
-  } 
-}
-close(con)
-
-systemcall <- paste("system('texcount -inc -incbib -total -sum ", nofwordcount, "', intern=TRUE)", sep="") # paste together texcount system command
-texcount.out <- eval(parse(text=systemcall)) # run texcount on current last compiled .tex file with edits
-
-sum.row <- grep("Sum count", texcount.out, value=TRUE) # extract row
-pattern <- "(\\d)+" # regex pattern for digits
-
-count <- regmatches(sum.row, regexpr(pattern, sum.row) )
-# extract digits
-
-count <- comma(as.numeric(count)) # add comma
-
-@
-
 % \pdf* commands provide metadata for the PDF output. ASCII characters only!
-\pdfauthor{A.A and B.B}
+\pdfauthor{Utku Turk and Pavel Logacev}
 \pdftitle{Agreement Attraction in Turkish}
@@
 This discrepancy has been hypothesized to be a result of the association between genitive case marking and subjecthood in Turkish, but not in English.
-In the present research, we test an alternative explanation in which Turkish \revise{number} agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
-\revise{When this ambiguity leads to erroneous processing, participants may end up with representations where the head noun is processed as an object of an embedded clause.
-Thus, w}e hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
+In the present research, we test an alternative explanation in which Turkish number agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
+We hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
 To test this hypothesis, we conducted a speeded acceptability judgment experiment and our results suggest that case-ambiguity does not play a role in agreement attraction, and thus lends credibility to the claim that genitive noun phrases may function as attractors in Turkish due to the association between genitive case and subjecthood.
@@
 
-People often fail to accurately process grammatical dependencies between different parts of a sentence \citep[e.g.,][]{GibsonThomas:1999,PhillipsEtAl:2011}.
-For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the \revise{agreement-wise irrelevant} attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed \revise{by} \textit{key}.
+Speakers often fail to accurately process grammatical dependencies between different parts of a sentence \citep[e.g.,][]{GibsonThomas:1999,PhillipsEtAl:2011}.
+For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the agreement-wise irrelevant attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed by \textit{key}.
 A number of previous studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999, WagersEtAl:2009} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with a singular attractor.
@@
 
-\citet{LagoEtAl:2019} demonstrated that genitive possessors (such as \textit{painters} in \textit{the painters' rival}) cause agreement attraction effects in Turkish.
+\citet{LagoEtAl:2019} demonstrated that genitive possessors (such as \textit{painters} in \textit{the painters' rival}) effect agreement attraction effects in Turkish.
 However, this finding appears to be at odds with \citeauthor{NicolEtAl:2016}'s (\citeyear{NicolEtAl:2016}) results, who failed to find a similar effect in English.
@@
 
-In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of case syncretism in the experimental sentences in their experiment, as a result of which all subject head nouns were ambiguous between possessive and accusative case.
+In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of local ambiguity in the experimental sentences in their experiment, as a result of which all subject head nouns were ambiguous between possessive and accusative case.
 
@@
 Turkish is an SOV word order language with overt case marking \citep{GokselKerslake:2005,Kornfilt:2011,Kornfilt:2013}. 
-For example, the possessor in the Turkish equivalent of the Saxon Genitive in \ref{ex:possgenex} is marked with genitive case, while the head noun is marked with possessive marker.
-Importantly, the possessive case marker \revise{is syncretic with} the accusative case marker when the noun stem ends in a consonant: 
+For example, the possessor in the Turkish construction in \ref{ex:possgenex}, which is similar to the Saxon Genitive, is marked with genitive case, while the head noun is marked with possessive case. 
+Importantly, the possessive case marker coincides in form with the accusative case marker when the noun stem ends in a consonant: 
 This is because in Turkish, case markers have different forms depending on whether the last sound of the stem is a vowel.
@@
 \citet{LagoEtAl:2019} argue that this erroneous retrieval may be facilitated by the genitive case marking on the attractor, because genitive NPs can function as subjects of embedded clauses in Turkish.
-Due to the ubiquity of genitive subjects, attractors marked with genitive case a priori likely to be agreement controllers.
+Due to the ubiquity of genitive subjects, attractors marked with genitive case are a priori likely to be agreement controllers.
 
-However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{e\u{g}itmen-i} (\textit{`instructor'}) in \ref{ex:lago} were consonant-ending, which made them locally ambiguous between possessive and accusative case \citep[pp.
-66--67]{GokselKerslake:2005} because the surface form of both, the possessive and accusative case is \textit{-i}.
+However, a potential problem with the stimuli in the \citet{LagoEtAl:2019} study is that the stems of all head nouns such as \textit{e\u{g}itmen-i} (\textit{`instructor'}) in \ref{ex:lago} were consonant-ending, making their possessive forms ambiguous between possessive and accusative case due to case syncretism between them in vowel-ending stems \citep[pp.
+66--67]{GokselKerslake:2005}.
+%because the surface form of both, the possessive and accusative case is \textit{-i}. 
+%locally
+As a result, the head noun (\textit{'instructor'}) in \ref{ex:ambiguous} can be disambiguated towards possessive case as in \ref{ex:ambiguous_possessive}, or towards accusative case as in \ref{ex:ambiguous_accusative}, where the genitive-marked noun functions as an embedded subject, and the matrix subject is omitted due to pro-drop.
+
+\ex.
+\label{ex:ambiguous}
+  \a. \textsc{Possessive Interpretation} \label{ex:ambiguous_possessive} \\
+  \gll Teknisyen-in e\u{g}itmen-i ko\c{s}-tu.\\
+       technician-\textsc{gen} instructor-\textsc{poss} run-\textsc{pst}\\
+  \glt `The technician's instructor ran.'
+  \b. \textsc{Accusative Interpretation} \label{ex:ambiguous_accusative}\\
+  \gll Teknisyen-in e\u{g}itmen-i kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
+  technician-\textsc{gen} instructor-\textsc{poss} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
+  \glt `I saw the technician firing the fast.'
+
+%{\color{red}
+%\ex. %Ambiguous Part 
+%\label{ex:ambiguous}\\
+%\gll Teknisyen-in e\u{g}itmen-i ola\u{g}an{\"u}st{\"u} h{\i}zl{\i} \ldots \\
+%technician-\textsc{gen} instructor-\textsc{poss} extraordinarily fast \ldots \\
+%  \a. Simplex Sentence \label{ex:simplexreading} \\
+%  \gll \ldots{} ko\c{s}-tu.\\
+%  \ldots{} run-\textsc{pst}\\
+%  \glt `The technician's instructor extraordinarily fast ran.'
+%  \b. Embedded Sentence \label{ex:embeddedreading}\\
+%  \gll \ldots{} kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
+%  \ldots{} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
+%  \glt `I saw the technician firing the instructor really fast.'
+%}
+
+Because accusative NPs cannot function as subjects in Turkish, it is possible that Lago et al.'s finding of agreement attraction effects in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the head nouns' \textit{reduced association with subjecthood} due to its ambiguity.
+%This ambiguity stems from the fact that the genitive case can serve as an embedded subject marker, and the accusative case can surface as \textit{-i}. 
+% For example, on some trials, 
+Because sentences like \ref{ex:lago} are locally ambiguous, participants may initially adopt an incorrect analysis of the genitive-possessive structure on some trials, and encode the genitive-marked first noun as the subject of an embedded verb and the ambiguous second noun as an accusative object.
+Under the assumption that remnants of an incorrect analysis affect the parsing process even after after a successful reanalysis \citep{Staub:2007}, the initial association between the genitive noun phrase and subjecthood may lead an agreement attraction effect.
+In contrast, this account predicts that the agreement attraction effect should be either significantly reduced or entirely absent when the head noun is unambiguous, as the function of the genitive noun phrase is disambiguated early, thus preventing potential digging-in effects \citep{Tabor:2004}.
 %
-
-Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due \revise{to} case syncretism between possessive and accusative.
-\revise{Because of this syncretism, there are two possible structures that readers may entertain upon reading the first two NPs.
-Consider \ref{ex:ambiguous} which can be represented with two different structures depending on the possible endings, which are shown in \ref{ex:simplexreading} and \ref{ex:embeddedreading}.}
-
-{\color{red}
-\ex. Ambiguous Part \label{ex:ambiguous}\\
-\gll Teknisyen-in e\u{g}itmen-i ola\u{g}an{\"u}st{\"u} h{\i}zl{\i} \ldots \\
-technician-\textsc{gen} instructor-\textsc{poss} extraordinarily fast \ldots \\
-  \a. Simplex Sentence \label{ex:simplexreading} \\
-  \gll \ldots{} ko\c{s}-tu.\\
-  \ldots{} run-\textsc{pst}\\
-  \glt `The technician's instructor extraordinarily fast ran.'
-  \b. Embedded Sentence \label{ex:embeddedreading}\\
-  \gll \ldots{} kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
-  \ldots{} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
-  \glt `I saw the technician firing the instructor really fast.'
-
-}
-
-\revise{This ambiguity stems from the fact that the genitive case can serve as an embedded subject marker, and the accusative case can surface as \textit{-i}.
-In some trials, participants may erroneously encode the genitive case on the first noun as a subject marker, and the \textit{-i} marked the second noun as an object.
-We hypothesize that the head noun will not be treated as a subject in those trials until a possible reanalysis after reading the matrix verb.
+%the head noun will arguably not be treated as a subject until a possible reanalysis after reading the matrix verb.
 We expect this reduced association to be reflected as an overall decrease in accuracy in grammatical conditions.
@@
 However, in ungrammatical conditions in which the matrix verb has an overt plural marker, we expect to have an easier interference of a plural marked Genitive NP which was recently encoded as a subject and an overall decrease in the accuracy.
+%
 We tested this hypothesis in a speeded-acceptability experiment with sentences similar to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}), but with unambiguously marked vowel-ending head nouns.
-We expect that the agreement attraction effect may arise specifically on trials where participants misparse the two initial NP cases and where the sentence contains a plural attractor with a plural verb.
-On trials where participants misparse the two initial NP cases, but the sentence does not have a plural attractor or a plural verb, we expect overall higher errors without the specific effect of a plural attractor.}
+%We expect that the agreement attraction effect may arise specifically on trials where participants misparse the two initial NP cases and where the sentence contains a plural attractor with a plural verb.
+On trials where participants misparse the two initial NP cases, but the sentence does not have a plural attractor or a plural verb, we expect overall higher errors without the specific effect of a plural attractor.
+%}
 
@@
 
-In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect, we analyzed the data from the present experiment \revise{compared our results to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) results, by including \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data in our Bayesian GLM and} using the experiment as an additional factor in the analysis.
+In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect, we analyzed the data from the present experiment compared our results to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) results, by including \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data in our Bayesian GLM and using the experiment as an additional factor in the analysis.
 

### 2021-11-06 paper/glossa/manuscript-knitr.tex

@@
 
-\newcommand{\revise}[1]{\textcolor{red}{#1}}
-
 % \pdf* commands provide metadata for the PDF output. ASCII characters only!
-\pdfauthor{A.A and B.B}
+\pdfauthor{Utku Turk and Pavel Logacev}
 \pdftitle{Agreement Attraction in Turkish}
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,296}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3303}
 
-\newcommand{\firstauthor}{{A.A.}}
-\newcommand{\firstauthorshort}{{A.A.}}
-\newcommand{\secondauthor}{{B.B.}}
-\newcommand{\secondauthorshort}{{B.B.}}
+\newcommand{\firstauthor}{{Utku T\"urk}}
+\newcommand{\firstauthorshort}{{T\"urk}}
+\newcommand{\secondauthor}{{Pavel Loga\v{c}ev}}
+\newcommand{\secondauthorshort}{{Loga\v{c}ev}}
 
-\author[\firstauthor \& \secondauthor]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
+\author[\firstauthorshort \& \secondauthorshort]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
 {%as many authors as you like, each separated by \AND.
-  \spauthor{\texttt{Hidden Hidden (\firstauthor)}\\ 
-  \institute{\texttt{Hidden University}}\\
+  \spauthor{\firstauthor\\ 
+  \institute{Bo\u{g}azi\c{c}i University}\\
   \small{
-    \texttt{hidden@hidden.edu}}
+    \texttt{utku.turk@boun.edu.tr}}
   }
   \AND
-  \spauthor{\texttt{Hidden Hidden (\secondauthor)}\\ 
-  \institute{\texttt{Hidden University}}\\
+  \spauthor{\secondauthor\\ 
+  \institute{Bo\u{g}azi\c{c}i University}\\
   \small{
-    \texttt{hidden@hidden.edu}}
+    \texttt{pavel.logacev@boun.edu.tr}}
   }%
@@
 All participants were native Turkish speakers, with an average age of 20 (range: 18 -- 32).
-The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at \texttt{Hidden University}.
+The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at Bo\u{g}azi\c{c}i University.
 All participants provided informed consent before their participation and their identity are completely anonimized.
@@
 In the results section, we provide summaries of the coefficient posterior distributions.
-For our model, we ran 4 chains with 1000 warm-up iterations and 1000 sampling iterations.
+For our model, we ran 4 chains with 2000 warm-up iterations and \ensuremath{1.8\times 10^{4}} sampling iterations.
 The data for our study, along with our analysis scripts can be found \url{hhttps://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}.
@@
 Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function.
-The main effect of grammaticality ($\hat{\beta}=3.09;$ $CI=[2.85; 3.35];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.03; -0.43];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
-There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.28;$ $CI=[-0.78; 0.23];$ $P(\beta<0)=    .86$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments (0.11).
+The main effect of grammaticality ($\hat{\beta}=3.04;$ $CI=[2.79; 3.29];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.72;$ $CI=[-1.00; -0.44];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
+There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.24;$ $CI=[-0.72; 0.25];$ $P(\beta<0)=    .83$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments (0.11).
 This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor (($\hat{\beta}=0.01;$ $CI=[-0.31; 0.33];$ $P(\beta<0)=    .46$).

### 2021-11-06 paper/glossa/manuscript-knitr.Rnw
osf2

@@
 For our model, we ran \Sexpr{n_chains} chains with \Sexpr{n_warmup} warm-up iterations and \Sexpr{n_iter-n_warmup} sampling iterations.
-The data for our study, along with our analysis scripts can be found \url{hhttps://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}.
+The data for our study, along with our analysis scripts can be found \url{https://osf.io/hegmd/}.
 
@@
 
-The data that support the findings of this study, the code, and the paper resources including \LaTeX{} and \texttt{Sweave} files are openly available in the anonimized github page at \url{https://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}.
-%exclude
+All data and R code used in the data analysis is available at \url{https://osf.io/hegmd/}. %exclude
 

### 2021-11-06 paper/glossa/manuscript-knitr.tex
osf2

@@
 For our model, we ran 4 chains with 2000 warm-up iterations and \ensuremath{1.8\times 10^{4}} sampling iterations.
-The data for our study, along with our analysis scripts can be found \url{hhttps://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}.
+The data for our study, along with our analysis scripts can be found \url{https://osf.io/hegmd/}.
 

### 2022-02-10 paper/glossa/manuscript-knitr.Rnw
lcn-revision

--- 2021-10-17 paper/glossa/manuscript-knitr.Rnw
@@
 \usepackage[linguistics]{forest}
-
-\newcommand{\revise}[1]{\textcolor{red}{#1}}
 
@@
 This discrepancy has been hypothesized to be a result of the association between genitive case marking and subjecthood in Turkish, but not in English.
-In the present research, we test an alternative explanation in which Turkish \revise{number} agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
-\revise{When this ambiguity leads to erroneous processing, participants may end up with representations where the head noun is processed as an object of an embedded clause.
-Thus, w}e hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
+In the present research, we test an alternative explanation in which Turkish agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
+We hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
 To test this hypothesis, we conducted a speeded acceptability judgment experiment and our results suggest that case-ambiguity does not play a role in agreement attraction, and thus lends credibility to the claim that genitive noun phrases may function as attractors in Turkish due to the association between genitive case and subjecthood.
@@
 People often fail to accurately process grammatical dependencies between different parts of a sentence \citep[e.g.,][]{GibsonThomas:1999,PhillipsEtAl:2011}.
-For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the \revise{agreement-wise irrelevant} attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed \revise{by} \textit{key}.
-A number of previous studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999, WagersEtAl:2009} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with a singular attractor.
+For example, in \ref{ex:pearlmutter}, the auxiliary verb \textit{were} erroneously agrees with the syntactically unrelated attractor noun phrase headed by \textit{cabinets} instead of the agreement controller headed \textit{key}.
+A number of previous  studies in comprehension \citep{NicolEtAl:1997, PearlmutterGarnseyBock:1999} showed that participants found sentences like \ref{ex:pearlmutter} acceptable more often and read them faster compared to their counterparts with a singular attractor.
 This phenomenon, known as \textit{agreement attraction} \citep{BockMiller:1991} has been attested in a number of languages, such as in Arabic \citep{TuckerEtAl:2015}, Armenian \citep{AvetisyanEtAl:2020}, German \citep{LagoFelser:2018}, Hindi \citep{BhatiaDillon:2020}, Serbian \citep{RisticEtAl:2016}, Slovak \citep{BadeckerKuminiak:2007}, Spanish \citep{LagoEtAl:2015}, and recently in Turkish \citep{LagoEtAl:2019}.
@@
 \citet{LagoEtAl:2019} hypothesize that Turkish possessor noun phrases, unlike their English counterparts, may function as agreement attractors because Turkish genitive NPs may function as subjects of non-finite clauses in Turkish \citep{GokselKerslake:2005,Kornfilt:2011}.
-As a result, Turkish genitive NPs may match the subjecthood feature used in the cue-based retrieval of a verb's subject \citep{LewisVasishth:2005, WagersEtAl:2009, ArnettWagers:2017}.
+As a result, Turkish genitive NPs may match the subjecthood feature used in the cue-based retrieval of a verb's subject \citep{LewisVasishth:2005, ArnettWagers:2017}.
 
@@
 For example, the possessor in the Turkish equivalent of the Saxon Genitive in \ref{ex:possgenex} is marked with genitive case, while the head noun is marked with possessive marker.
-Importantly, the possessive case marker \revise{is syncretic with} the accusative case marker when the noun stem ends in a consonant: 
+Importantly, the possessive case marker coincides in form with the accusative case marker when the noun stem ends in a consonant: 
 This is because in Turkish, case markers have different forms depending on whether the last sound of the stem is a vowel.
@@
 %
-
-Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due \revise{to} case syncretism between possessive and accusative.
-\revise{Because of this syncretism, there are two possible structures that readers may entertain upon reading the first two NPs.
-Consider \ref{ex:ambiguous} which can be represented with two different structures depending on the possible endings, which are shown in \ref{ex:simplexreading} and \ref{ex:embeddedreading}.}
-
-{\color{red}
-\ex. Ambiguous Part \label{ex:ambiguous}\\
-\gll Teknisyen-in e\u{g}itmen-i ola\u{g}an{\"u}st{\"u} h{\i}zl{\i} \ldots \\
-technician-\textsc{gen} instructor-\textsc{poss} extraordinarily fast \ldots \\
-  \a. Simplex Sentence \label{ex:simplexreading} \\
-  \gll \ldots{} ko\c{s}-tu.\\
-  \ldots{} run-\textsc{pst}\\
-  \glt `The technician's instructor extraordinarily fast ran.'
-  \b. Embedded Sentence \label{ex:embeddedreading}\\
-  \gll \ldots{} kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
-  \ldots{} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
-  \glt `I saw the technician firing the instructor really fast.'
-
-}
-
-\revise{This ambiguity stems from the fact that the genitive case can serve as an embedded subject marker, and the accusative case can surface as \textit{-i}.
-In some trials, participants may erroneously encode the genitive case on the first noun as a subject marker, and the \textit{-i} marked the second noun as an object.
-We hypothesize that the head noun will not be treated as a subject in those trials until a possible reanalysis after reading the matrix verb.
-We expect this reduced association to be reflected as an overall decrease in accuracy in grammatical conditions.
-Upon reading the verb, participants will either find the sentence ungrammatical since they have expected a structure similar to \ref{ex:embeddedreading} or reanalyze the sentence and will judge the sentence according to the structure in \ref{ex:simplexreading}.
-Since there is no plural marker at the matrix verb, the plural on the attractor will not have an additional effect.
-However, in ungrammatical conditions in which the matrix verb has an overt plural marker, we expect to have an easier interference of a plural marked Genitive NP which was recently encoded as a subject and an overall decrease in the accuracy.
+Because accusative NPs cannot function as subjects in Turkish, it is possible that the agreement attraction effects found in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the \textit{head nouns' reduced association with subjecthood} due case syncretism between possessive and accusative.
 We tested this hypothesis in a speeded-acceptability experiment with sentences similar to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}), but with unambiguously marked vowel-ending head nouns.
-We expect that the agreement attraction effect may arise specifically on trials where participants misparse the two initial NP cases and where the sentence contains a plural attractor with a plural verb.
-On trials where participants misparse the two initial NP cases, but the sentence does not have a plural attractor or a plural verb, we expect overall higher errors without the specific effect of a plural attractor.}
 
@@
 
-In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect, we analyzed the data from the present experiment \revise{compared our results to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) results, by including \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data in our Bayesian GLM and} using the experiment as an additional factor in the analysis.
+In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect we analyzed the data from the present experiment together with \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data, using the experiment as an additional factor in the analysis.
 
@@
 
-\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{nmlz} = nominalizer, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular, \textsc{when} = when.
-%exclude
+\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular, \textsc{when} = when. %exclude
 

### 2022-02-10 paper/glossa/manuscript-knitr.tex
lcn-revision

--- 2021-10-17 paper/glossa/manuscript-knitr.tex
@@
 
-\newcommand{\revise}[1]{\textcolor{red}{#1}}
-
 % \pdf* commands provide metadata for the PDF output. ASCII characters only!
@@
 
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3,296}
+\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 2,933}
 
@@
 Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function.
-The main effect of grammaticality ($\hat{\beta}=3.09;$ $CI=[2.85; 3.35];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.03; -0.43];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
-There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.28;$ $CI=[-0.78; 0.23];$ $P(\beta<0)=    .86$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments (0.11).
-This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor (($\hat{\beta}=0.01;$ $CI=[-0.31; 0.33];$ $P(\beta<0)=    .46$).
+The main effect of grammaticality ($\hat{\beta}=3.08;$ $CI=[2.84; 3.33];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.04; -0.42];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
+There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.27;$ $CI=[-0.77; 0.25];$ $P(\beta<0)=    .85$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments ().
+This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor (($\hat{\beta}=0.01;$ $CI=[-0.32; 0.33];$ $P(\beta<0)=    .48$).
 It also showed a main effect of plural attractor ($\hat{\beta}=0.46;$ $CI=[0.26; 0.65];$ $P(\beta<0)< .001$).

### 2022-02-10 paper/lcn_revision/manuscript-knitr.Rnw
lcn-revision

--- 2021-11-06 paper/glossa/manuscript.Rnw
@@
-\documentclass[apacite,linguex]{glossa}
+% interactapasample.tex
+% v1.05 - August 2017
+
+\documentclass[]{interact}
+
+\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
+\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
+%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required
+\usepackage[doublespacing]{setspace}% To produce a `double spaced' document if required
+\setlength\parindent{24pt}% To increase paragraph indentation when line spacing is doubled
+
+\usepackage{tikz,xcolor,hyperref}
+
+% Make Orcid icon
+\definecolor{lime}{HTML}{A6CE39}
+\DeclareRobustCommand{\orcidicon}{%
+	\begin{tikzpicture}
+	\draw[lime, fill=lime] (0,0) 
+	circle [radius=0.16] 
+	node[white] {{\fontfamily{qag}\selectfont \tiny ID}};
+	\draw[white, fill=white] (-0.0625,0.095) 
+	circle [radius=0.007];
+	\end{tikzpicture}
+	\hspace{-2mm}
+}
+
+\foreach \x in {A, ..., Z}{%
+	\expandafter\xdef\csname orcid\x\endcsname{\noexpand\href{https://orcid.org/\csname orcidauthor\x\endcsname}{\noexpand\orcidicon}}
+}
+
+% Define the ORCID iD command for each author separately. Here done for two authors.
+\newcommand{\orcidauthorA}{0000-0001-8011-1541}
+\newcommand{\orcidauthorB}{0000-0002-2837-2258}
+
+%\usepackage[longnamesfirst,sort]{natbib}% Citation support using natbib.sty
+%\bibliographystyle{unsrtnat}
+%\bibpunct[, ]{(}{)}{;}{a}{,}{,}% Citation support using natbib.sty
+%\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% To set the list of references in 10 point font using natbib.sty
+
+\usepackage[natbibapa,nodoi]{apacite}% Citation support using apacite.sty. Commands using natbib.sty MUST be deactivated first!
+\setlength\bibhang{12pt}% To set the indentation in the list of references using apacite.sty. Commands using natbib.sty MUST be deactivated first!
+%\let\cite\shortcite
+
+\renewcommand\bibliographytypesize{\fontsize{10}{12}\selectfont}% To set the list of references in 10 point font using apacite.sty. Commands using natbib.sty MUST be deactivated first!
+
+\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}[theorem]{Proposition}
+
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
+
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}
+\newtheorem{notation}{Notation}
 
@@
 \usepackage[linguistics]{forest}
+\usepackage{linguex}
+\renewcommand{\firstrefdash}{}%
+\AtBeginDocument{\settowidth{\Exlabelwidth}{(110)}}
+\RequirePackage{cgloss} %for adding the language name and source of the example on the first line of glossed examples (requires \gll before the foreign language example and \glt before the translation)
 
-% \pdf* commands provide metadata for the PDF output. ASCII characters only!
-\pdfauthor{Utku Turk and Pavel Logacev}
-\pdftitle{Agreement Attraction in Turkish}
-\pdfkeywords{agreement attraction, syncretism, Turkish, bayesian, replication}
-
-\title[Agreement Attraction in Turkish]{Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3303}
-
-\newcommand{\firstauthor}{{Utku T\"urk}}
-\newcommand{\firstauthorshort}{{T\"urk}}
-\newcommand{\secondauthor}{{Pavel Loga\v{c}ev}}
-\newcommand{\secondauthorshort}{{Loga\v{c}ev}}
-
-\author[\firstauthorshort \& \secondauthorshort]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
-{%as many authors as you like, each separated by \AND.
-  \spauthor{\firstauthor\\ 
-  \institute{Bo\u{g}azi\c{c}i University}\\
-  \small{
-    \texttt{utku.turk@boun.edu.tr}}
-  }
-  \AND
-  \spauthor{\secondauthor\\ 
-  \institute{Bo\u{g}azi\c{c}i University}\\
-  \small{
-    \texttt{pavel.logacev@boun.edu.tr}}
-  }%
-}
+\newcommand{\rev}[1]{{\color{red}#1}}
 
@@
 
-\SweaveOpts{concordance=TRUE}
+\articletype{Short Article}% Specify the article type or omit as appropriate
 
-\sffamily
+\title{Agreement Attraction in Turkish: The Case of Genitive Attractors}
+
+\author{
+\name{Utku T\"{u}rk\textsuperscript{a}\orcidA{}\thanks{CONTACT Utku T\"{u}rk. Email: utkuturk@pm.me} and Pavel Loga\v{c}ev\textsuperscript{a}\orcidB{}}
+\affil{\textsuperscript{a}Bo\u{g}azi\c{c}i University, \.{I}stanbul, Turkey}
+}
+
 \maketitle
@@
 \begin{abstract}
-
-Previous studies have shown that speakers may find sentences violating subject-verb agreement grammatical when the sentence contains a feature-matching noun phrase.
-This so-called agreement attraction effect has also been found in genitive possessive structures such as \textit{'the teacher's brother'} in Turkish (Lago et al., 2019), which is in contrast with its absence in similar constructions in English (Nicol et al., 2016).
-This discrepancy has been hypothesized to be a result of the association between genitive case marking and subjecthood in Turkish, but not in English.
-In the present research, we test an alternative explanation in which Turkish number agreement attraction effects are due to a potential confound in Lago et al.'s experiment, as a result of which subject head nouns were locally ambiguous between the possessive and the accusative case.
-We hypothesized that this ambiguity may have inhibited the availability of the head noun as an agreement controller as the accusative is a non-subject case in Turkish.
-To test this hypothesis, we conducted a speeded acceptability judgment experiment and our results suggest that case-ambiguity does not play a role in agreement attraction, and thus lends credibility to the claim that genitive noun phrases may function as attractors in Turkish due to the association between genitive case and subjecthood.
-%exclude
+Speakers have been shown to find sentences with erroneous agreement acceptable under certain conditions.
+This so-called agreement attraction effect has also been found in genitive-possessive structures such as \textit{``the teacher's brother''} in Turkish (Lago et al., 2019), which is in contrast to its absence in similar constructions in English (Nicol et al., 2016).
+It has been hypothesized that this discrepancy is a result of the association between genitive case marking and subjecthood in Turkish.
+We test an alternative explanation according to which Lago et al.'s findings are due to a potential confound in their experiment, as all subject head nouns were locally ambiguous between possessive and accusative case.
+The results of our speeded acceptability judgment experiment suggest that the presence of case ambiguity does not affect agreement attraction, and thus suggests that genitive NPs may function as attractors in Turkish due to the association between genitive case and subjecthood.
 
@@
 \begin{keywords}
-agreement attraction; syncretism; Turkish; bayesian; replication
+Agreement attraction; syncretism; Turkish; \rev{sentence processing; number}
 \end{keywords}
-
-\rmfamily
 
@@
 
-In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of local ambiguity in the experimental sentences in their experiment, as a result of which all subject head nouns were ambiguous between possessive and accusative case.
+In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of local ambiguity in \rev{their} experimental sentences, as a result of which all subject head nouns were ambiguous between possessive and accusative case.
 
@@
     technician-\textsc{gen} instructor-\textsc{poss} \\
-\glt `the instructor of the technician'
+\glt ``the instructor of the technician''
 
 \citet{LagoEtAl:2019} demonstrated an agreement attraction effect in Turkish genitive-possessive constructions in a speeded acceptability judgment study with sentences like \ref{ex:lago}, in which the number of the attractor and the verb was manipulated.
-The resulting $2$x$2$ design, indicated by brackets and slashes in \ref{ex:lago}, consisted of two grammatical conditions, in which the verb agreed with the singular subject head noun, and two ungrammatical conditions, in which the verb carried plural agreement, and thus did not agree with the subject.
+The resulting $2$x$2$ design, indicated by brackets and slashes in \ref{ex:lago}, consisted of two grammatical conditions, in which the verb agreed \rev{in number} with the singular subject head noun, and two ungrammatical conditions, in which the verb carried plural agreement, and thus did not agree with the subject.
 In ungrammatical sentences, they found a higher percentage of \textit{acceptable} responses when the genitive attractor was plural than when it was singular, indicating agreement attraction.
@@
 technician-\{\textsc{pl}/\textsc{sg}\}-\textsc{gen} instructor-\textsc{poss} extraordinarily fast run-\textsc{pst}-\{\textsc{pl}/\textsc{sg}\}\\
-\glt `The technician's/technicians' instructor extraordinarily fast ran\{\textsc{pl}/\textsc{sg}\}.'
+\glt ``The technician's/technicians' instructor \rev{ran\{\textsc{pl}/\textsc{sg}\}} extraordinarily fast.''
 
-\citet{LagoEtAl:2019} hypothesized that these effects originated from how case and number information is encoded and retrieved: According to \citeauthor{LewisVasishth:2005}'s (\citeyear{LewisVasishth:2005}) cue-based retrieval model, phrases are encoded in a content-addressable memory as bundles of features called \textit{chunks} which include information like number, gender, case, and syntactic function \citep[e.g.,][]{SmithVasishth:2020}.
+\citet{LagoEtAl:2019} hypothesized that these effects originated from how case and number information \rev{are} encoded and retrieved: According to \citeauthor{LewisVasishth:2005}'s (\citeyear{LewisVasishth:2005}) cue-based retrieval model, phrases are encoded in a content-addressable memory as bundles of features called \textit{chunks} which include information like number, gender, case, and syntactic function \citep[e.g.,][]{SmithVasishth:2020}.
 Under \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) proposal, participants predict the number of the verb based on the noun phrases they process while reading the subject.
@@
 66--67]{GokselKerslake:2005}.
-%because the surface form of both, the possessive and accusative case is \textit{-i}. 
-%locally
 As a result, the head noun (\textit{'instructor'}) in \ref{ex:ambiguous} can be disambiguated towards possessive case as in \ref{ex:ambiguous_possessive}, or towards accusative case as in \ref{ex:ambiguous_accusative}, where the genitive-marked noun functions as an embedded subject, and the matrix subject is omitted due to pro-drop.
+\rev{We also calculated the relative probability of having an accusative marked noun compared to an possessive marked noun following genitive marking.
+Data from annotated treebanks from Universal Dependencies v2.9 \citep{TurkEtAl2021,KuzgunEtAl2020,TurkEtAl2019b,SulubacakEtAl2016,Coltekin2015} showed that the relative probability of encountering accusative marking after the genitive-marked noun is \Sexpr{p_acc_given_gen}.}
 
@@
        technician-\textsc{gen} instructor-\textsc{poss} run-\textsc{pst}\\
-  \glt `The technician's instructor ran.'
+  \glt ``The technician's instructor ran.''
   \b. \textsc{Accusative Interpretation} \label{ex:ambiguous_accusative}\\
@@
   technician-\textsc{gen} instructor-\textsc{poss} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
-  \glt `I saw the technician firing the fast.'
-
-%{\color{red}
-%\ex. %Ambiguous Part 
-%\label{ex:ambiguous}\\
-%\gll Teknisyen-in e\u{g}itmen-i ola\u{g}an{\"u}st{\"u} h{\i}zl{\i} \ldots \\
-%technician-\textsc{gen} instructor-\textsc{poss} extraordinarily fast \ldots \\
-%  \a. Simplex Sentence \label{ex:simplexreading} \\
-%  \gll \ldots{} ko\c{s}-tu.\\
-%  \ldots{} run-\textsc{pst}\\
-%  \glt `The technician's instructor extraordinarily fast ran.'
-%  \b. Embedded Sentence \label{ex:embeddedreading}\\
-%  \gll \ldots{} kov-du\u{g}-un-u g\"{o}r-d\"{u}-m.\\
-%  \ldots{} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
-%  \glt `I saw the technician firing the instructor really fast.'
-%}
+  \glt ``I saw the technician firing the \rev{instructor}.''
 
 Because accusative NPs cannot function as subjects in Turkish, it is possible that Lago et al.'s finding of agreement attraction effects in sentences like \ref{ex:lago} are not due to the genitive attractors' association with subjecthood, but rather due to the head nouns' \textit{reduced association with subjecthood} due to its ambiguity.
-%This ambiguity stems from the fact that the genitive case can serve as an embedded subject marker, and the accusative case can surface as \textit{-i}. 
-% For example, on some trials, 
+
 Because sentences like \ref{ex:lago} are locally ambiguous, participants may initially adopt an incorrect analysis of the genitive-possessive structure on some trials, and encode the genitive-marked first noun as the subject of an embedded verb and the ambiguous second noun as an accusative object.
@@
 In contrast, this account predicts that the agreement attraction effect should be either significantly reduced or entirely absent when the head noun is unambiguous, as the function of the genitive noun phrase is disambiguated early, thus preventing potential digging-in effects \citep{Tabor:2004}.
-%
-%the head noun will arguably not be treated as a subject until a possible reanalysis after reading the matrix verb.
-We expect this reduced association to be reflected as an overall decrease in accuracy in grammatical conditions.
-Upon reading the verb, participants will either find the sentence ungrammatical since they have expected a structure similar to \ref{ex:embeddedreading} or reanalyze the sentence and will judge the sentence according to the structure in \ref{ex:simplexreading}.
-Since there is no plural marker at the matrix verb, the plural on the attractor will not have an additional effect.
-However, in ungrammatical conditions in which the matrix verb has an overt plural marker, we expect to have an easier interference of a plural marked Genitive NP which was recently encoded as a subject and an overall decrease in the accuracy.
-%
 We tested this hypothesis in a speeded-acceptability experiment with sentences similar to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}), but with unambiguously marked vowel-ending head nouns.
-%We expect that the agreement attraction effect may arise specifically on trials where participants misparse the two initial NP cases and where the sentence contains a plural attractor with a plural verb.
-On trials where participants misparse the two initial NP cases, but the sentence does not have a plural attractor or a plural verb, we expect overall higher errors without the specific effect of a plural attractor.
-%}
 
@@
   millionaire-\textsc{pl}-\textsc{gen} tailor-\textsc{poss} completely without.reason fire-\textsc{pass}-\textsc{pst}-\textsc{pl}\\
-  \glt `The millionaires' tailor were fired for no reason at all.'
+  \glt ``The millionaires' tailor were fired for no reason at all.''
   \b. \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{ex:expitem-plsg} \\
@@
   millionaire-\textsc{pl}-\textsc{gen} tailor-\textsc{poss} completely without.reason fire-\textsc{pass}-\textsc{pst}\\
-  \glt `The millionaires' tailor was fired for no reason at all.'
+  \glt ``The millionaires' tailor was fired for no reason at all.''
   \b. * \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{ex:expitem-sgpl}\\
@@
   millionaire-\textsc{gen} tailor-\textsc{poss} completely without.reason fire-\textsc{pass}-\textsc{pst}-\textsc{pl}\\
-  \glt `The millionaire's tailor were fired for no reason at all.'
+  \glt ``The millionaire's tailor were fired for no reason at all.''
   \b. \textsc{Singular Attractor Grammatical (Singular Verb)} \label{ex:expitem-sgsg}\\
@@
   millionaire-\textsc{gen} tailor-\textsc{poss} completely without.reason fire-\textsc{pass}-\textsc{pst}\\
-  \glt `The millionaire's tailor was fired for no reason at all.'
+  \glt ``The millionaire's tailor was fired for no reason at all.''
 
@@
 The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at Bo\u{g}azi\c{c}i University.
-All participants provided informed consent before their participation and their identity are completely anonimized.
+All participants provided informed consent before their participation and their identity \rev{were} completely anonimised.
 
@@
 
-All sentences started with a complex subject NP like \textit{milyonerlerin terzisi} `\textit{the millionaires' tailor},' in which the genitive possessor functioned as the attractor, and the head noun carried an unambiguous possessive case marker.
+All sentences started with a complex subject NP like \textit{milyonerlerin terzisi} ``\textit{the millionaires' tailor},'' in which the genitive possessor functioned as the attractor, and the head noun carried an unambiguous possessive case marker.
 Because the plural marking on nominals is not optional and the head noun was singular, absent of \textit{-lar}, in all conditions, sentences with plural verb agreement were ungrammatical.
@@
   sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{when} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}\\
-  \glt `When the student of the sociologist spoke, they revealed an inconsistency.'
+  \glt ``When the student of the sociologist spoke, they revealed an inconsistency.''
   \b. * \textsc{Ungrammatical Filler (Singular Verb)} \label{ex:ung_filler}\\
@@
   dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{when} door slowly  open-\textsc{pst}\\
-  \glt Intended:`When the husband of the dancer came, the door opened slowly.'
+  \glt Intended:``When the husband of the dancer came, the door opened slowly.''
 
@@
 
-In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect, we analyzed the data from the present experiment compared our results to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) results, by including \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data in our Bayesian GLM and using the experiment as an additional factor in the analysis.
+In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect, we analyzed the data from the present experiment \rev{and} compared our results to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) results, by including \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data in our Bayesian GLM and using the experiment as an additional factor in the analysis.
 
 Prior to the analysis, we removed the data for all participants who failed to show sufficient sensitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected.
-Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between the grammatical condition \ref{ex:expitem-sgsg} and the ungrammatical condition \ref{ex:expitem-sgpl} fell below the threshold of 0.25 percentage points.
-We also excluded trials in which the participants missed the response deadline or gave overly fast responses (below 200 ms).
-As a result, we excluded 10.22\% of the trials from our experiment and 2.38\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.
+Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between \rev{conditions with singular attractors \ref{ex:expitem-sgsg} and \ref{ex:expitem-sgpl}} fell below the threshold of \Sexpr{accuracy_threshold} percentage points.
+We also excluded trials in which the participants missed the response deadline.
+As a result, we excluded \rev{\Sexpr{perc_deletion_exp1}\%} of the trials from our experiment and \Sexpr{perc_deletion_lago}\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.
 
@@
 We analyzed only experimental sentences and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors.
-We used by-participant and by-item intercepts and slopes for all predictors.
-All factors were sum-coded. We have used standard priors provided by the brms package.
+We used by-participant and by-item intercepts and slopes for all predictors and \rev{their interaction}.
+All factors were sum-coded.
+\rev{A Student's \emph{t}-distribution ($\nu$ = 3, $\mu$ = 0, $\sigma$ = 2.5), a normal distribution ($\mu$ = 0, $\sigma$ = 1), a Cauchy distribution (($\mu$ = 0, $\sigma$ = 1)) and a LKJ distribution ($\eta$ = 2) were used for our intercept, slopes of predictors, standard deviations of random effects, correlation coefficients in interaction models respectively as priors.}
 
-Because the magnitude of the agreement attraction effect can be operationalized either as the interaction between grammaticality and the presence of a plural attractor, or as the effect of a plural attractor in ungrammatical sentences, we used a second model with predictors (ii) and (iii) and their interaction to analyze responses to ungrammatical conditions only.
+Because the magnitude of the agreement attraction effect can be operationalised either as the interaction between grammaticality and the presence of a plural attractor, or as the effect of a plural attractor in ungrammatical sentences, we used a second model with predictors (ii) and (iii) and their interaction to analyze responses to ungrammatical conditions only.
 
@@
 For our model, we ran \Sexpr{n_chains} chains with \Sexpr{n_warmup} warm-up iterations and \Sexpr{n_iter-n_warmup} sampling iterations.
-The data for our study, along with our analysis scripts can be found \url{https://osf.io/hegmd/}.
+The data for our study, along with our analysis scripts can be found at \url{https://osf.io/hegmd/}.
 
@@
 
-Figure \ref{fig:AverageResponses} shows the average proportions of `acceptable' responses by experimental condition in our experiment with unambiguous possessive marking, side by side with Lago et al.'s findings.
+Figure \ref{fig:AverageResponses} shows the average proportions of ``acceptable'' responses by experimental condition in our experiment with unambiguous possessive marking, side by side with Lago et al.'s findings.
 It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = \Sexpr{exp1_cur_entry1$M}, SE = \Sexpr{exp1_cur_entry1$SE}) than their counterparts with singular attractors (M = \Sexpr{exp1_cur_entry2$M}, SE=\Sexpr{exp1_cur_entry2$SE}).
@@
 
-\begin{figure}[hbt!]
-\centering
-
-<<AverageResponses, echo=FALSE, fig.align='center', height=3, dev = cairo_pdf, dpi = 300, message=FALSE>>=
+<<AverageResponses, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='The average percentage of acceptable responses according to the experimental conditions in our study and \\citet{LagoEtAl:2019}.
+Error bars signal standard errors calculated following \\citet{Morey:2008,Cousineau:2005}.'>>=
 
@@
 @
-
-\caption{The average percentage of acceptable responses according to the experimental conditions in our study and \citet{LagoEtAl:2019}.
-Error bars signal standard errors calculated following \citet{Morey:2008,Cousineau:2005}.}
-\label{fig:AverageResponses}
-\end{figure}
 
@@
 
-\begin{figure}[hbt!]
-\centering
-
-<<ResponseModel,  echo=FALSE, fig.align='center', height=3, warning=FALSE, dev = cairo_pdf, dpi = 300, message=FALSE>>=
+<<ResponseModel, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\\% credible intervals for the probit regression coefficients for the model of responses in our experiment and \\citet{LagoEtAl:2019}.'>>=
 
@@
 
-\caption{Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses in our experiment and \citet{LagoEtAl:2019}.}
-\label{fig:ResponseModel}
-\end{figure}
-
-\begin{figure}[hbt!]
-\centering
-
-<<ResponseModelUngram,  echo=FALSE, fig.align='center', height=1.5, warning=FALSE, dev = cairo_pdf, dpi = 300, message=FALSE>>=
+<<ResponseModelUngram, message = FALSE, echo=FALSE, warning = FALSE, dev='cairo_pdf', fig.height=1.5, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\\% credible intervals for the probit regression coefficients for the model of responses to \\protect{\\textbf{ungrammatical sentences}} in our experiment and \\citet{LagoEtAl:2019}.'>>=
 
@@
 @
-
-\caption{Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses to \protect{\textbf{ungrammatical sentences}} in our experiment and \citet{LagoEtAl:2019}.}
-\label{fig:ResponseModelUngram}
-\end{figure}
 
@@
 
-Our experimental findings were comparable to \citet{LagoEtAl:2019}: We observed that the presence of a plural attractor increased the rate of erroneous `acceptable' responses  
+Our experimental findings were comparable to \citet{LagoEtAl:2019}: We observed that the presence of a plural attractor increased the rate of erroneous ``acceptable'' responses  
 % increased the overall error rate
@@
 
-\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{nmlz} = nominalizer, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular, \textsc{when} = when.
+\textsc{dat} = dative, \textsc{gen} = genitive, \textsc{nmlz} = nominaliser, \textsc{pass} = passive, \textsc{pl} = plural, \textsc{poss} = possessive, \textsc{pst} = past, \textsc{sg} = singular, \textsc{when} = when.
 %exclude
-
-\section*{Data Availability} %exclude
-
-All data and R code used in the data analysis is available at \url{https://osf.io/hegmd/}. %exclude
 
@@
 
-{\firstauthor} conceived the initial version of the presented idea. Both authors designed the the experiment together. 
-{\firstauthor} wrote the stimuli and conducted the experiment.
-The statistical analysis was carried out by {\secondauthor}; {\firstauthor} prepared all summaries and plots.
-{\firstauthor} wrote the first draft of the manuscript and both authors edited it subsequently.
+Utku T\"urk conceived the initial version of the presented idea. Both authors designed the experiment together. 
+Utku T\"urk wrote the stimuli and conducted the experiment.
+The statistical analysis was carried out by Pavel Loga\v{c}ev; Utku T\"urk prepared all summaries and plots.
+Utku T\"urk wrote the first draft of the manuscript and both authors edited it subsequently.
 
-%\printbibliography %for use with biblatex; comment out if you use natbib
-%\bibliography{gp_short} %for use with natbib; comment out if you use biblatex, and change 'sample' by the name of your bib-file
+\section*{Data Availability Statement} %exclude
+
+All data and R code used in the data analysis is available at \url{https://osf.io/hegmd/}.
+
 \bibliographystyle{apacite}
-\bibliography{gp_short.bib}
+\bibliography{lcn_short.bib}
 
 \end{document}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% TeX-engine: luatex
-%%% End:

### 2022-02-10 paper/lcn_revision/manuscript-knitr.tex
lcn-revision

--- 2022-02-10 paper/lcn_revision/manuscript-knitr.Rnw
@@
 
-\documentclass[]{interact}
+\documentclass[]{interact}\usepackage[]{graphicx}\usepackage[]{color}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 \newcommand{\rev}[1]{{\color{red}#1}}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 \rev{We also calculated the relative probability of having an accusative marked noun compared to an possessive marked noun following genitive marking.
-Data from annotated treebanks from Universal Dependencies v2.9 \citep{TurkEtAl2021,KuzgunEtAl2020,TurkEtAl2019b,SulubacakEtAl2016,Coltekin2015} showed that the relative probability of encountering accusative marking after the genitive-marked noun is \Sexpr{p_acc_given_gen}.}
+Data from annotated treebanks from Universal Dependencies v2.9 \citep{TurkEtAl2021,KuzgunEtAl2020,TurkEtAl2019b,SulubacakEtAl2016,Coltekin2015} showed that the relative probability of encountering accusative marking after the genitive-marked noun is 0.21.}
 
@@
 
-We recruited \Sexpr{n_subject} undergraduate students to participate in the experiment in exchange for course credit.
-All participants were native Turkish speakers, with an average age of \Sexpr{mean_age} (range: \Sexpr{min_age} -- \Sexpr{max_age}).
+We recruited 118 undergraduate students to participate in the experiment in exchange for course credit.
+All participants were native Turkish speakers, with an average age of 20 (range: 18 -- 32).
 The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at Bo\u{g}azi\c{c}i University.
@@
 Prior to the analysis, we removed the data for all participants who failed to show sufficient sensitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected.
-Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between \rev{conditions with singular attractors \ref{ex:expitem-sgsg} and \ref{ex:expitem-sgpl}} fell below the threshold of \Sexpr{accuracy_threshold} percentage points.
+Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between \rev{conditions with singular attractors \ref{ex:expitem-sgsg} and \ref{ex:expitem-sgpl}} fell below the threshold of 0.1 percentage points.
 We also excluded trials in which the participants missed the response deadline.
-As a result, we excluded \rev{\Sexpr{perc_deletion_exp1}\%} of the trials from our experiment and \Sexpr{perc_deletion_lago}\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.
+As a result, we excluded \rev{3.39\%} of the trials from our experiment and 2.27\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.
 
@@
 In the results section, we provide summaries of the coefficient posterior distributions.
-For our model, we ran \Sexpr{n_chains} chains with \Sexpr{n_warmup} warm-up iterations and \Sexpr{n_iter-n_warmup} sampling iterations.
+For our model, we ran 4 chains with 1000 warm-up iterations and 1000 sampling iterations.
 The data for our study, along with our analysis scripts can be found at \url{https://osf.io/hegmd/}.
@@
 Figure \ref{fig:AverageResponses} shows the average proportions of ``acceptable'' responses by experimental condition in our experiment with unambiguous possessive marking, side by side with Lago et al.'s findings.
-It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = \Sexpr{exp1_cur_entry1$M}, SE = \Sexpr{exp1_cur_entry1$SE}) than their counterparts with singular attractors (M = \Sexpr{exp1_cur_entry2$M}, SE=\Sexpr{exp1_cur_entry2$SE}).
-The magnitude of the effect (\Sexpr{m_effect}) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was also 0.11.
-Accuracy rates for grammatical conditions were nearly equal (M = \Sexpr{exp1_cur_entry3$M} and \Sexpr{exp1_cur_entry4$M}, SE = \Sexpr{exp1_cur_entry3$SE} and \Sexpr{exp1_cur_entry4$SE}, for singular and plural attractors respectively).
+It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = 0.24, SE = 0.01) than their counterparts with singular attractors (M = 0.14, SE=0.01).
+The magnitude of the effect (0.10) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was also 0.11.
+Accuracy rates for grammatical conditions were nearly equal (M = 0.92 and 0.91, SE = 0.01 and 0.01, for singular and plural attractors respectively).
 
-<<AverageResponses, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='The average percentage of acceptable responses according to the experimental conditions in our study and \\citet{LagoEtAl:2019}.
-Error bars signal standard errors calculated following \\citet{Morey:2008,Cousineau:2005}.'>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[hbt!]
 
-plot(p_avg_resp)
+{\centering \includegraphics[width=\linewidth]{figure/AverageResponses-1}
 
-@
+}
+
+\caption{The average percentage of acceptable responses according to the experimental conditions in our study and \citet{LagoEtAl:2019}.
+Error bars signal standard errors calculated following \citet{Morey:2008,Cousineau:2005}.}\label{fig:AverageResponses}
+\end{figure}
+
+\end{knitrout}
 
 Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function.
-The main effect of grammaticality (\Sexpr{estimate_cGrammatical}) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the negative interaction between grammaticality and attractor number (\Sexpr{estimate_cGrammatical_cAttractorPlural}) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
-There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number (\Sexpr{estimate_threeway_interaction}), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments (\Sexpr{m_effect_lago}).
-This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor ((\Sexpr{estimate_ungramResp_cAmbiguity_cAttractorPlural}).
-It also showed a main effect of plural attractor (\Sexpr{estimate_ungramResp_cAttractorPlural}).
+The main effect of grammaticality ($\hat{\beta}=3.01;$ $CI=[2.76; 3.27];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.71;$ $CI=[-1.00; -0.44];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
+There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.29;$ $CI=[-0.81; 0.20];$ $P(\beta<0)=    .88$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments ().
+This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor (($\hat{\beta}=0.06;$ $CI=[-0.25; 0.37];$ $P(\beta<0)=    .36$).
+It also showed a main effect of plural attractor ($\hat{\beta}=0.50;$ $CI=[0.32; 0.67];$ $P(\beta<0)< .001$).
 Taken together, the coefficients indicated a substantial agreement attraction effect regardless of the presence of local ambiguity.
 
-<<ResponseModel, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\\% credible intervals for the probit regression coefficients for the model of responses in our experiment and \\citet{LagoEtAl:2019}.'>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[hbt!]
 
-suppressWarnings({
-p_m_response
-})
+{\centering \includegraphics[width=\linewidth]{figure/ResponseModel-1}
 
-@
+}
 
-<<ResponseModelUngram, message = FALSE, echo=FALSE, warning = FALSE, dev='cairo_pdf', fig.height=1.5, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\\% credible intervals for the probit regression coefficients for the model of responses to \\protect{\\textbf{ungrammatical sentences}} in our experiment and \\citet{LagoEtAl:2019}.'>>=
+\caption{Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses in our experiment and \citet{LagoEtAl:2019}.}\label{fig:ResponseModel}
+\end{figure}
 
-suppressWarnings({
-p_m_ungram_response
-})
+\end{knitrout}
 
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[hbt!]
+
+{\centering \includegraphics[width=\linewidth]{figure/ResponseModelUngram-1}
+
+}
+
+\caption{Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses to \protect{\textbf{ungrammatical sentences}} in our experiment and \citet{LagoEtAl:2019}.}\label{fig:ResponseModelUngram}
+\end{figure}
+
+\end{knitrout}
 

### 2022-02-10 paper/lcn_revision/manuscript.Rnw
lcn-revision

--- 2022-02-10 paper/lcn_revision/manuscript-knitr.Rnw
@@
 
-<<AverageResponses, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='The average percentage of acceptable responses according to the experimental conditions in our study and \\citet{LagoEtAl:2019}.
-Error bars signal standard errors calculated following \\citet{Morey:2008,Cousineau:2005}.'>>=
+<<AverageResponses, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\linewidth', fig.pos='hbt!', fig.cap='The average percentage of acceptable responses according to the experimental conditions in our study and \citet{LagoEtAl:2019}.
+Error bars signal standard errors calculated following \citet{Morey:2008,Cousineau:2005}.'>>=
 
@@
 
-<<ResponseModel, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\\% credible intervals for the probit regression coefficients for the model of responses in our experiment and \\citet{LagoEtAl:2019}.'>>=
+<<ResponseModel, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses in our experiment and \citet{LagoEtAl:2019}.'>>=
 
@@
 
-<<ResponseModelUngram, message = FALSE, echo=FALSE, warning = FALSE, dev='cairo_pdf', fig.height=1.5, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\\% credible intervals for the probit regression coefficients for the model of responses to \\protect{\\textbf{ungrammatical sentences}} in our experiment and \\citet{LagoEtAl:2019}.'>>=
+<<ResponseModelUngram, message = FALSE, echo=FALSE, warning = FALSE, dev='cairo_pdf', fig.height=1.5, fig.align='center', out.width='\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses to \protect{\textbf{ungrammatical sentences}} in our experiment and \citet{LagoEtAl:2019}.'>>=
 

### 2022-02-10 paper/lcn_submission_pre_revision/cover_letter.tex
lcn-revision

\documentclass[11pt]{letter}
\usepackage{blindtext}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\name{Utku T\"{u}rk}
%\address{Bo\u{g}azi\c{c}i University}
%\signature{signature de l'expéditeur}
\date{\today}

\begin{document}

\begin{letter}{Dear Prof. Lorraine K. Tyler,}

\opening{Together with Pavel Loga\v{c}ev (Bo\u{g}azi\c{c}i University), I would like to submit our work titled \emph{``Agreement Attraction in Turkish: The Case of Genitive Attractors''} to Language, Cognition and Neuroscience for consideration as a short article. }

In the manuscript, we test an alternative explanation of previously attested agreement attraction effects in Turkish (Lago et al., 2019, \textit{Linguistic Approaches to Bilingualism}). Lago and colleagues found that in Turkish genitive-possessive constructions similar to the English \textit{the singer's friends}, the genitive noun phrase (\textit{singer's}) can cause agreement attraction effects. This finding is surprising, as no such effects have been attested in comparable structures in English (Nicol et al., 2016, \textit{Front. in Psych.}).

Lago et al. argue that genitives can function as attractors in Turkish but not in English because genitive subjects exist in Turkish but not English. We test an alternative explanation, which is that their findings are due to a local ambiguity in their experiment, which constitutes a potential confound.

Having eliminated the potential confound, we were able replicate the agreement attraction effect in Turkish genitive-possessive structures. We thus demonstrate that agreement attraction effects occur in unambiguous genitive-possessive constructions in Turkish.

This finding lends further credence to the idea that the observed differences between Turkish and English structures are indeed likely to be due to the presence of genitive subjects in the former but not in the latter as argued by Lago and colleagues.

\ps{
Sincerely,\\
Utku T\"{u}rk\\
Department of Linguistics\\
Bo\u{g}azi\c{c}i University\\
Turkey}
%\cc{nom des autres destinataires}
%\encl{pièces jointes}
\end{letter}
\end{document}

### 2022-02-10 paper/lcn_submission_pre_revision/lcn_turkish_agreement_attraction.tex
lcn-revision

--- 2022-02-10 paper/lcn_revision/manuscript-knitr.Rnw
@@
 
-\newcommand{\rev}[1]{{\color{red}#1}}
-
 \begin{document}
@@
 \begin{keywords}
-Agreement attraction; syncretism; Turkish; \rev{sentence processing; number}
+Agreement attraction; syncretism; Turkish; Bayesian GLM; replication
 \end{keywords}
@@
 
-In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of local ambiguity in \rev{their} experimental sentences, as a result of which all subject head nouns were ambiguous between possessive and accusative case.
+In this paper, we test an alternative explanation of \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) findings which is related to an instance of local ambiguity in the experimental sentences in their experiment, as a result of which all subject head nouns were ambiguous between possessive and accusative case.
 
@@
 \citet{LagoEtAl:2019} demonstrated an agreement attraction effect in Turkish genitive-possessive constructions in a speeded acceptability judgment study with sentences like \ref{ex:lago}, in which the number of the attractor and the verb was manipulated.
-The resulting $2$x$2$ design, indicated by brackets and slashes in \ref{ex:lago}, consisted of two grammatical conditions, in which the verb agreed \rev{in number} with the singular subject head noun, and two ungrammatical conditions, in which the verb carried plural agreement, and thus did not agree with the subject.
+The resulting $2$x$2$ design, indicated by brackets and slashes in \ref{ex:lago}, consisted of two grammatical conditions, in which the verb agreed with the singular subject head noun, and two ungrammatical conditions, in which the verb carried plural agreement, and thus did not agree with the subject.
 In ungrammatical sentences, they found a higher percentage of \textit{acceptable} responses when the genitive attractor was plural than when it was singular, indicating agreement attraction.
@@
 technician-\{\textsc{pl}/\textsc{sg}\}-\textsc{gen} instructor-\textsc{poss} extraordinarily fast run-\textsc{pst}-\{\textsc{pl}/\textsc{sg}\}\\
-\glt ``The technician's/technicians' instructor \rev{ran\{\textsc{pl}/\textsc{sg}\}} extraordinarily fast.''
+\glt ``The technician's/technicians' instructor extraordinarily fast ran\{\textsc{pl}/\textsc{sg}\}.''
 
-\citet{LagoEtAl:2019} hypothesized that these effects originated from how case and number information \rev{are} encoded and retrieved: According to \citeauthor{LewisVasishth:2005}'s (\citeyear{LewisVasishth:2005}) cue-based retrieval model, phrases are encoded in a content-addressable memory as bundles of features called \textit{chunks} which include information like number, gender, case, and syntactic function \citep[e.g.,][]{SmithVasishth:2020}.
+\citet{LagoEtAl:2019} hypothesized that these effects originated from how case and number information is encoded and retrieved: According to \citeauthor{LewisVasishth:2005}'s (\citeyear{LewisVasishth:2005}) cue-based retrieval model, phrases are encoded in a content-addressable memory as bundles of features called \textit{chunks} which include information like number, gender, case, and syntactic function \citep[e.g.,][]{SmithVasishth:2020}.
 Under \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) proposal, participants predict the number of the verb based on the noun phrases they process while reading the subject.
@@
 As a result, the head noun (\textit{'instructor'}) in \ref{ex:ambiguous} can be disambiguated towards possessive case as in \ref{ex:ambiguous_possessive}, or towards accusative case as in \ref{ex:ambiguous_accusative}, where the genitive-marked noun functions as an embedded subject, and the matrix subject is omitted due to pro-drop.
-\rev{We also calculated the relative probability of having an accusative marked noun compared to an possessive marked noun following genitive marking.
-Data from annotated treebanks from Universal Dependencies v2.9 \citep{TurkEtAl2021,KuzgunEtAl2020,TurkEtAl2019b,SulubacakEtAl2016,Coltekin2015} showed that the relative probability of encountering accusative marking after the genitive-marked noun is \Sexpr{p_acc_given_gen}.}
 
@@
   technician-\textsc{gen} instructor-\textsc{poss} fire-\textsc{nmlz}-\textsc{poss}-\textsc{acc} see-\textsc{pst}-\textsc{1sg}\\
-  \glt ``I saw the technician firing the \rev{instructor}.''
+  \glt ``I saw the technician firing the fast.''
 
@@
 
-We recruited \Sexpr{n_subject} undergraduate students to participate in the experiment in exchange for course credit.
-All participants were native Turkish speakers, with an average age of \Sexpr{mean_age} (range: \Sexpr{min_age} -- \Sexpr{max_age}).
+We recruited 118 undergraduate students to participate in the experiment in exchange for course credit.
+All participants were native Turkish speakers, with an average age of 20 (range: 18 -- 32).
 The experiment was carried out following the principles of the Declaration of Helsinki and the regulations concerning research ethics at Bo\u{g}azi\c{c}i University.
-All participants provided informed consent before their participation and their identity \rev{were} completely anonimised.
+All participants provided informed consent before their participation and their identity are completely anonimised.
 
@@
 
-In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect, we analyzed the data from the present experiment \rev{and} compared our results to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) results, by including \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data in our Bayesian GLM and using the experiment as an additional factor in the analysis.
+In order to test whether the morphological ambiguity present in the \citet{LagoEtAl:2019} sentences affected the presence or magnitude of the agreement attraction effect, we analyzed the data from the present experiment compared our results to \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) results, by including \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) data in our Bayesian GLM and using the experiment as an additional factor in the analysis.
 
 Prior to the analysis, we removed the data for all participants who failed to show sufficient sensitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected.
-Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between \rev{conditions with singular attractors \ref{ex:expitem-sgsg} and \ref{ex:expitem-sgpl}} fell below the threshold of \Sexpr{accuracy_threshold} percentage points.
-We also excluded trials in which the participants missed the response deadline.
-As a result, we excluded \rev{\Sexpr{perc_deletion_exp1}\%} of the trials from our experiment and \Sexpr{perc_deletion_lago}\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.
+Specifically, we removed all participants for whom the difference in the percentage of \textit{yes} responses between the grammatical condition \ref{ex:expitem-sgsg} and the ungrammatical condition \ref{ex:expitem-sgpl} fell below the threshold of 0.25 percentage points.
+We also excluded trials in which the participants missed the response deadline or gave overly fast responses (below 200 ms).
+As a result, we excluded 10.22\% of the trials from our experiment and 2.38\% of the \citeauthor{LagoEtAl:2019}'s (\citeyear{LagoEtAl:2019}) trials.
 
@@
 We analyzed only experimental sentences and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors.
-We used by-participant and by-item intercepts and slopes for all predictors and \rev{their interaction}.
-All factors were sum-coded.
-\rev{A Student's \emph{t}-distribution ($\nu$ = 3, $\mu$ = 0, $\sigma$ = 2.5), a normal distribution ($\mu$ = 0, $\sigma$ = 1), a Cauchy distribution (($\mu$ = 0, $\sigma$ = 1)) and a LKJ distribution ($\eta$ = 2) were used for our intercept, slopes of predictors, standard deviations of random effects, correlation coefficients in interaction models respectively as priors.}
+We used by-participant and by-item intercepts and slopes for all predictors.
+All factors were sum-coded. We have used standard priors provided by the brms package.
 
@@
 Figure \ref{fig:AverageResponses} shows the average proportions of ``acceptable'' responses by experimental condition in our experiment with unambiguous possessive marking, side by side with Lago et al.'s findings.
-It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = \Sexpr{exp1_cur_entry1$M}, SE = \Sexpr{exp1_cur_entry1$SE}) than their counterparts with singular attractors (M = \Sexpr{exp1_cur_entry2$M}, SE=\Sexpr{exp1_cur_entry2$SE}).
-The magnitude of the effect (\Sexpr{m_effect}) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was also 0.11.
-Accuracy rates for grammatical conditions were nearly equal (M = \Sexpr{exp1_cur_entry3$M} and \Sexpr{exp1_cur_entry4$M}, SE = \Sexpr{exp1_cur_entry3$SE} and \Sexpr{exp1_cur_entry4$SE}, for singular and plural attractors respectively).
+It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = 0.22, SE = 0.01) than their counterparts with singular attractors (M = 0.11, SE=0.01).
+The magnitude of the effect (0.11) was in line with the findings reported in \citet{LagoEtAl:2019}, where the difference was also 0.11.
+Accuracy rates for grammatical conditions were nearly equal (M = 0.93 and 0.92, SE = 0.01 and 0.01, for singular and plural attractors respectively).
 
-<<AverageResponses, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='The average percentage of acceptable responses according to the experimental conditions in our study and \\citet{LagoEtAl:2019}.
-Error bars signal standard errors calculated following \\citet{Morey:2008,Cousineau:2005}.'>>=
+\begin{figure}[hbt!]
+\centering
 
-plot(p_avg_resp)
+\includegraphics[width=\linewidth]{AverageResponses-1.jpg}
 
-@
+\caption{The average percentage of acceptable responses according to the experimental conditions in our study and \citet{LagoEtAl:2019}.
+Error bars signal standard errors calculated following \citet{Morey:2008,Cousineau:2005}.}
+\label{fig:AverageResponses}
+\end{figure}
 
 Figure \ref{fig:ResponseModel} shows estimates and 95\% credible intervals of a Bayesian GLM with a probit link function.
-The main effect of grammaticality (\Sexpr{estimate_cGrammatical}) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
-Meanwhile, the negative interaction between grammaticality and attractor number (\Sexpr{estimate_cGrammatical_cAttractorPlural}) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
-There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number (\Sexpr{estimate_threeway_interaction}), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments (\Sexpr{m_effect_lago}).
-This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor ((\Sexpr{estimate_ungramResp_cAmbiguity_cAttractorPlural}).
-It also showed a main effect of plural attractor (\Sexpr{estimate_ungramResp_cAttractorPlural}).
+The main effect of grammaticality ($\hat{\beta}=3.09;$ $CI=[2.85; 3.35];$ $P(\beta<0)< .001$) indicates that, on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences.
+Meanwhile, the negative interaction between grammaticality and attractor number ($\hat{\beta}=-0.73;$ $CI=[-1.03; -0.43];$ $P(\beta<0)> .999$) indicated a larger difference (positive) effect of plural attractors in ungrammatical conditions, and thus a number agreement attraction effect.
+There was weak evidence for a negative three-way interaction between the presence of ambiguity, ungrammaticality, and attractor number ($\hat{\beta}=-0.28;$ $CI=[-0.78; 0.23];$ $P(\beta<0)=    .86$), which was largely driven by differences in the effect of attractor number in \textit{grammatical conditions}, as the magnitude of the effect in the ungrammatical conditions was identical in both experiments (0.11).
+This is consistent with the estimates of the model based on ungrammatical sentences in Figure \ref{fig:ResponseModelUngram}, which show no indication of an interaction between ambiguity and the presence of a plural attractor (($\hat{\beta}=0.01;$ $CI=[-0.31; 0.33];$ $P(\beta<0)=    .46$).
+It also showed a main effect of plural attractor ($\hat{\beta}=0.46;$ $CI=[0.26; 0.65];$ $P(\beta<0)< .001$).
 Taken together, the coefficients indicated a substantial agreement attraction effect regardless of the presence of local ambiguity.
 
-<<ResponseModel, message = FALSE, echo=FALSE,  warning = FALSE, dev='cairo_pdf', fig.height=3, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\\% credible intervals for the probit regression coefficients for the model of responses in our experiment and \\citet{LagoEtAl:2019}.'>>=
+\begin{figure}[hbt!]
+\centering
 
-suppressWarnings({
-p_m_response
-})
+\includegraphics[width=\linewidth]{ResponseModel-1.jpg}
 
-@
+\caption{Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses in our experiment and \citet{LagoEtAl:2019}.}
+\label{fig:ResponseModel}
+\end{figure}
 
-<<ResponseModelUngram, message = FALSE, echo=FALSE, warning = FALSE, dev='cairo_pdf', fig.height=1.5, fig.align='center', out.width='\\linewidth', fig.pos='hbt!', fig.cap='Estimates and 95\\% credible intervals for the probit regression coefficients for the model of responses to \\protect{\\textbf{ungrammatical sentences}} in our experiment and \\citet{LagoEtAl:2019}.'>>=
+\begin{figure}[hbt!]
+\centering
 
-suppressWarnings({
-p_m_ungram_response
-})
+\includegraphics[width=\linewidth]{ResponseModelUngram-1.jpg}
 
-@
+\caption{Estimates and 95\% credible intervals for the probit regression coefficients for the model of responses to \protect{\textbf{ungrammatical sentences}} in our experiment and \citet{LagoEtAl:2019}.}
+\label{fig:ResponseModelUngram}
+\end{figure}
 

### 2022-02-10 R/analysis/01_data_wrangling.R

@@ -73,11 +73,11 @@ avg_by_subj_lagoetal_wide <- avg_by_subj_lagoetal %>%
 
 n_subject <- data_exp1$subject %>% unique() %>% length()   
 # identify bad participants 
-accuracy_threshold <- 0.25
+accuracy_threshold <- 0.10
 bad_subjects <- subset(avg_by_subj_wide, delta_dc <= accuracy_threshold ) %>% .$subject
 data_exp1_clean <- data_exp1 %>% subset(!subject %in% bad_subjects)
 
-rt_threshold <- 200
+rt_threshold <- 0
 data_exp1_clean %<>% filter( RT > rt_threshold)
 
 perc_deletion_exp1 <- round(100*((nrow(data_exp1)-nrow(data_exp1_clean))  / nrow(data_exp1)),2)

### 2022-02-10 R/analysis/03_descriptive_plots.R

@@ -39,7 +39,7 @@ p_avg_resp <- avg_exp$resp %>%
                          color = attractor_num, group = attractor_num)) + 
                 geom_point(position = pd) + geom_line(position = pd) + 
                 facet_wrap(~experiment) + 
-  theme_bw(base_family = 'Fira Sans')+
+  theme_bw(base_family = 'Times')+
   theme(strip.background =element_rect(fill="white"))+
   theme(strip.text = element_text(colour = 'black'))
 
@@ -52,3 +52,4 @@ p_avg_resp <- p_avg_resp + xlab("") + ylab("Percentage 'acceptable'")
 
 avg_exp_resp_exp1 <- avg_exp$resp %>% subset(experiment == "Experiment 1")
 avg_exp_resp_lagoetal <- avg_exp$resp %>% subset(experiment == "Lago et al. (2019)")
+

### 2022-02-10 R/analysis/04_bayesian_models.R

@@ -9,62 +9,83 @@ df_merged %<>% within(., {
   #cFreqlog_n1 <- scale(freqlog_n1)
   #cFreqlog_n2 <- scale(freqlog_n2)
 })
+
+priors <- c(set_prior("student_t(3,0,2.5)", class = "Intercept"),
+            set_prior("normal(0,1)", class = "b"),
+            set_prior("cauchy(0,1)", class = "sd"),
+            set_prior("lkj(2)", class = "cor"))
+
+
 df_merged_nofillers <- df_merged %>% subset(is.na(source) | source != "filler")
+
+# RUN WITH PRIORS!
 
 
 models <- c()
 
 n_chains <- 4
 n_cores <- 4
-n_iter <- 20000
-n_warmup <- 2000
+n_iter <- 2000
+n_warmup <- 1000
+
+fname_responses <- "./R/fits/responses_priors"
+fname_responses_stan <- "./R/models/responses_priors.stan"
+m_responses <- brm(ResponseYes ~ cEndsInConsonant * cGrammatical * cAttractorPlural + 
+                                 (cGrammatical * cAttractorPlural + 1| subject) + 
+                                 (cGrammatical * cAttractorPlural + 1| item),
+                   data = df_merged_nofillers,
+                   prior = priors,
+                   family = bernoulli("probit"), 
+                   chains = n_chains, cores = n_cores, iter = n_iter, warmup = n_warmup, init_r = .1,
+                   file = fname_responses, save_model = fname_responses_stan)
+
+models[['responses']] <- m_responses
+
+fname_ungram_responses <- "./R/fits/ungram_responses_priors"
+fname_ungram_responses_stan <- "./R/models/ungram_responses_priors.stan"
+m_ungram_responses <- brm(ResponseYes ~ cEndsInConsonant * cAttractorPlural + 
+                            (cAttractorPlural + 1| subject) + 
+                            (cAttractorPlural + 1| item),
+                          data = df_merged_nofillers %>% subset(grammatical != "grammatical"),
+                          family = bernoulli("probit"), 
+                          prior = priors,
+                          chains = n_chains, cores = n_cores, iter = n_iter, warmup = n_warmup, init_r = .1,
+                          file = fname_ungram_responses, save_model = fname_ungram_responses_stan)
+
+models[['ungram_responses']] <- m_ungram_responses
 
 
 
-# formula_null <- ResponseYes ~ cGrammatical * cAttractorPlural +
[…]

### 2022-02-10 R/analysis/05_model_plots.R

@@ -7,7 +7,7 @@ contrast_names <- c("cGrammatical" = "Grammaticality",
                     "cEndsInConsonant:cGrammatical:cAttractorPlural" = "Ambiguity * Grammaticality * Plural Attractor")
 
 p_m_response <- 
-  create_model_coefs_plot( m_responses_full, 
+  create_model_coefs_plot( m_responses, 
         plot_stats = T, map_names = contrast_names,
         expand_right = 2.5, expand_top = 1.4, x_stat_adjust = 1.1,
         x_breaks = -1:4 ) + 
@@ -16,6 +16,27 @@ p_m_response <-
 p_m_response <- p_m_response + theme(axis.title.x = element_text(hjust=0.15))
 
 p_m_response <- print(p_m_response + annotate(x=-1, xend=4, y=0, yend=0, lwd=0.25, geom="segment"))
+
+
+{
+  ungram_contrast_names <- c("cEndsInConsonant" = "Ambiguity",
+                             "cAttractorPlural" = "Plural Attactor",
+                             "cEndsInConsonant:cAttractorPlural" = "Ambiguity * Plural Attractor")
+  
+  p_m_ungram_response <- 
+    create_model_coefs_plot( m_ungram_responses, 
+                             plot_stats = T, map_names = ungram_contrast_names,
+                             expand_right = 2, expand_top = 5, x_stat_adjust = 1.1,
+                             x_breaks = c(-1,-0.5,0,0.5,1) ) + 
+    xlab("Estimate (probit)")
+  
+  p_m_ungram_response <- p_m_ungram_response + theme(axis.title.x = element_text(hjust=0.25))
+  
+  p_m_ungram_response <- print(p_m_ungram_response + annotate(x=-1, xend=1, y=0, yend=0, lwd=0.25, geom="segment"))
+  
+}
+
+
 
 {
   if (exp1only ==T) {
@@ -79,22 +100,3 @@ p_m_response <- print(p_m_response + annotate(x=-1, xend=4, y=0, yend=0, lwd=0.2
     # TODO: fill this up.
   }
 }
-
-{
-  ungram_contrast_names <- c("cEndsInConsonant" = "Ambiguity",
-                             "cAttractorPlural" = "Plural Attactor",
-                             "cEndsInConsonant:cAttractorPlural" = "Ambiguity * Plural Attractor")
-  
-  p_m_ungram_response <- 
-    create_model_coefs_plot( m_ungram_responses, 
[…]

### 2022-02-10 R/analysis/06_text_inputs.R

@@ -13,11 +13,11 @@ exp1_cur_entry4 = avg_exp$resp %>% filter(experiment == "Experiment 1", grammati
 exp1_cur_entry4$M %<>% round(.,2)
 exp1_cur_entry4$SE %<>% round(.,2)
 
-lago_cur_entry1 = avg_exp$resp %>% filter(experiment == "Lago et al. (2019)", grammatical == "ungrammatical", attractor_num == "plural")
+lago_cur_entry1 = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "plural")
 lago_cur_entry1$M %<>% round(.,2)
 lago_cur_entry1$SE %<>% round(.,2)
 
-lago_cur_entry2 = avg_exp$resp %>% filter(experiment == "Lago et al. (2019)", grammatical == "ungrammatical", attractor_num == "singular")
+lago_cur_entry2 = avg_exp$resp %>% filter(experiment == "Lago et al. (2018)", grammatical == "ungrammatical", attractor_num == "singular")
 lago_cur_entry2$M %<>% round(.,2)
 lago_cur_entry2$SE %<>% round(.,2)
 
@@ -26,9 +26,9 @@ min_age <- min(form_exp1$Age)
 max_age <- max(form_exp1$Age)
 m_effect <- sprintf("%0.2f", exp1_cur_entry1$M-exp1_cur_entry2$M)
 m_effect_lago <- sprintf("%0.2f", lago_cur_entry1$M-lago_cur_entry2$M)
-estimate_cGrammatical <- print_estimate_with_ci( m_responses_full, 'cGrammatical' )
-estimate_cGrammatical_cAttractorPlural <- print_estimate_with_ci( m_responses_full, 'cGrammatical:cAttractorPlural')
-estimate_threeway_interaction <- print_estimate_with_ci( m_responses_full, 'cEndsInConsonant:cGrammatical:cAttractorPlural')
+estimate_cGrammatical <- print_estimate_with_ci( m_responses, 'cGrammatical' )
+estimate_cGrammatical_cAttractorPlural <- print_estimate_with_ci( m_responses, 'cGrammatical:cAttractorPlural')
+estimate_threeway_interaction <- print_estimate_with_ci( m_responses, 'cEndsInConsonant:cGrammatical:cAttractorPlural')
 
[…]

### 2022-02-10 R/analysis/bayesfactor.r

@@ -1,114 +1,0 @@
-
-
-fname_responses_null <- "./R/fits/responses_null"
-fname_responses_null_stan <- "./R/models/responses_null.stan"
-m_responses_null <- brm(ResponseYes ~ cGrammatical * cAttractorPlural +
-                                (cGrammatical * cAttractorPlural + 1| subject) +
-                                (cGrammatical * cAttractorPlural + 1| item),
-                    data = df_merged_nofillers,
-                    family = bernoulli("probit"), 
-                    prior = c(
-                            set_prior("student_t(3,0,2.5)", class = "Intercept"),
-                            set_prior("normal(0,1)", class = "b", coef = "cAttractorPlural"),
-                            set_prior("normal(0,1)", class = "b", coef = "cGrammatical"),
-                            set_prior("normal(0,1)", class = "b", coef = "cGrammatical:cAttractorPlural"),
-                            set_prior("normal(0,1)", class = "sd"),
-                            set_prior("lkj(2)", class = "cor")
-                            ),
-                    chains = n_chains, cores = n_cores, iter = n_iter, warmup = n_warmup, init_r = .1,
-                    file = fname_responses_null, save_model = fname_responses_null_stan,
-                    save_all_pars = TRUE)
-
-lml_null <- bridgesampling::bridge_sampler(m_responses_null, silent = TRUE)
-
-brm_fit_multiple <- function(prior_sd, lower_boundary, fname) {
-
-    fit <- brm(
-        ResponseYes ~ cEndsInConsonant * cGrammatical * cAttractorPlural +
-                    (cGrammatical * cAttractorPlural + 1 | subject) +
-                    (cGrammatical * cAttractorPlural + 1 | item),
-        data = df_merged_nofillers,
-        prior = c(
-            prior(normal(0,1), class = Intercept),
-            set_prior(paste0("normal(0,", prior_sd, ")"), class = "b", lb = lower_boundary),
-            prior(normal(0,1), class = "sd"),
-            prior(lkj(2), class = "cor")
-        ),
-        family = bernoulli("probit"),
[…]

### 2022-02-10 R/analysis/poss_vs_acc.R

@@ -1,0 +1,51 @@
+# load the neccassary packages
+library(udpipe)
+library(readxl)
+library(dplyr)
+library(magrittr)
+
+#load the conllu file from the directory
+tb <- udpipe_read_conllu("./data/all_ud_tr.conllu")
+
+# select relevant columns
+# doc_id is for treebank identification, 
+# token_id, sentence and sentence_id is just to be able to check it afterwards
+# feats is morphological features of a token
+tb %<>% dplyr::select(doc_id, sentence, sentence_id, token_id, feats)
+
+# create a lagged condition
+# prev_feats is the features of the previous word
+tb <- within(tb, prev_feats <- c(NA, head(as.character(feats), -1)))
+
+# create vector with search conditions, 
+# and grep rows that contain these markings
+# acc stands for accusative marking
+# since ud does not encode possessive as a case marking
+## we need to use [psor] tag.
+search_for <- c("Acc", "psor")
+tb_slim<- tb %>% subset(grepl(paste(search_for, collapse = "|"), feats))
+
+# only select accusative marked ones
+tb_gen_acc <- tb_slim %>% subset(grepl("Acc", feats))
+# with the genitive marking in the previous word
+tb_gen_acc %<>% subset(grepl("Gen", prev_feats))
+# clear false positives, for example mood = gen
+tb_gen_acc %<>% subset(!grepl("Mood=Gen", prev_feats))
+# tourism treebank is horrendous
+tb_gen_acc %<>% subset(!grepl("tourism", doc_id)) 
+# count
+c_acc_given_gen <- nrow(tb_gen_acc)
+
+tb_poss_acc <- tb_slim %>% subset(grepl("psor", feats))
+# discarded both acc and psor marking, 
+# because in those cases the last marking is actually accusative, 
+# so they should be included with acc markinds.
+tb_poss_acc <- tb_poss_acc %>% subset(!grepl("Acc", feats)) 
+tb_poss_acc %<>% subset(grepl("Gen", prev_feats))
+tb_poss_acc %<>% subset(!grepl("Mood=Gen", prev_feats))
+tb_poss_acc %<>% subset(!grepl("tourism", doc_id)) # tourism treebank is horrendous
+c_poss_given_gen <- nrow(tb_poss_acc)
+
+p_acc_given_gen <- c_acc_given_gen / (c_acc_given_gen + c_poss_given_gen)
+p_acc_given_gen <- round(p_acc_given_gen, 2)
+#p_poss_given_gen

### 2022-02-10 R/scripts/00.0-packages.R

@@ -4,7 +4,7 @@ library(gdata)
 library(MASS)
 library(magrittr)
 library(ggplot2)
-theme_set(theme_bw(base_family = "Fira Sans"))
+theme_set(theme_bw(base_family = "Times"))
 library(car, warn.conflicts = FALSE)
 library(brms)
 library(xtable)

### 2022-02-10 R/scripts/misc.R

@@ -276,7 +276,7 @@ create_model_coefs_plot <- function(m,
     p <- p + facet_wrap(~model)
   }
   
-  p <- p + theme_bw(base_family = "Fira Sans") + 
+  p <- p + theme_bw(base_family = "Times") + 
     theme(panel.border = element_blank(), 
           axis.ticks.y = element_blank(),
           #strip.text.x = element_blank(),

### 2022-02-10 full_analysis.R

@@ -6,6 +6,7 @@ set.seed(42)
 ## Set the path to the active document (full_analysis_and_pdf)
 setwd(here::here())
 
+
 ## Set parameters for the model analysis
 # parameters:
 # By default, only run a model for 'acceptable responses
@@ -15,66 +16,22 @@ setwd(here::here())
 # additional lago only bayesian model and coes
 # model of the RTs
 
-exp1only <- F; lagoonly <- F; rt <- F
+exp1only = F; lagoonly = F; rt = F
 
+files = c("./R/scripts/00.0-packages.R",
+            "./R/scripts/00.1-prepare.R",
+            "./R/scripts/00.2-eda.R",
+            "./R/scripts/misc.R", 
+            "./R/analysis/01_data_wrangling.R", "./R/analysis/02_word_freq.R", 
+            "./R/analysis/03_descriptive_plots.R","./R/analysis/04_bayesian_models.R",
+            "./R/analysis/05_model_plots.R", "./R/analysis/06_text_inputs.R", 
+            "./R/analysis/poss_vs_acc.R")
 
-# If else in which we check
-# First, the complete environment needed for the paper
-# If the file does not exist, it runs all scripts and analyses
-# saves the environment, which would already be present here.
-# If the file exist, it asks whether or not you would like to refresh it.
-# This would be done after some stuff within the analysis are changed
-# or the parameters above are changed.
-# If said yes (y), then everything is run again.
-# If said no (n), then it loads the complete_environment.RData
-# Possible improvements:
-## Check whether or not important stuff is in the complete_environment,
-## or whether or not it is corrupt
-## I put two files assignment, that should not be the case.
-
-if (file.exists('data/complete_environment.RData') == F) {
-  {
-    
-    ## Every file for the analysis and the paper is ordered nicely.
-    files <<- c("./R/scripts/00.0-packages.R",
-                "./R/scripts/00.1-prepare.R",
-                "./R/scripts/00.2-eda.R",
-                "./R/scripts/misc.R", 
-                "./R/analysis/01_data_wrangling.R", "./R/analysis/02_word_freq.R", 
-                "./R/analysis/03_descriptive_plots.R","./R/analysis/04_bayesian_models.R",
-                "./R/analysis/05_model_plots.R", "./R/analysis/06_text_inputs.R")
-    
-    ## source them all
-    for (f in files) {
-      source(f)
-    }
-    
-    ## save the image
[…]

### 2022-02-10 pdf_render.R

@@ -1,33 +1,19 @@
+load(file='./data/complete_environment.RData')
+
 # PDF render
 ## set working directory for the paper
 setwd(
   paste0(
-    here::here(),'/paper/glossa/'
+    here::here(),'/paper/lcn_revision/'
   )
 )
+
 # Convert it to knitr
 knitr::Sweave2knitr("manuscript.Rnw")
 
-
 # knit it to a pdf
-knitr::knit2pdf(compiler = 'xelatex', 'manuscript-knitr.Rnw') %>% 
-  file.rename(.,'manuscript.pdf')
-
-  
-# delete aux
-clean.knitr <- function() {
-  if (.Platform$OS.type=="unix") {
-    
-    system(paste0("cd '", getwd(), 
-                  "';rm *.gz;rm *.toc;rm *.log;rm *.glo;rm *.aux;rm *.ist;rm *-knitr.Rnw"))
-  } else {
-    warning("This function works only in UNIX systems")
-  }
-}
-
-#clean.knitr()
+knitr::knit2pdf(compiler = 'luatex', 'manuscript-knitr.Rnw')
 
 # open the PDF
-system2('open', args = 'manuscript.pdf', wait = FALSE)
-
+system2('open', args = 'manuscript-knitr.pdf', wait = FALSE)
 
